
\section{Medical Gear}\label{sec:medical_gear}
These devices are useful for first aid, diagnosis, surgery, and long~-term patient care. This section also describes static medical robots and microbots, which are treated as equipment. FOr mobile machines, see \textit{Medical Robots} (p. \pageref{sec:medical_robots}).

\subsection{Anti~-Toxin Kit}\label{subsec:anti-toxin_kit}
This is an antidote for one specific non~-nanotech toxin; 10 uses. \$25, 0.5 lb. LC4.

\subsection{Automed}\label{subsec:automed}
This is a coffin~-sized trauma pod. A single patient enters it, and the lid is shut. The pod can treat the patient on its own, or be controlled remotely.

The automed is equipped with robot arms, surgical tools, and diagnostic sensors. Its dedicated computer can treat its patient with Diagnosis-14, Electronics Operation (Medical)-14, First Aid-15, Physician-13, and Surgery-15. It has no imagination, so new diseases or strange problems may stump it -- in which case it does its best to sustain the patient and call for help.

An automed may also be used to diagnose or treat patients by manual or remote control. Used this way, it can function as a crash kit (p. \pageref{itm:crash_kit}), as diagnostic probes (below), and as a portable surgery (p. \pageref{itm:portable_surgery}); however, do not add their equipment modifiers when the automed uses its own skills. It's common for automeds to be teleoperated by AIs rather than living doctors.

An automed can sustain patients on life support, as a transport ESU (p. \pageref{itm:transport_esu}). It has 100 uses of bandage spray (below) and an internal pharmacy with room for 200 doses of drugs. The drugs are chosen and stocked by the automed's owners, and can be dispensed as needed. There is also a medium-range radio (p. \pageref{itm:radio_comm_medium}) connected to the medical sensors, an internal camera, and a speaker. \$100,000, 250 lb., E/200 hr. LC4.

\subsection{Bandage Spray}\label{subsec:bandage_spray}
This spray~-on antiseptic bandage seals and disinfects minor wounds while acting as an analgesic. It comes in flesh~-tone, colored, and transparent versions. First Aid using bandage spray receives a +2 (quality) bonus to skill. 

\textit{One-Use Bandage Spray:}\label{itm:one-use_bandage_spray} One use. \$3, 0.1 lbs. LC4. 

\textit{Bandage Spray Can:}\label{itm:bandage_spray_can} Six applications. \$15, 0.5 lbs. LC4.

The spray can stop bleeding and restore 1 HP in 5 seconds.

\subsection{Biomonitor}\label{subsec:biomonitor}
A non~-invasive monitor that records basic vital signs: pulse, heartbeat, blood pressure, etc. It has a small display, and stores its data internally on a standard disk so that a doctor can review the patient's medical history.

\textit{Biomonitor Bracelet:}\label{itm:biomonitor_bracelet} A doctor consulting or monitoring it receives a +1 (quality) bonus to Diagnosis skill for the wearer. \$50, 0.1 lb., A/100 hr. LC4.

\textit{Biomonitor Autoinjector:}\label{itm:biomonitor_autoinjector} As above, but incorporates a hypo or patch with 10 doses of drugs. It injects a programmed drug when a specific physical or stress related psychological condition occurs, e.g., unconsciousness, heart attack, Bad Temper or Berserk disadvantage, transforming into a werewolf, etc. If an appropriate drug is available, the device can serve as a Mitigator (see p. B112) for such conditions. \$200 (plus drug dosage), 0.15 lb., A/100 hr. LC4.

\textit{Diagnostic Sensors:}\label{itm:diagnostic_sensors} A ``doc in a box'' that connects to a set of sensors which must be attached over the body. It gives readouts on the patient's vital signs, including pulse, electrocardiogram, blood pressure, and respiratory rate. This provides a +2 (quality) bonus to Diagnosis. \$500, 0.5 lb., 2B/1,000 hr. LC4.

\subsection{Diagnostic Bed}\label{subsec:diagnostic_bed}
An examination table equipped with a full range of biological and medical scanners, including a CAT scan, a PET scan, T~-rays, ultrasound, and X~-rays. The patient lies on the table and scan results are projected onto an overhead screen.

Provides a +3 (quality) bonus to Diagnosis skill for most medical conditions, save those requiring detailed and non~-invasive brain imaging (see HyMRI, p. \pageref{subsec:hymri_scanner}). If the imaging results from a diagnostic bed is combined with diagnostic probes (below) or laboratory tests, the total bonus to skill is +5. \$25,000, 250 lbs., E/100 hr. LC4.

\subsection{Diagnostic Probes}\label{subsec:diagnostic_probes}
A solution of tiny medical biosensors which can be injected into a patient as part of a diagnostic procedure. Injecting them requires only a hypo, but retrieval requires an automed, diagnostic bed, chrysalis machine, or ESU. If they've had at least two hours to circulate, their data gives a +3 (quality) bonus to Diagnosis skill. If the data is combined with readings from an imaging scan performed by a diagnostic bed (above) or HyMRI (p. \pageref{subsec:hymri_scanner}), the total quality bonus to skill is +5.

A diagnostic bed can communicate with the probes without removal being required. If not removed, they'll work for a month and then degrade harmlessly. \$200 per dose. LC4.

\subsection{Disposable Hypo}\label{subsec:disposable_hypo}
A tiny one~-use syringe, no longer than a fingernail. It is preloaded with a dose of a drug, poison, or metabolic nanoagent in injectable form. If the drug costs \$5 or more, the hypo is included at no additional cost. Otherwise, \$0.50 plus the cost of the drug, 0.01 lb. LC4.

\subsection{Disposable Test Kit}\label{subsec:disposable_test_kit}
This tests for a specific disease, toxin, drug, or condition (e.g., pregnancy or malnutrition). No skill is required; the kit produces a color change to indicate a positive result. Available in versions that test urine or blood. \$5, 0.1 lb. LC4.

\subsection{Emergency Support Unit}\label{subsec:emergency_support_unit}
This is a life support system for patients who can no longer sustain their own bodily functions. See Mortal Wounds (p. B423) for the effect of trauma maintenance: the patient rolls to survive each day rather than each half-hour, and may use the higher of his Physician's skill or his HT.

Attaching a mortally-injured patient to an ESU requires an Electronics Operation (Medical) roll; each attempt takes 10 seconds. The system also includes diagnostic biosensors (p. \pageref{itm:diagnostic_sensors}). An ESU can function as a Mitigator (-60\%, see p. B112) for any Terminal Illness disadvantage caused by organ failure or similar problems.

An ESU can maintain the biological functions of someone who is dead (unless they're at -5 × HP or worse), preserving the body intact for later use. It can also perform whole~-blood transfusions. A ``blood-wash'' to remove toxins or nanomachines takes two hours.

\textit{Hospital ESU:}\label{itm:hospital_esu} A standard trauma maintenance unit, usually integrated into a hospital bed (the bed is not included). It provides a +2 (quality) bonus to Physician skill or HT rolls for trauma maintenance. \$15,000, 120 lbs., 4D/200 hr. LC4.

\textit{Transport ESU:}\label{itm:transport_esu} A lightweight but shock-resistant and stabilized version of the hospital ESU, attached to a stretcher or installed in a vehicle. It is used for safe transport of critically injured patients. It provides a +1 (quality) bonus to Physician skill or HT rolls for trauma maintenance. \$10,000, 60 lbs., 2D/100 hr. LC4.

\textit{Wearable Life Support Unit:}\label{itm:wearable_life_support_unit} Takes over the function of a specific failed organ, such as the heart or kidneys. It is only useful as a Mitigator for terminal illness caused by organ failure. \$2,000, 4 lbs., 4C/100 hr. LC4.

\textit{Suitcase ESU:}\label{itm:suitcase_esu} A lightweight system that can be attached to a prone patient. It is often used by paramedics or built into robots. \$5,000, 12 lbs., D/50 hr. LC4

\subsection{First Aid Kits}\label{subsec:first_aid_kits}
These kits contain basic medical instruments.

\textit{First Aid Kit:}\label{itm:first_aid_kit} Contains a bandage spray can (p. 197), ointments, etc. It gives a +1 (quality) bonus to First Aid skill, or +2 when using the bandage spray to treat bleeding. \$50, 2 lbs. LC4.

\textit{Crash Kit:}\label{itm:crash_kit} Contains a defibrillator, an oxygen mask, sutures, a bandage spray can, and no-shock drugs. It provides a +2 (quality) bonus to First Aid skill and counts as improvised equipment (-5) for Surgery skill. \$200, 10 lbs. LC4.

\subsection{Hibernation Chamber}\label{subsec:hibernation_chamber}
This chamber slows down a living subject's metabolic activity through chemical means. It reduces oxygen consumption, body temperature, food and water consumption. %It is the lowest-TL means of achieving ``suspended animation.''

It takes an hour to reduce the subject to a hibernation state, after which he is unconscious and his life support requirements drop by a factor of 10. He also ``ages'' at roughly one~-tenth the usual rate. The subject may be kept unconscious indefinitely if the chamber is equipped to provide for life support. Once the chamber is opened, the subject will be at 0 FP (or his current total, if less). He can recover FP normally, although stimulants may also be used.

Hibernation is used to give critically ill patients awaiting organ transplants more time, to keep patients suffering severe blood loss alive long enough for surgery, and to reduce life support requirements during long voyages.

\textit{Hibernation Chamber:}\label{itm:hibernation_chamber} Houses a single person. It is equipped with life support systems to keep the patient alive at his low metabolic rate, stimulate muscles, etc. These must be connected to an external life support source, but the occupant uses up one~-tenth the normal life support requirement. \$20,000, 200 lbs., external power. LC3.

\textit{Suspended Animation Tube:}\label{itm:suspended_animation_tube} Has a self~-contained regenerative life system that maintains all needs for as long as the power holds out. It will auto~-revive if power is about to fail. \$50,000, 750 lbs., 5E/10 years (or indefinite with external power). LC3.

\textit{Hibernation Case:}\label{itm:hibernation_case} A compact unit that fits inside a trunk. Designed mostly for storing organs and pets, but a child, dwarf, or small teenager (SM-1) could fit inside. It will auto~-revive if power is about to fail. \$10,000, 125 lbs., 5D/1 month. LC3.

Hibernation chambers are specific to classes of species (e.g., mammals) and may not work on some races.

\subsection{HyMRI Scanner}\label{subsec:hymri_scanner}
A conventional magnetic resonance imaging (MRI) scanner uses powerful electromagnets to stimulate the protons in the patient's body into emitting radio energy, which is used to produce a non~-invasive image. HyMRI augments this with an inhaled laser~-polarized inert gas such as an isotope of xenon or helium. This increases the resolution, especially in the lungs and nearby heart and brain.

Use Diagnosis skill to operate the scanner. It is basic equipment for the noninvasive diagnosis of brain and spinal disorders, as well as for mind emulation (p. \pageref{subsec:mind_emulation}), and provides a +5 (quality) bonus for diagnosing heart~-lung problems.

An MRI is not safely usable on anyone with magnetic or ferrous material in their body, e.g., cybernetics or fragments. If in doubt, a diagnostic scan should precede its use.

\textit{Hospital HyMRI:}\label{itm:hospital_hymri} A large device that the patient must lie inside. \$250,000, 500 lbs., 2E/10 hr (or external power). LC3.

\textit{Portable HyMRI:}\label{itm:portable_hymri} A helmet-sized device clamped over the patient. This is only usable for imaging the head. \$25,000, 50 lbs., 2D/1 hr. LC3.

\subsection{Plasti~-Skin}\label{subsec:plasti-skin}
This antiseptic and hemostatic patch can serve as a pressure bandage or a tourniquet. When the flesh beneath it heals, the patch falls off. It reduces the time required for bandaging (p. B424) from 60 seconds to 20 seconds, and the hemostatic proteins incorporated into it stop bleeding immediately after successful application.

Plasti~-skin is normally a different color than flesh (so the bandage can be easily identified). However, versions that assume the color of the underlying skin are available to cover tattoos and scars -- these are useful as disguises. A field dressing pack with four applications is \$2, 1/8 lb. LC4.

\subsection{Pneumohypo}\label{subsec:pneumohypo}
This hypo injects drugs with a charge of compressed air. It must be touching the patient to inject its drug. If used as a weapon, it can penetrate DR 1, or normal clothing, has Reach C, cannot parry, and uses Knife skill (or DX-4). Its vial holds one dose of a drug.

These devices are about the size of a penlight, and are included in all medical kits at no extra cost. Air cartridges providing 100 charges of compressed air are \$10. It takes three seconds to remove an empty drug vial or air cartridge and replace a new one. \$20, 0.1 lb. LC4.

\subsection{Physician's Equipment}\label{subsec:physician's_equipment}
Anyone under the care of a competent physician (Physician skill 12+) who has a stock of drugs and medical supplies gets +1 on all rolls for natural recovery. The healer may also make a Physician roll to cure the patient. Only one physician may roll per patient, but a single physician can care for many patients.

The exact number of patients a physician can attend to and the frequency with which he may roll to cure them depend on the TL of his Physician skill; see the Medical Help Table, below. On a success, the patient recovers 1 HP; on a critical success, he recovers 2 HP. This is in addition to natural healing. However, a critical failure costs the patient 1 HP!

\textit{Medical Supplies:} Drugs and other disposable supplies sufficient for 50 patient-days of Physician treatment. Gives a +1 (quality) bonus. Without this gear, the doctor operates as if at the TL6 level. \$500, 5 lbs. LC4.

\textit{Medical Bed:} A robotic nursing bed with built-in instruments, waste-relief systems, and an automated programmable drug dispensary for treating one patient. Adds +3 (quality) to Physician skill; allows three Medical Care rolls daily. \$10,000, 100 lbs., D/100 hr. LC4.

\textit{Biomonitor:} If a patient has been wearing a biomonitor bracelet (p. \pageref{itm:biomonitor_bracelet}) for at least a day, its accumulated data makes it easier to treat him. This gives +1 to Physician skill. \$50, 0.1 lb., A/100 hr. LC4.

\textit{Suit Doc:} An array of intelligent diagnostic sensors and general-purpose medical drug injectors that can be built into any sealed suit. It can perform ongoing Medical Care (p. B424-425) on the wearer as if he were under the care of a doctor operating at its TL who has Physician-10. A suit doc's drug pack is good for five days. Extra suit doc drug packs are \$50 and 0.5 lbs. \$5,000, 5 lbs., C/100 hr. LC3.

\begin{table}[H]
    \subsection{Medical Help Table}
    \centering
    \small
    \rowcolors{1}{}{\colormedical}
    \begin{tabularx}{\columnwidth}{ccc}
         \textbf{Medical TL} & \textbf{Frequency of Rolls} & \textbf{Patients per Doctor} \\
         6 & Daily & 20 \\
         % 9 && 2 × daily & 50 \\
         10 & 3 × daily & 50 \\
    \end{tabularx}
    % \caption{Caption}
    \label{tab:medical_help}
\end{table}

\subsection{Diagnostic Smart Bandage}\label{subsec:diagnostic_smart_bandage}
This is a sensor~-equipped hemostatic plasti~-skin bandage containing smart drug patches. A diagnostic smart bandage is manually applied; this takes 20 seconds, but otherwise use normal Bandaging rules (p. B424). It adds +2 (quality) bonus to skill when performing Bandaging, and its hemostatic proteins always stop bleeding.

After its application, the bandage will begin treating the patient for shock (p. B424), delivering a cocktail of drugs that help keep him calm, warm, and comfortable. After 10 minutes of this treatment, the bandage gets a First Aid-12 roll to determine its success. This is not quite as effective as a human medic: success restores only 1d HP rather than 1d+1, and there is no special result on a critical success. As usual, a critical failure results in a 2 HP loss.

\textit{Diagnostic Smart Bandage:}\label{itm:diagnostic_smart_bandage} Described above; four applications are \$20, 0.4 lbs. LC4.

\textit{Diagnostic Smart Bandage Spray:}\label{itm:diagnostic_smart_bandage_spray} Takes only three seconds to apply; uses a smart aerosol. One application is \$5, 0.1 lb. LC4.

\subsection{Surgical Equipment}\label{subsec:surgical_equipment}
A complete set of surgical equipment provides a +4 bonus to Surgery skill rolls in addition to the equipment quality modifiers described below. See Surgery (p. B223 and p. B424).

\textit{Surgical Instruments:}\label{itm:surgical_instruments} A complete set of surgical tools, including laser scalpels, forceps, bio-glue, sonic probe, and sutures. (This is also included in the crash kit, p. \pageref{itm:crash_kit}.) It is basic equipment for the Surgery skill. \$300, 15 lbs., 5B/20 hr. LC4.

\textit{Operating Theater:}\label{itm:operating_theater} An entire room full of specialized equipment. Its instruments include manipulators that can be controlled via virtual reality gloves and an augmented reality interface; the surgeon still needs steady hands, but he's not putting them inside the patient. As a result, smaller incisions are needed and recovery times are halved. It provides a +2 (quality) bonus to Surgery skill. \$200,000, 1,000 lbs., 20C/40 hr. or external power. LC4.

\textit{Portable Surgery:}\label{itm:portable_surgery} A complete set of equipment that fits in the back of a utility vehicle, a trailer, or a hospital cart. This equipment is favored by ``street docs'' and military units. Its capabilities are the same as that of an operating theater, but it gives a +1 (quality) bonus to Surgery skill and +2 (quality) bonus to First Aid. A portable surgery takes five minutes to pack or unpack. \$50,000, 250 lbs., 5C/40 hr. (or external power). LC4.

\textit{Specialized Operating Theater:}\label{itm:specialized_operating_theater} Dedicated to a particular Surgery specialization. It gives a +TL/2 (quality) Surgery bonus in that specialization, but is only basic equipment otherwise. \$1,000,000, 1,000 lbs., 20C/40 hr. or external power. LC4.

\textit{Specialized Portable Surgery:}\label{itm:specialized_portable_surgery} As above, but dedicated to a particular Surgery specialization, such as brain surgery or cybernetics. It provides a +2 (quality) bonus to Surgery skill in that specialization, but is only useful as basic equipment for other types of surgery. \$100,000, 250 lbs., 5C/40 hr. or external power. LC4.

\subsection{Pocket Medic}\label{subsec:pocket_medic} 
This is a static robot the size of a paperback book. If clamped onto a wounded area, it will treat injuries. It has a hypo, anesthetic spray gun, and small surgical arms. It dispenses bandage spray (p. 197), then treats for shock with First Aid-12 (+1 per TL after TL9). After it is finished, it signals for removal. If its sensors indicate that first aid has failed, or that the patient is not responding to treatment, it calls for a physician. It has a built-in short-range radio (p. 44). \$1,200, 2 lbs., B/10 hr. LC4.

\subsection{Medscanner}\label{subsec:medscanner}
This multi-purpose medical scanner can detect internal injuries, genetic problems, diseases, implants, and more.It is a pocket-sized device with a one~-yard range. It gives a +3 (quality) bonus to Diagnosis skill. \$1,000, 0.25 lbs., B/10 hr. LC4.

\subsection{Nanostasis}\label{subsec:nanostasis}
This is a means of safely shutting down a person's metabolism, putting him into a state of permanent suspended animation, in which no special preservation tank is needed. It uses nanomachines to install protective scaffolding and fixatives around and within every cell in the patient's body. Once placed in stasis, an organism does not require any oxygen or food, and cannot age or deteriorate, although it remains vulnerable to physical damage. Reversal of nanostasis requires similar bio~-nanotech to remove the preservatives and restart bodily functions.

A living being placed into nanostasis is not dead. However, it is inanimate and unconscious, with IQ 0 and the Immunity to Metabolic Hazards, Injury Tolerance (Unliving), and Unaging advantages.

Nanostasis can also replace the need for anesthesia during surgery.

Nanostasis is safe, but the subject will be disoriented for hours (sometimes days) afterward. Upon revival, the process supervisor makes a Physician roll. Critical failure means the patient has the Confused (9) disadvantage for 20-HT hours, and Amnesia (Partial) for at least a week; roll vs. HT weekly to recover. Failure produces the same effects, but roll vs. HT daily to regain memory. On a success, Confused lasts only (20-HT)/2 hours and there is no memory loss. Critical success means immediate recovery.

\textit{Nanostasis Tank:}\label{itm:nanostasis_tank} A growth tank (p. \pageref{subsec:growth_tank}) modified to place someone into nanostasis, or to revive him. It takes five hours for the process to slow and then completely stop the patient's metabolism. Afterward, he can be safely removed. Reviving a patient takes eight hours. The tank uses up one package of nanomachines (\$5,000, 0.1 lbs.) per patient. \$300,000, 250 lbs., E/200 hours. LC3.

\textit{Nanostasis Pod:}\label{itm:nanostasis_pod} An armored and radiation~-shielded (DR 50, PF 100) pod that contains a nanostasis tank and automatic suspension and revival equipment (Physician-14 for this purpose only). It powers down when not in use; it is designed to keep someone preserved for centuries. It can revive its occupant at a pre~-set date. \$500,000, 500 lbs., E/200 hours (when not powered down). LC3.

\subsection{Neural Inhibitor}\label{subsec:neural_inhibitor}
A two~-inch~-wide disk with adhesive bonding material on one side. When applied to the bare skin of a living being with an approximately terrestrial vertebrate nervous system, it cuts off nerve impulses.

Its effects depend on where it is placed. If a neural inhibitor were attached to a person's forearm, his hand would be paralyzed, but he'd feel no pain from a hand or forearm injury, and surgery could be performed without anesthesia. If it were placed near the neck over the spinal cord, he would be paralyzed from the neck down. Use on the skull induces unconsciousness until removed. If the subject is not cooperating, treat these effects as a HT-6 affliction attack; the victim may roll to resist each second in contact.

A neural inhibitor gives a +1 (quality) bonus to First Aid to treat shock (p. B424). \$200, 0.1 lb., A/10 hr. LC 3.

\subsection{Paramedical Swarm}\label{subsec:paramedical_swarm}
This swarm of microbots is designed for autonomous patient care. It is made up of teams of specialized microbots. Some taste blood and perform diagnosis, some cut away damaged tissue, clean wounds, sew up cuts, and inject drugs, and some enter the body to perform internal repairs or diagnosis.

The swarm may perform First Aid, cleaning and repairing damaged tissue and injecting no~-shock drugs. Each square yard of swarm can treat one person at a time. A paramedical swarm has Diagnosis-10 and First Aid-10. It provides its own basic equipment for both skills, but it cannot benefit from other types of medical equipment. Paramedical swarms can't treat somebody in a sealed suit, but a swarm can be housed in microbot arteries (p. \pageref{subsec:microbot_arteries}). \$6,000/square yard; see Swarmbots (pp. 35-37) for additional microbot swarm rules and options. LC3.

\subsection{Regeneration Tank}\label{subsec:regeneration_tank}
A regeneration tank is a biofab (p. \pageref{subsec:biofab}) optimized for rapid whole-body cell repair. The tank contains mechanisms for controlling nanomachines as they permeate the user's body, instructing and assisting every viable cell in what repairs to make. Nonviable cells are programmed to self-destruct, or are removed and replaced with clones of healthy cells.

A Physician roll is required to supervise the procedure. Success means it works normally; failure takes twice as long as usual. It can heal everything up to permanent crippling injuries, at 1 HP per 12 hours, or radiation at 10 rads per day. Missing limbs and organs regrow in six weeks. \$500,000, 600 lbs., 2E/200 hr. LC3. A regeneration tank requires nanomachines and feedstock: a week's supply is \$1,000, 1 lb.

\subsection{Rejuvenation Tank}\label{subsec:rejuvenation_tank}
This specialized regeneration tank reverses the aging process. Its nanomachines reset cellular clocks, killing senescent or dying cells and replacing them with healthy ones.

Rejuvenation requires three months of treatment, after which the subject's body is restored to young adulthood and full health. All age~-related disadvantages and attribute losses are removed, as are any crippling injuries.

Rejuvenation is a risky procedure. The process supervisor must make a Physician roll. On a critical success, the patient is rejuvenated and fully recovered. Success means that the patient is rejuvenated but suffers Confused (9) (p. B129) for 1d days as he adjusts to his rejuvenated body. Failure means the structures of his memory were permanently disrupted: he has Partial Amnesia (p. B123). A critical failure results in either a messy death (such as being turned into a mass of cancer cells) or revival with no mind at all. An unfortunate side effect of \textit{all} rejuvenations is the sterilization of the patient. Furthermore, each additional rejuvenation a patient undergoes adds a cumulative -1 penalty to the physician roll to use the tank.

A rejuvenation tank can also function as a regeneration tank. \$1,000,000, 600 lbs., 2E/200 hr. LC2.

\subsection{Suitcase Doc}\label{subsec:suitcase_doc}
This device must be placed atop a patient's torso or other injured part (this takes a Ready maneuver). After that, it is autonomous. It unfolds, extruding surgical manipulators, anesthesia and life support tubes, and diagnostic sensors as necessary. It uses its manipulators to cut away clothing and treats the patient using Diagnosis-10, First Aid-12, Physician-10, and Surgery-10. It incorporates diagnostic probes (p. \pageref{subsec:diagnostic_probes}), suitcase ESU (p. \pageref{itm:suitcase_esu}), and a crash kit (p. \pageref{itm:crash_kit}).

If the doc encounters a problem it can't handle, it calls for help on its short-range radio. It also carries 10 uses of bandage spray and an internal pharmacy with up to 20 doses of drugs. \$10,000, 20 lbs., 2C/10 hr. LC3.

\section{Medical Robots}\label{sec:medical_robots}
Most medical robots are static equipment or tiny microbotss.

\subsection{Nursebot}\label{subsec:nursebot}
\hfill \large{\textbf{209 points}}\normalsize

This man-shaped robot caregiver can assist the elderly and disabled, both at home and in clinics and hospitals. Its
long, dexterous fingers have retractable surgical instruments, which can function as claws if used in combat. Its oversized head contains infrared and sonar systems for patient imaging.

Some nursebots can pass as human, although a sculpted humanoid version is more common.

\begin{hangparas}{1em}{1}
    \textbf{Attribute Modifiers:} ST+3 [30]; HT+2 [20].
    
    \textbf{Secondary Characteristic Modifiers:} HP+7 [14].
    
    \textbf{Advantages:} Absolute Direction [5]; Ambidexterity [5]; Discriminatory Taste (Profiling, +50\%) [15]; Doesn't Breathe [20]; DR 2 [10]; High Manual Dexterity 2 [10]; Infravision [10]; Machine [25]; Microscopic Vision 2 [10]; Penetrating Vision 1 (Blockable, Dense Substances, -30\%) [7]; Radio (Burst, +30\%, Secure, +20\%, Video, +40\%) [19]; Sealed [15]; Sensitive Touch [10]; Sharp Claws (Switchable, +10\%) [6]; Vacuum Support [5].
    
    \textbf{Perks:} Accessories (Personal computer; surgical instruments) [2]; Sanitized Metabolism [1].
    
    \textbf{Disadvantages:} Electrical [-20]; Restricted Diet (Very Common, power cells) [-10].
\end{hangparas}

\subsubsection{Lenses}\label{subsubsec:nursebot_lenses}
Select one of these model lenses, then combine it with a machine intelligence lens (p. \pageref{sec:machine_intelligence_lenses}) and a biomorphic lens (p. \pageref{sec:biomorphic_lens}).

\begin{hangparas}{1em}{1}
    \textit{Vintage Model} (-5 points): Add Maintenance (one person, weekly) [-5]. \$150,000, 150 lbs., 2D/8 hr. LC4.
    
    \textit{Modern Model} (+1 point): Add Maintenance (one person, bi-weekly) [-3], Reduced Consumption 2 [4]. \$100,000, 150 lbs., 2D/24 hr. LC4.
\end{hangparas}

\section{Psychiatric Equipment}\label{sec:psychiatric_equipment}
This equipment is for monitoring and manipulating the mind.

\subsection{Brainscanner}\label{subsec:brainscanner}
A brainscanner observes the human brain by the mind's electrical activity. A high-resolution 3D structural scan of the subject's brain is assembled using a HyMRI or similar system. Other real-time electrical recording technologies such as magnetoencephalography (MEG) or electroencephalography (EEG) are used to record the firing of individual brain cells and map those impulses to the scan.

Brainscanners can also be used to create a ``persona map,'' a model of the way a person thinks. The subject must be conscious, but cooperation is not required. Roll against Electronics Operation (Medical); one roll is allowed each day. Updates are performed at +1 and generally take a few hours.

Careful study of a recent persona map can reveal a person's main mental advantages, disadvantages, and quirks. It requires two hours and a successful Psychology skill roll, which provides a +2 bonus to Psychology and +1 to other social skills when dealing with that individual.

\textit{Scanning Net:}\label{itm:scanning_net} This is a network of electrodes, superconducting quantum-interference devices (SQUID), and other sensors that must be attached to the subject's head. It must be used in conjunction with a prior HyMRI scan. \$6,000, 4 lbs. LC4.

\textit{Implant Net:}\label{itm:implant_net} A neural interface (p. \pageref{sec:neural_interfaces}) or biomonitor implant (p. \pageref{subsec:biomonitor_implant}) allows brain scans without the use of a scanning net. This provides +1 to all tasks that require a brainscan.

\subsection{Deep Brainscanning}\label{subsec:deep_brainscanning}
This is an \textit{interactive} brainscan. The person running the scan must fit the subject with a neural interface (p. \pageref{sec:neural_interfaces}), then stimulate the parts of the brain associated with memory recall. The subject is conscious but in a dreamlike state through most of the process. Roll every week rather than daily. Success provides data that gives triple the bonus of a brainscan, and which is sufficient to design a shadow mind emulation (p. \pageref{subsec:mind_emulation}).

\section{Biotech Equipment}\label{sec:biotech_equipment}
Equipment for growing life forms and for biotechnology research. Portable labs (p. \pageref{subsec:portable_laboratories}) for Biology skill are also useful.

\subsection{Growth Tank}\label{subsec:growth_tank}
An artificial womb that can be used to grow a life form to infancy or adulthood. It's no faster than natural growth. An organism developing in a growth tank has the same awareness as a baby in its womb. If kept past the fetal stage, it will not develop mentally beyond infancy unless additional stimulation (such as an educational dreamgame) is provided.

\textit{Incubator Growth Tank:}\label{itm:incubator_growth_tank} Can carry a human infant to term. \$10,000, 10 lbs., external power. LC3. 

\textit{Adult Growth Tank:}\label{itm:adult_growth_tank} Big enough to allow a human to grow to adulthood inside it. \$200,000, 200 lbs., external power. LC3.

Larger and smaller tanks are \$1,000 and 1 lb. for each pound of body weight they can support.

\subsection{Biofab}\label{subsec:biofab}
This is a specialized wet nanofactory that can assemble organs or even a complete life form. A biofabricator can assemble living things rapidly (about a year of growth every week). It can grow an adult human in about 18-20 weeks.

\textit{Incubator Biofab:}\label{itm:incubator_biofab} Can carry a human infant to term. \$200,000, 50 lbs., D/20 hr. (but usually runs on external power). LC2.

\textit{Adult Biofab:}\label{itm:adult_biofab} Big enough to allow a human to grow to adulthood inside it. \$4,000,000, 1,000 lbs., E/20 hr. (but usually runs on building power). LC2.

Larger and smaller tanks are \$20,000 and 5 lb. for each pound of body weight they can support.

\section{Drugs and Nano}\label{sec:drugs_nano}
A drug may be a pill, injection, aerosol, contact agent, or aerosol contact agent. Many drugs are available in multiple forms. Most pills require 30 minutes or more to take effect, but can be dissolved in drinks. Contact agents such as patches take at least five minutes, while aerosols and injections take effect almost immediately. Double cost for aerosols or contact agents, or multiply by 10 for aerosol contact agents.

Each doubling of dosage gives an extra -1 to the roll to resist.

\subsubsection{Analgine~-Beta}\label{subsubsec:analgine-beta}
This drug masks pain for a period equal to half the user's HT in hours. Unfortunately, the user is also Numb for the same period. \$50 per dose. LC3.

\subsubsection{Antirad}\label{subsubsec:antirad}
This cocktail of multiple drugs has the combined effect of partial protection against radiation. It grants the user Radiation Tolerance 5 (p. B79). \$80/dose. LC4

\subsubsection{Hyperstim}\label{subsubsec:hyperstim}
This drug \textit{instantly} awakens an unconscious person, regardless of his HP or FP. Someone using this drug cannot fail a HT roll to avoid unconsciousness. After the drug wears off, roll vs. HT. Failure causes 1 HP damage, while critical failure also results in a heart attack. \$100 per dose. LC2.

\subsubsection{Morphazine}\label{subsubsec:morphazine}
This drug puts the patient into a deep, dreamless sleep. The user gets a HT-3 roll to resist; failure results in the user falling asleep for eight hours times the margin of failure. It is a reliable, powerful sleeping pill, often available only through prescription. If injected, it works in one second. \$10 per dose. LC3.

\subsubsection{Soothe}\label{subsubsec:soothe}
Places the user in a dreamy state of euphoria. Roll HT-3; if the roll is failed, the drug causes the Euphoria irritating condition and High Pain Threshold advantage for five minutes times the margin of failure. The user has no memory of events that occur while under the drug's influence. \$15 per dose. LC4.

\subsubsection{Crediline}\label{subsubsec:crediline}
A psychoactive drug designed for interrogations and drug-assisted psychotherapy. It is often abused by criminals. The subject becomes trusting and talkative. He must roll HT-3 or suffer the Gullibility (9) disadvantage for (25-HT) minutes. \$240 per dose. LC2.

\subsubsection{Ascepaline}\label{subsubsec:ascepaline}
Accelerates cellular regeneration: anyone using it regenerates 1 HP every 4 hours. Each dose lasts a day, and a week should elapse before another dose is taken. If not, roll vs. HT+2 for the second dose, HT+1 for the third, etc. Failure means the user's natural ability to heal without the drug is permanently damaged: the user gains Unhealing (Partial) (p. B160). He may still use Ascepaline, however. \$20 per dose. LC3.

\subsubsection{Purge}\label{subsubsec:purge}
This cleanses the user's system of foreign biochemicals. If the user makes a HT roll, it neutralizes any active drugs (including recreational drugs and alcohol) within 2d minutes. Failure means that the dose had no effect; critical failure also nauseates the user (-3 DX for 1 hour). Purge will not counteract drug addiction or cure side effects that remain after the drug that caused them wears off. Purge has no effect on TL11+ drugs or most deadly poisons, but it will counteract sleep gas. \$20 per dose. LC4.

\subsubsection{Memory~-Beta}\label{subsubsec:memory~-beta}
Stimulates the user's memory. After taking a dose of the drug, he can remember nearly anything that has happened to him that he concentrates on recalling. An IQ roll is required to focus on something specific, and some stimulus is required to recall buried memories. If the IQ roll fails, the user gets lost in his own memories, reliving bits and pieces of his life. A critical failure results in the user being captured by some especially strong memory, whether of joy, tragedy, terror or even birth. This may trigger buried phobias or other psychological traumas. \$250 per dose. LC3.

\subsubsection{Genericillin}\label{subsubsec:genericillin}
This is a very powerful, general-purpose antibiotic. It doesn't treat all diseases, but it's a good thing to try. A dose of genericillin gives a +5 to HT to recover from bacterial diseases and infection for a week. \$25 per dose. LC4.

\subsubsection{Enzyme-Blocking Drugs}\label{subsubsec:enzyme-blocking_drugs}
Enzyme-blocking drugs cover a wide-variety of drugs which target the enzymes vital to a particular bacteria's or virus' ability to replicate. Sometimes, this enzyme-targeting has a negative affect on the human body, and with each dose the user must make a HT roll to avoid losing 1 HP.

Enzyme blockers may either be targeted against a single species of virus or bacteria (e.g., influenza) or be broad-spectrum versions, designed to affect numerous common bacteria. Unlike a vaccine, a specific enzyme blocker is generally effective against mutant strains; a mutation is rarely drastic enough to alter the fundamental enzymes that a particular virus or bacteria uses.

A specific enzyme blocker, affecting only one microbe, gives a +8 to HT rolls to resist that particular illness; broad-spectrum agents give a +3. The effect is similar to that of an antibiotic, but is effective against viruses or parasites; HT bonuses are cumulative with antibiotics.

A typical course costs \$10. Some might require a \textit{daily} course to stave off a virus.

\subsubsection{Wideawake}\label{subsubsec:wideawake}
An extremely effective stimulant, this drug time-releases controlled doses of stimulants that prevent the user falling asleep, without causing any side effects. It provides the Doesn’t Sleep advantage for a week. Any form, \$20/dose. LC4.

\subsubsection{Adders}\label{subsubsec:adders}
Adders are a series of different drugs which that temporarily add to physical or mental abilites. Each variety of drug provides a bonus to one of ST, DX, IQ, HT, or Basic Move. One dose adds 1 point, but multiple doses can be taken together. After it wears off, the affected attribute suffers a penalty equal to the original bonus and lasting twice as long.

To obtain the desired effect, a user must make a HT roll at -1 for every dose taken. If the roll is successful the attribute is raised by the number of doses taken for (25 - HT)/4 hours. If the roll fails, the attribute is raised by 1 for one hour, regardless of the number of doses taken. On a critical failure, the drug decreases the attribute by the number of doses taken, for one hour.

As long as any attribute bonus or penalty is in effect, using any other type of adder results in adverse side effects. If the user takes the same type of adder within 24 hours of a dose, he must make a new HT roll at a penalty equal to the total of all doses taken in that period. The bonus is only that of the new dose, but the letdown period is that of all the doses combined.

Adder users often feel very good under the effects of the drug -- similar to the Overconfidence advantage -- and are at least mildly depressed when it wears off. 

Poor quality or black market adders can be addictive. Pill or hypo, \$25/dose. LC3.

\subsubsection{Peter-Pan Process}\label{subsubsec:peter-pan_process}
These drugs can be taken by anyone who is not yet an adult. They retard physical growth (and the onset of puberty, if it has yet to occur). They do not halt aging. See Children (p. B20) for realistic attributes for pre-adolescents and young teens.

The course of hormone treatment requires \$500 per month to ``stunt'' apparent age. Child actors, teenage gymnasts, male singers and others may be stunted to lengthen their careers, but many legal systems consider the practice to be child abuse. LC3.

\subsubsection{Basic}\label{subsubsec:basic_drug}
A mild and relatively safe psychoactive combat drug, Basic has two effects: it provides Combat Reflexes (no effect if someone already has it) and suppresses the Pacifism disadvantage (exception: Total Nonviolence degrades to Reluctant Killer). Anyone who has Total Nonviolence who seriously injures or kills someone, or someone with Cannot Kill who kills must, \textit{after the drug wears off}, roll to avoid a nervous breakdown as described under the Cannot Kill disadvantage. It requires a HT-2 roll to resist and has short-term effects lasting (25 - HT)/4 minutes. \$12/dose. LC1.

\subsubsection{Hypoxyline}\label{subsubsec:hypoxyline}
Humans suffer lung damage when breathing gases with high partial pressures of oxygen, which can occur in a very dense atmosphere (p. B430) or while diving. This drug allows a human to operate with comfort in dense atmospheres without requiring a respirator to reduce oxygen pressure, or to breathe compressed air rather than special diving gas mixtures without ill effect. Only available in hypo form, lasting a day per dose. \$50/dose. LC4.

% \subsection{Biomedical Nanomachines}\label{subsec:biomedical_nanomachines}
% These travel through tissue examining, dismantling, and rebuilding damaged molecular structures. Early versions are the size of bacteria, and specialized to repair specific types of molecular damage. More advanced machines are the size of viruses, with onboard computers, manipulators, and motive systems.

% These machines are powered by the same chemicals that power the body's own cells. Cell repair machines produce some heat, but the resulting rise in body temperature is no greater than that produced by ordinary exercise.

% \subsubsection{Tailored Immune Machines}\label{subsubsec:tailored_immune_machines}
% Another form of modern medicine uses biomedical nanomachines to seek out and destroy disease-causing microorganisms or
% tumors. It's also possible to get expensive nano that wards
% off these problems and stays in the body for weeks or
% permanently; see GURPS Bio-Tech. Alternatively, medics
% may use cheaper tailored nanomachines designed for a
% specific purpose. This requires successfully diagnosing the
% problem. After it is diagnosed, prescribing the correct treat-
% ment requires a successful Physician roll.
% A dose of tailored nano specific to a particular disease is
% $50 per dose and LC4; pharmacies, automeds, and hospi-
% tals usually stock a large range. Tailored immune machines
% for exotic ailments such as a rare disease or biological
% weapon may be harder to find, and cost $500 per dose.
% Tailored immune machines for unknown diseases require a
% new invention (but see Programmable Immune Machines,
% below).
% If the correct nano is taken (by injection or pill) it cures
% the patient in 3d hours at TL10 or 1d hours at TL11+. If it
% was incorrectly proscribed, it will have no effect; another
% try with a different selection may be possible. If one dose
% works, the GM may allow the same nano to work on any
% patient with an identical problem.