These are directed energy weapons.

\section{Lasers}\label{sec:lasers}
%\addcontentsline{toc}{section}{Lasers}
Lasers are among the most versatile of beam weapons, with a wide range of offensive and defensive applications.

Lasers can be broadly classified by the effect on their target:

\textit{Dazzle} lasers cause temporary blindness.

\textit{Blinding} lasers cause permanent damage to eyesight or optics

\textit{High~-energy} lasers blind, and inflict physical burn damage.

While older laser weapons made use of chemical lasers, this technology has been made obsolete by solid~-state lasers which use a solid crystalline material as the lasing medium. Alternatively, some modern laser systems use free electron lasers, these are usually found on vehicle systems -- see p. TODO.

\subsection{Laser Dazzler}\label{subsec:laser_dazzler}
A laser dazzler is a low~-energy laser that fires a wide beam of coherent light. Dazzlers temporarily blind eyes andoptical sensors, and are designed for personal defense and riot control. That said, they can be deployed offensively by blinding a target such that they suffer an accident. In the case that such an accident is fatal, dazzlers leave no evidence\ldots unless the victim had laser sensors and recorded the attack.

A laser dazzler delivers a Vision~-based affliction attack against anyone struck. To be affected, the target must be looking at the laser. The victim gets a HT roll to resist, at the penalty noted on the weapon table; add +3 to HT if he is beyond 1/2D range. DR has no effect, but Protected Vision adds +5 to resist. A Nicitating Membrane adds +1 per level. Failure to resist inflicts Blindness (p. B125) for minutes equal to the margin of failure.

Laser dazzlers deliver cone attacks -- see \textit{Area and Spreading Attacks} (p. B413).

\subsubsection{Weapons}\label{subsubsec:laser_dazzler_weapons}
\textit{Dazzler Carbine:}\label{itm:dazzler_carbine} A long~-range dazzler weapon, most often used for police or covert operations.

\textit{Penlights, Flashlights, and Searchlights:} Most modern flashlights have a ``laser dazzle'' setting; see \textit{Flashlights} (p. \pageref{subsec:flashlights_searchlights}) for descriptions. The combat statistics are present below.

\subsubsection{Dazzle Mode}\label{subsubsec:dazzle_mode}
Any high~energy laser (see p. TODO) may be designed with a dazzle mode. Switching to or from this mode takes a Ready maneuver. When in dazzle mode, the laser fires a low~-power laser beam that is identical to the effect of a dazzler laser, except it does not have a cone effect -- it must strike the target's face or eyes. A HT-5 is needed to resist the affliciton. Dazzle mode uses up negligible power. The setting adds +0.1 CF to the laser.

\subsection{Blinding Lasers}\label{subsec:blinding_lasers}
These weapons emit a medium~-power laser beam that can cause permanent blindness, or fry optics, without burning flesh. The beam is wide enough that it need only be aimed at the target, not the eyes. 

Dedicated blinding lasers are generally rare, as high~-energy lasers are more effective. However, military active sensors, targeting systems, and electronic warfare systems that utilize lasers often incoporate a ``high~-power optical countermeasures'' mode that is designed to blind sensors (and eyes). 

A blinding laser delivers a Vision~-based affliction attack. Anyone hit who is looking toward the laser can be affected. The victim gets a HT-10 roll to resist (HT-7 past 1/2D range). Protected Vision adds +5 to resist; a Nicitating Membrane adds +1 per level.

Failure to resist inflicts crippling Blindness (p. B125).

\multicolinterrupt{
    \normalsize
    \begin{table}[H]
        \sffamily
        \hrule height 1pt\medskip
        \subsection{\textit{Dazzler Laser Weapons Table}}
        \noindent BEAM WEAPONS (PROJECTOR) (DX-4, or other Beam Weapons-4)
        \centering
        \small
        \rowcolors{1}{}{\colorweaponry}
        \begin{tabularx}{\linewidth}{lcXccXcXcXcXc}
            \textbf{Weapon} & \textbf{Damage} & \textbf{Acc} & \textbf{Range} & \textbf{Weight} & \textbf{RoF} & \textbf{Shots} & \textbf{ST} & \textbf{Bulk} & \textbf{Rcl} & \textbf{Cost} & \textbf{LC} & \textbf{Notes} \\
            Dazzler Carbine & HT-5 aff (3 yd) & 6 & 1,500/4,500 & 5/C & 1 & 9,000(3) & 6† & -2 & 1 & \$500 & 3 & [1] \\ 
            Laser Penlight & HT-4 aff (1 yd) & 6 & 100/300 & 0.1/A & 1 & 900(3) & 1 & -1 & 1 & \$3 & 4 & [1] \\
            Mini Laser Flashlight & HT-5 aff (1 yd) & 6 & 170/500 & 0.25/B & 1 & 3,600(3) & 1 & -1 & 1 & \$10 & 4 & [1] \\
            Heavy Laser Flashlight & HT-5 aff (1 yd) & 6 & 330/1,000 & 1/2B & 1 & 3,600(3) & 1 & -2 & 1 & \$20 & 4 & [1] \\
            Laser Searchlight & HT-5 aff (2 yd) & 12 & 7,000/20,000 & 10/C & 1 & 1,800(3) & 1 & -5 & 1 & \$500 & 4 & [1] \\
        \end{tabularx}
        \label{tab:dazzler_laser_weapons}
    \end{table}
}

\subsubsection{Weapons}\label{subsubsec:blinding_lasers_weapons}
\textit{Blinding Mode:} A high~-energy laser (below) may be designed with a Blinding Mode, enabling it to fire a medium~-power laser beam. Modify the laser's statistics as shown on the table below when using this mode. Changing to or from this mode requires a Ready maneuver. This mode adds +0.1 CF.

\textit{Military Ladar:} These are military sensor arrays that can focus laser energy into a beam powerful enough to function as a weapon. The weapon statistics of these arrays are given here; the sensor statistics are covered on p. \pageref{itm:tactical_ladar}.

\subsection{High~-Energy Laser}\label{subsec:high-energy_laser}
The most common form of laser weapon. These emit near~-infrared or visible coherent light in a narrow, tightly~-focused beam that can burn through armor or explode flesh into steam. The beam has a duration of only a few microseconds; the lasers cycle multiple times per second.

Lasers inflict lower damage than equivalent~-sized projectile weapons, particle beams, or plasma guns, but they're far more accurate and completely recoilless.

High~energy lasers are available in different sub~-types depending on the frequency of light used: infrared (below), blue~-green (below), and ultraviolet (p. TODO). All inflict tight~-beam burning damage.

Laser eye injuries are especially dangerous. If an eye takes enough laser damage to cripple it, the result is \textit{always} permanent crippling (giving the victim the One Eye disadvantage, or if he only has one eye, Blindness).

High~-energy laser beams are silent and invisible, but in dusty air, there will be a slight glow from incinerated dust particles.

Rain, fog, smoke, snow, and similar weather or atmospheric conditions interfere with all high~-energy lasers, adding extra DR to the target equal to the vision penalty (per yard). Thus,if a yard of smoke would be -10 to vision, then each yard gives DR 10; if every 100 yards of haze gives -1 to vision, then 1,000 yards provides DR 10.

A high~-energy laser beam can pass through material transparent to its particular frequency of light, which includes most glass, plastic canopies, etc. Increase the lasers armor divisor to (10) when it strikes glasses, visors, windows, etc. unless the material was specifically designed to be laser~-resistant. Almost all modern transparent armor \textit{is} laser~-resistant.

Mirrored surfaces are not effective against a high~-energy laser: any laser powerful enough to inflict damage destroys the mirror, ruining its reflectivity. However, if the mirror's reflectivity is capable of withstanding laser damage, then a shield~-sized mirror will provide its Defense Bonus vs. a visible~-light laser.

High~-energy lasers inflict tight~-beam burning damage with a (2) armor divisor. 

\begin{calloutbox}\label{callout:chem_infrared_lasers} %frametitle=Chemical Infrared Lasers
    %\addcontentsline{toc}{subsection}{Chemical Infrared Lasers}
    \subsection{Chemical Infrared Lasers}
    A few older high~-energy lasers are chemical lasers. They are continuous~-beam weapons powered by highly reactive, energetic and corrosive chemicals -- usually hydrogen~-fluorine or oxygen-iodine. Chemical lasers should be issued to robots or troops in sealed suits, as fumes from the exhaust inflict 1 HP of toxic damage per second to anyone within a yard of the weapon. Carrying a man-portable chem-laser poses similar risks to a flamethrower -- if the chemical tank is damaged, the spill can injure the wielder.
\end{calloutbox}

\subsubsection{Infrared Laser}\label{subsubsec:infrared_laser}
IR lasers emit a coherent beam of near~-infrared frequency light. They are the most common high~-energy laser, as they are more efficient to generate than other frequencies and propagate well in both air and space.

IR lasers inflict tight~-beam burning damage with a (2) armor divisor. They can't penetrate more than a few inches of water, which reduces their underwater range to 0/1.

\subsubsection{Option: Blue~-Green}\label{subsubsec:option_blue-green}
The standard laser light frequency for high~-energy laser weapons shown on the weapon table is red or near~-infrared light, but there are other alternatives. One of the most popular is the shorter blue~-green wavelengths. Blue~-green lasers require more power to generate, but permit greater ranges, and can also propagate underwater.

Any high~-energy laser (except chemical lasers) can be designed to use a blue~-green wavelength. Blue~-green lasers inflict the usual tight~-beam burn damage with the (2) armor divisor. Double the Range, but halve the RoF; treat each shot as consuming two shots for the purpose of power drain. Blue~-green lases can fire underwater.

A blue~-green laser's underwater range depends on the water's clarity. The maximum Range can never exceed 150 yards in crystal~-clear water, 60 yards in average water, or 15 yards in murky water. It is possible to fire into or out of water (out to normal ranges) as long as the maximum range \textit{through} water is not exceeded.

\multicolinterrupt{
    \begin{table}[H]
        \sffamily
        \hrule height 1pt\medskip
        \subsection{\textit{Blinding Laser Table}}
        \noindent BEAM WEAPONS (PROJECTOR) (DX-4, or other Beam Weapons-4)
        \centering
        \small
        \rowcolors{1}{}{\colorweaponry}
        \begin{tabularx}{\linewidth}{lcXccXcXcXcXc}
            \textbf{Weapon} & \textbf{Damage} & \textbf{Acc} & \textbf{Range} & \textbf{Weight} & \textbf{RoF} & \textbf{Shots} & \textbf{ST} & \textbf{Bulk} & \textbf{Rcl} & \textbf{Cost} & \textbf{LC} & \textbf{Notes} \\
            Blinding Mode & HT-10 aff & var. & var. & var. & var. & 10× & var. & var. & 1 & var. & var. & [1] \\ 
            Military LADAR & HT-10 aff & 24 & ×0.1/×0.3 & -- & 1 & -- & -- & -- & 1 & -- & -- & [2] \\
        \end{tabularx}
        \label{tab:blinding_laser}
    \end{table}
    [1] Use the high~-energy laser's statistics for everything noted as var., with the exception that each shot in blinding mode counts as one~-tenth of a normal shot (i.e., it has 10 times as many shots).
    
    [2] Multiply range shown by the sensor system's detection range, e.g., a ladar with 100~-mile range has a blinding laser range of 10/30 miles.

        \begin{table}[H]
        \sffamily
        \hrule height 1pt\medskip
        \subsection{\textit{High~-Energy Laser Table}}
        \noindent BEAM WEAPONS (PISTOL) (DX-4, other Beam Weapons-4, or Guns (Pistol)-4)
        \centering
        \small
        \rowcolors{1}{}{\colorweaponry}
        \begin{tabularx}{\linewidth}{lcXccXcXcXcX}
            \textbf{Weapon} & \textbf{Damage} & \textbf{Acc} & \textbf{Range} & \textbf{Weight} & \textbf{RoF} & \textbf{Shots} & \textbf{ST} & \textbf{Bulk} & \textbf{Rcl} & \textbf{Cost} & \textbf{LC} \\
            Heavy Laser Pistol & 4d(2) burn & 6 & 300/900 & 3.3/2C & 10 & 56(3) & 6 & -2 & 1 & \$2,400 & 3 \\ 
            Holdout Laser & 2d(2) burn & 3 & 100/300 & 0.35/B & 10 & 22(3) & 3 & -1 & 1 & \$300 & 3 \\ 
            Laser Pistol & 3d(2) burn & 6 & 200/600 & 1.5/C & 10 & 66(3) & 4 & -2 & 1 & \$1,100 & 3 \\ 
        \end{tabularx}
        \label{tab:high-energy_laser}
    \end{table}
}

\subsubsection{Option: Ultraviolet}\label{subsubsec:option_ultraviolet}
Some high~-energy lasers fire a beam in the near~-ultraviolet wavelength. An ultraviolet laser has superior range (in vacuum) compared to infrared or blue~-green lasers, but its beam is rapidly absorbed by atmosphere. The beam is invisible, but it ionizes air molecules when fired in atmopshere of greater than trace density, producing a visible green glow along its path.

An ultraviolet laser has triple the usual Range, but due to its lower efficiency, its Damage is halved. Treat half~-dice as a +2 modifier, e.g., 5d(2) becomes 2d+2(2). UV lasers are mainly used for space combat and on airless worlds. In atmosphere, the Range cannot exceed 500 yards divided by atmospheric pressure.

\subsubsection{Mounted Lasers}\label{subsubsec:mounted_lasers}
\textit{Area Defense Laser:}\label{itm:area_defense_laser} This is built to engage lightly armored targets, such as spacecraft and ballistic missiles, at a range of a few hundred miles.

\textit{Point Defense Laser:}\label{itm:point_defense_laser} This is a vehicle~-mounted system. It is designed to destroy soft targets like missiles, aircraft, and personnel at a range of several miles, with minimal collateral damage.

\textit{Semi~-Portable Laser:}\label{itm:semi-portable_laser} This continuous~-beam chemical~-powered weapon is the size of a heavy machine gun. Its chemical tank is separate, and has SM-2, DR 10, HP 12. If disabled, the chemical splash inflicts 2d corrosion damage over a 2~-yard radius.

\textit{Laser Cannon:}\label{itm:laser_cannon} A large vehicle~-mounted weapon. It is a standard spacecraft and air defense system.

\textit{Strike Laser:}\label{itm:strike_laser} A smaller version of the laser cannon, often used by fighter aircraft, and as a defensive weapon for armored vehicles or spacecraft.

\textit{Gatling Laser:}\label{itm:gatling_laser} A rapid~-fire laser weapon. Infantry use these on a tripod; they're also often vehicle mounted or used as ``small arms'' by powered troopers.

\subsubsection{Laser Pistols}\label{subsubsec:laser_pistols}
\textit{Heavy Laser Pistol:}\label{itm:heavy_laser_pistol} A bulky but rapid~-firing military~-style laser sidearm, often used as an alternative to a machine pistol.

\textit{Holdout Laser:}\label{itm:holdout_laser} A tiny weapon disguised as an innocuous object, such as a wrist communicator or pen. Its mechanism uses non~-metallic ceramics and exotic composites, so with the power cell removed, an ordinary scanner cannot distinguish it from a civilian electronic device.

\textit{Laser Pistol:}\label{itm:laser_pistol} The basic laser sidearm.

\subsubsection{Laser Rifles}\label{subsubsec:laser_rifles}
\textit{Chem Assault Laser:}\label{itm:assault_laser} This is an older, chemical~-pumped laser. It is most often used for microgravity combat. If its chemical power pack is attacked, it has SM-4, DR 10, HP 7; if disabled, it inflicts 1d corrosion damage in a 1~-yard radius.

\textit{Chem Laser Sniper Rifle:}\label{itm:laser_sniper_rifle} A bulky but accurate chemical laser rifle, used as a battlefield sniping weapon. If its chemical pack is attacked, it has SM-4, DR 10, HP 7; if disabled, it inflicts 1d corrosion damage in a 1~-yard radius.

\textit{Dinosaur Laser:}\label{itm:dinosaur_laser} A big laser sniper rifle, capable of stopping a battlesuit or a dinosaur (hence its nickname). Also called a ``heavy laser.'' These are mostly military weapons, but sometimes are used to hunt big game.

\textit{Laser Carbine:}\label{itm:laser_carbine} A compact ``assault'' version of the laser rifle, favored by vehicle crews and special opts teams. Its low bulk makes up for its lack of range.

\textit{Laser Rifle:}\label{itm:laser_rifle} The standard infantry combat laser, capable of full automatic fire. Quite common across the universe.

\textit{Survival Laser:}\label{itm:survival_laser} A carbine verison of the heavy laser pistol. Survival lasers are designed to be broken down into four pocket~-sized components, which take one minute to assemble/disassemble. Although it is not very powerful, it has excellent accuracy and only modest power drain.

\multicolinterrupt{
    \begin{table}[H]
        \hrule height 1pt\medskip
        % \subsection{\textit{Dazzler Laser Weapons Table}}
        \noindent BEAM WEAPONS (PISTOL) (DX-4, other Beam Weapons-4, or Guns (Rifle)-4)
        \centering
        \small
        \rowcolors{1}{}{\colorweaponry}
        \begin{tabularx}{\linewidth}{lcXccXcXcXcX}
            \textbf{Weapon} & \textbf{Damage} & \textbf{Acc} & \textbf{Range} & \textbf{Weight} & \textbf{RoF} & \textbf{Shots} & \textbf{ST} & \textbf{Bulk} & \textbf{Rcl} & \textbf{Cost} & \textbf{LC} \\
            % name & damage & acc & range & weight & rof & shots & st & bulk & rcl & \$ & LC \\ 
            Assault Laser & 4d(2) burn & 12+1 & 700/2,100 & 10/Dp & 1 & 40(5) & 7† & -5 & 1 & \$10,000 & 2 \\ 
            Laser Sniper Rifle & 5d(2) burn & 12+2 & 1,100/3,300 & 20/Dp & 1 & 20(5) & 10† & -8 & 1 & \$20,000 & 1 \\ 
            Dinosaur Laser & 8d(2) burn & 12 & 1,300/3,900 & 19/Dp & 1 & 35(5) & 10† & -5 & 1 & \$19,000 & 1 \\ 
            Laser Carbine & 5d(2) burn & 12 & 500/1,500 & 5.6/2C & 10 & 28(3) & 5† & -3 & 1 & \$4,600 & 2 \\ 
            Laser Rifle & 6d(2) burn & 12 & 700/2,100 & 8/Dp & 10 & 83(5) & 7† & -4 & 1 & \$8,000 & 2 \\ 
            Survival Laser & 4d(2) burn & 12 & 300/900 & 3.3/2C & 6 & 56(3) & 6† & -3 & 1 & \$2,400 & 3 \\ 
        \end{tabularx}\medskip
        
        \noindent GUNNER (BEAMS) (DX-4, other Gunner-4)
        \begin{tabularx}{\linewidth}{lcXcrccXcXrX}
            \textbf{Weapon} & \textbf{Damage} & \textbf{Acc} & \textbf{Range} & \textbf{Weight} & \textbf{RoF} & \textbf{Shots} & \textbf{ST} & \textbf{Bulk} & \textbf{Rcl} & \textbf{Cost} & \textbf{LC} \\
            % name & damage & acc & range & weight & rof & shots & st & bulk & rcl & \$ & LC \\ 
            Area Defense Laser & 6d×5(2) burn & 18 & 36,000/110,000 & 8,000/10Fp & 1 & 83(5) & 200M & -10 & 1 & \$2,000,000 & 1 \\ 
            Point Defense Laser & 3d×5(2) burn & 18 & 9,000/27,000 & 1,000/Fp & 1 & 66(5) & 70M & -10 & 1 & \$250,000 & 1 \\ 
            Semi~-Portable Laser & 6d(2) burn & 18 & 1,400/4,300 & 70/Ep & 10 & 100(5) & 18M & -8 & 1 & \$32,000 & 1 \\ 
            Gatling Laser & 6d×2(2) burn & 18 & 2,900/8,700 & 70/Ep & 4 & 100(5) & 18M & -8 & 1 & \$70,000 & 1 \\ 
            Laser Cannon & 6d×10(2) burn & 18 & 72,000/220,000 & 8,000/10Fp & 1 & 83(5) & 200M & -10 & 1 & \$4,000,000 & 1 \\ 
            Strike Laser & 6d×5(2) burn & 18 & 18,000/54,000 & 1,000/Fp & 1 & 66(5) & 70M & -10 & 1 & \$500,000 & 1 \\ 
        \end{tabularx}
        \label{tab:high-energy_laser_rifle_gunner}
    \end{table}
}

\subsection{Pulsed Energy Projectile (PEP) Lasers}\label{subsec:pep_lasers}
A high~energy laser can be modified so that it instead fires pulsed energy projectiles (PEP): a wider pulse of coherent light with an extremely short duration. A hit causes a surface explosion, concussion, and blunt trauma -- sometimes enough to knock a person down -- though it has less penetration than a standard laser.

The pulsed energy projectile option isn't listed on the weapon table; rather, it's available as an option that may be taken for any laser that does 10 or less damage, except for chemical lasers. Change the damage from burning to crushing, add the explosion damage modifier, and remove the armor divisor. The other statistics remain the same.

It is also possible to design a laser that can have a PEP setting. This is +1 CF; switching modes takes a Ready maneuver.

\section{Electrolasers}\label{sec:electrolasers}
%\addcontentsline{toc}{section}{Electrolasers}
Electrolasers use a pair of low~-power far~-ultraviolet laser beams to create an ionized path through the air, then transmit an electrical discharge that follows to the target. In effect, they are an electric stun gun that usese a laser beam instead of a wire. They're also called "zappers" or "stat guns."

\subsection{Low~-Power Electrolaser}\label{subsec:low-power_electrolaser}
These are non~-lethal weapons. They deliver both an electrical shock and a minor laser burn.

The laser beam inflicts 1d-3 burn damage. It needn't penetrate to carry the charge. Smoke, fog, rain, or clouds give extra DR equal to the visible penalty. For example, if rain gives a penalty of -1 per 100 yards, a target 200 yards away gets an extra DR 2.

An electrolaser's shock is a HT~-based affliction attack with a (2) armor divisor (each 2 DR on the location struck provides +1 to HT). Add +3 past 1/2D range. If the victim fails to resit, the shock stuns her. She may roll against HT every turn at the same penalty (but \textit{without} the DR bonus) to recover. Electrolasers also affect machines that are Electrical.

Electrolaser weapons produce a ``zap'' sound, no louder than a silenced pistol, and the beam is visible. They are most effective in dry climates. In humid conditions they are less accurate; the electrical bolt jumps off the path to paths of lower resistance. This gives a -2 to hit in moist, humid environments, and a -6 to hit in rain, drizzle, or heavy fog. In a vacuum or trace atmosphere, there is no air to ionize; the electrolaser only inflicts 1d-3 burn damage from the laser, with no additional linked effect.

\subsubsection{Electrolaser Weapons}\label{subsubsec:electrolaser_weapons}
\textit{Electrolaser Carbine:}\label{itm:electrolaser_carbine} This compact rifle is one of the most common stun weapons. They are standard in almost every police vehicle universe wide.

\textit{Electrolaser Pistol:}\label{itm:electrolaser_pistol} A wireless successor to dart~-firing electric stun guns. Another weapon standard in police (and prison guard) loadouts.

\textit{Heavy Electrolaser:}\label{itm:heavy_electrolaser} A heavy~-duty electrolaser used against armored foes or large animals. Its ultraviolet carrier beam causes a more severe burn than lower~-powered weapons, so it's best used on targets that have some protection.

\textit{Holdout Electrolaser:}\label{itm:holdout_electrolaser} A palm~-sized zapper. 

\textit{Underbarrel Electrolaser}\label{itm:underbarrel_electrolaser} This electrolaser is designed to be attached under the barrel of any weapon with Bulk -3 or more, providing a backup stun capability. Use the Bulk, ST, and sighting bonuses of the weapon it is installed in.

\textit{Semi~-Portable Electrolaser:}\label{itm:semi~-portable electrolaser} Also called a ``tripod zapper,'' this powerful long~-range electrolaser is usually mounted on a vehicle or tripod. Like the heavy electrolaser, its carrier beam can inflict nasty burns.

\subsection{Lethal Electrolasers}\label{subsec:lethal_electrolasers}
Any electrolaser may have an optional ``kill'' setting that uses up to two shots instead of one. It takes a Ready maneuver to change settings.

On ``kill'' the weapon transmits a higher~-amperage current. Any HT roll that fails by 5 or more triggers the Heart Attack mortal condition (p. B428). For electrical machines, a ``heart attack'' results in the target's electrical systems burning out until repaired.

Lethal electrolasers are all LC2.

\multicolinterrupt{
    \begin{table}[H]
        \hrule height 1pt\medskip
        \subsection{\textit{Electrolaser Table}}
        \noindent {\normalsize BEAM WEAPONS (PISTOL) (DX-4, other Beam Weapons-4, or Guns (Rifle)-4)}
        \centering
        \small
        % \rowcolors{1}{}{\colorweaponry}
        \begin{tabularx}{\linewidth}{lcXccXcXcXcX}
            \textbf{Weapon} & \textbf{Damage} & \textbf{Acc} & \textbf{Range} & \textbf{Weight} & \textbf{RoF} & \textbf{Shots} & \textbf{ST} & \textbf{Bulk} & \textbf{Rcl} & \textbf{Cost} & \textbf{LC} \\
            % name & damage & acc & range & weight & rof & shots & st & bulk & rcl & \$ & LC \\
            \rowcolor{\colorweaponry}
            Electrolaser Pistol & HT-4(2) aff & 4 & 40/80 & 2.2/C & 3 & 36(3) & 4 & -2 & 1 & \$1,800 & 4 \\
            \rowcolor{\colorweaponry}
            \textit{linked} & 1d-3 burn &  &  &  &  &  &  &  &  &  &  \\
            Holdout Electrolaser & HT-2(2) aff & 2 & 10/20 & 0.3/B & 1 & 22(3) & 3 & -1 & 1 & \$250 & 4 \\
            \textit{linked} & 1d-3 burn &  &  &  &  &  &  &  &  &  &  \\
        \end{tabularx}\medskip
        
        \noindent {\normalsize BEAM WEAPONS (RIFLE) (DX-4, other Beam Weapons-4, or Guns (Rifle)-4)}
        \begin{tabularx}{\linewidth}{lcXccXcXcXcX}
            \textbf{Weapon} & \textbf{Damage} & \textbf{Acc} & \textbf{Range} & \textbf{Weight} & \textbf{RoF} & \textbf{Shots} & \textbf{ST} & \textbf{Bulk} & \textbf{Rcl} & \textbf{Cost} & \textbf{LC} \\
            % name & damage & acc & range & weight & rof & shots & st & bulk & rcl & \$ & LC \\ 
            \rowcolor{\colorweaponry}
            Electrolaser Carbine & HT-4(2) & 8 & 160/470 & 3.7/2C & 3 & 72(3) & 4† & -4 & 1 & \$3,900 & 3 \\
            \rowcolor{\colorweaponry}
            \textit{linked} & 1d-3 burn &  &  &  &  &  &  &  &  &  &  \\
            Heavy Electrolaser & HT-6(2) aff & 8 & 400/1,100 & 20/Dp & 1 & 83(3) & 10† & -5 & 1 & \$20,000 & 3 \\
            \textit{linked} & 1d-2 burn &  &  &  &  &  &  &  &  &  &  \\
            \rowcolor{\colorweaponry}
            Underbarrel Electrolaser & HT-3(2) aff & 4 & 90/270 & 1.8/C & 1 & 66(3) & 4 & -- & 1 & \$1,300 & 4 \\
            \rowcolor{\colorweaponry}
            \textit{linked} & 1d-3 burn &  &  &  &  &  &  &  &  &  &  \\
        \end{tabularx}\medskip

        \noindent {\normalsize GUNNER (BEAMS) (DX-4, other Gunner-4)}
        \begin{tabularx}{\linewidth}{lcXccXcXcXcX}
            \textbf{Weapon} & \textbf{Damage} & \textbf{Acc} & \textbf{Range} & \textbf{Weight} & \textbf{RoF} & \textbf{Shots} & \textbf{ST} & \textbf{Bulk} & \textbf{Rcl} & \textbf{Cost} & \textbf{LC} \\
            % name & damage & acc & range & weight & rof & shots & st & bulk & rcl & \$ & LC \\ 
            \rowcolor{\colorweaponry}
            Semi~-Portable Electrolaser & HT-8(2) aff & 12 & 600/1,900 & 70/Dp & 10 & 100(5) & 18M & -8 & 1 & \$70,000 & 1 \\
            \rowcolor{\colorweaponry}
            \textit{linked} & 1d-1 burn &  &  &  &  &  &  &  &  &  &  \\
        \end{tabularx}\medskip
        \label{tab:electrolaser}
    \end{table}
}
% \normalsize

\section{Microwave Weapons}\label{sec:microwave_weapons}
%\addcontentsline{toc}{section}{Microwave Weapons}
Microwave weapons project electromagnetic beams with wavelengths longer than infrared light, but shorter than radio waves. Microwave beam weaponry is usually used to stun people or machines, depending on the frequency used.

\subsection{Microwave Area Denial (MAD)}\label{subsec:mad}
These ``pain beam'' weapons use microwaves to heat the surface of the target's skin to about 130\degree{}F, activating pain receptors without causing actual burning. The sensation is similar to touching a hot light bulb all over the surface of the body. MAD weapons are often used for riot control.

MAD beams deliver a HT-based affliction attack (modifier varying by weapon) with no armor divisor; add the target's DR to HT to resist. If they fail to resist, they suffer from the Agony affliction (p. B428) for as long as they are in the beam, and for one second afterward.

MAD beams are ranged cone attacks ~- see \textit{Area and Spreading Attacks} (p. B413).

\subsubsection{MAD Weapons}\label{subsubsec:mad_weapons}
\textit{Portable MAD:}\label{itm:portable_mad} A weapon the size of a light machine gun, used as a portable anti~-riot device. It is sometimes built into vehicles as a secondary weapon.

\textit{Tactical MAD:}\label{itm:tactical_mad} A large semi~-portable projector capable of breaking up a crowd at a thousand yards. It's usually tripod~-mounted or built into a vehicle.

\multicolinterrupt{
    \begin{table}[b]
        \hrule height 1pt\medskip
        \subsection{\textit{MAD Weapons Table}}
        \noindent BEAM WEAPONS (Projector) (DX-4, other Beam Weapons-4)
        \centering
        \small
        \rowcolors{1}{}{\colorweaponry}
        \begin{tabularx}{\linewidth}{lcXccXcXcXcX}
            \textbf{Weapon} & \textbf{Damage} & \textbf{Acc} & \textbf{Range} & \textbf{Weight} & \textbf{RoF} & \textbf{Shots} & \textbf{ST} & \textbf{Bulk} & \textbf{Rcl} & \textbf{Cost} & \textbf{LC} \\
            % name & damage & acc & range & weight & rof & shots & st & bulk & rcl & \$ & LC \\ 
            Portable MAD & HT-3 aff (1 yd) & 12 & 400/800 & 20/Dp & 1 & 300(5) & 10† & -5 & 1 & \$10,000 & 3 \\ 
        \end{tabularx}\medskip

        \rowcolors{1}{}{\colorweaponry}
        \noindent GUNNER (BEAMS) (DX-4, other Gunner-4)
        \begin{tabularx}{\linewidth}{lcXcrccXcXrX}
            \textbf{Weapon} & \textbf{Damage} & \textbf{Acc} & \textbf{Range} & \textbf{Weight} & \textbf{RoF} & \textbf{Shots} & \textbf{ST} & \textbf{Bulk} & \textbf{Rcl} & \textbf{Cost} & \textbf{LC} \\
            % name & damage & acc & range & weight & rof & shots & st & bulk & rcl & \$ & LC \\ 
            Tactical MAD & HT-4 aff (3 yd) & 18 & 600/1,200 & 70/Dp & 1 & 100(5) & 18M & -8 & 1 & \$70,000 & 3 \\ 
        \end{tabularx}
        \label{tab:mad_weapons}
    \end{table}
}

\subsection{Microwave Disruptors}\label{subsec:microwave_disruptor}
These generate a directional pulse that can scramble and overload electronics and electrical systems. 

Microwave disruptors project ranged cone attacks -- see \textit{Area and Spreading Attacks} (p. B413). Any target in the cone is struck by an affliction attack. This only afflicts electrical systems and those with the Electrical disadvantage. Make a HT roll or be shut down (or unconcious) for minutes equal to the margin of failure. Add +3 to resist beyond 1/2D range. The target's SM adds to the HT roll to resist. 

Microwave disruptors are contact agents that ignore DR unless the target is sealed. Disruption can propagate along radar or communication antennas, power lines, and communication cables. Treat a target with unshielded electronic access as unsealed.

Microwave disruptors come in holdout~-sized ``scramblers'' for sabotaging computers or other electronics, and heavier carbines and semi~-portable weapons for disabling robots and vehicular targets. Very large microwave disruptors are rare, since most large vehicles are sealed; EMP warheads (p. TODO) are more effective.

\subsubsection{Microwave Disruptor Weaponry}\label{subsubsec:microwave_disruptor_weaponry}
Most microwave disruptors are personal weapons requiring Beam Weapons (Projector) skill to use.

\textit{EMP Gun:}\label{itm:emp_gun} The basic portable microwave weapon, capable o stopping a robot or vehicle, or fying a room full of electronics. 

\textit{Pulse Carbine:}\label{itm:pulse_carbine} A more compact version of the EMP Gun, primarily used as an anti~-robot weapon.

\textit{Scrambler:}\label{itm:scrambler} A pocket holdout microwave pulse weapon.

\textit{Tactical Disruptor:}\label{itm:tactical_disruptor} A semi~-portable microwave cannon, usually tripod~-mounted or installed in a vehicle or robot. It requires Gunner (Beams) skill to use.

\multicolinterrupt{
    \begin{table}[H]
        \hrule height 1pt\medskip
        \subsection{\textit{High~-Power Microwave Weapon Table}}
        \noindent BEAM WEAPONS (Projector) (DX-4, other Beam Weapons-4)
        \centering
        \small
        \rowcolors{1}{}{\colorweaponry}
        \begin{tabularx}{\linewidth}{lcXccXcXcXcX}
            \textbf{Weapon} & \textbf{Damage} & \textbf{Acc} & \textbf{Range} & \textbf{Weight} & \textbf{RoF} & \textbf{Shots} & \textbf{ST} & \textbf{Bulk} & \textbf{Rcl} & \textbf{Cost} & \textbf{LC} \\
            % name & damage & acc & range & weight & rof & shots & st & bulk & rcl & \$ & LC \\ 
            EMP Gun & HT-3 aff (1 yd) & 6 & 90/270 & 1.8/C & 1 & 33(3) & 4 & -2 & 1 & \$650 & 2 \\ 
            Pulse Carbine & HT-4 aff (1 yd) & 12 & 160/480 & 5/2C & 1 & 28(3) & 5† & -3 & 1 & \$2,000 & 2 \\ 
            Scrambler & HT-2 aff (1 yd) & 3 & 40/120 & 0.3/B & 1 & 11(3) & 3 & -1 & 1 & \$120 & 2 \\ 
        \end{tabularx}\medskip

        \rowcolors{1}{}{\colorweaponry}
        \noindent {\normalsize GUNNER (BEAMS) (DX-4, other Gunner-4)}
        \begin{tabularx}{\linewidth}{lcXcrccXcXrX}
            \textbf{Weapon} & \textbf{Damage} & \textbf{Acc} & \textbf{Range} & \textbf{Weight} & \textbf{RoF} & \textbf{Shots} & \textbf{ST} & \textbf{Bulk} & \textbf{Rcl} & \textbf{Cost} & \textbf{LC} \\
            % name & damage & acc & range & weight & rof & shots & st & bulk & rcl & \$ & LC \\ 
            Tactical Disruptor & HT-8 aff (3 yd) & 18 & 600/1,200 & 70/Dp & 1 & 50(5) & 18M & -8 & 1 & \$32,000 & 1 \\ 
        \end{tabularx}
        \label{tab:high-power_microwave_weapon}
    \end{table}
}

\section{Particle Accelerators}\label{sec:particle_accelerators}
%\addcontentsline{toc}{section}{Particle Accelerators}

\subsection{Charged Particle Beams (``Blasters'')}
These particle beam weapons accelerate ionized electrons to near~-light velocities. They work best in an atmosphere -- the beam collides with air molecules, creating enough ions of the opposite charge so that the beam is self~-neutralized and remains coherent. The beam resembles a linear lightning bolt. In a vacuum, range is reduced, since the particles repel one another, but the beam is invisible. 

Blasters inflict burn damage with a (5) armor divisor and the surge damage modifier. In a vacuum or trace atmosphere, the beam's Acc is halved (round up) and the beam's Range is divided by 5.

This technology is still new and experimental and see limited functional models. 

\subsubsection{Mounted Weapons}\label{subsubsec:blasters_mounted_weapons}
\textit{Blaster Cannon:}\label{itm:blaster_cannon} A multi~-ton weapon installed in the turret or hull of a spacecraft or tank.

\subsection{Omni~-Blasters}\label{subsec:omni-blasters}
At +1 CF, a blaster may incorporate a stun setting, firing non~-lethal energy bolt similar in nature to an electrolaser beam. A stun setting feels like a powerful electrical shock. Unlike an electrolaser, a blast's stun bolt works in any environment. It takes one turn to ``switch to stun.''

When set to stun, the victim takes no damage, but must make a HT roll to resist falling unconscious. The HT roll is at a -1 penalty per die of damage the blaster usually inflicts, up to a maximum of -10. The victim adds one~-third of his DR to HT -- that is, the blaster gets a (3) armor divisor instead of its usual (5). A failed roll results in the victim falling unconscious for minutes equal to the margin of failure.

\multicolinterrupt{
    \begin{table}[H]
        \hrule height 1pt\medskip
        \subsection{\textit{Particle Beam Table}}
        \noindent GUNNER (BEAMS) (DX-4, other Gunner-4)
        \centering
        \small
        \rowcolors{1}{}{\colorweaponry}
        \begin{tabularx}{\linewidth}{lcXccXcXcXcX}
            \textbf{Weapon} & \textbf{Damage} & \textbf{Acc} & \textbf{Range} & \textbf{Weight} & \textbf{RoF} & \textbf{Shots} & \textbf{ST} & \textbf{Bulk} & \textbf{Rcl} & \textbf{Cost} & \textbf{LC} \\
            % name & damage & acc & range & weight & rof & shots & st & bulk & rcl & \$ & LC \\ 
            Blaser Cannon & 5d×10(5) burn sur & 15 & 30,000/90,000 & 4,000/10Fp & 1 & 20(5) & 160M & -10 & 1 & \$2,000,000 & 1 \\ 
        \end{tabularx}
        \label{tab:particle_beam}
    \end{table}
}

\section{Sonic Weapons}\label{sec:sonic_weapons}
%\addcontentsline{toc}{section}{Sonic Weapons}
Sonic beam weapons focus sound waves to hurt, incapacitate, or kill. Their range is multiplied by air pressure in atmospheres, up to a maximum of two times the listed range. They won't work in a vacuum or trace atmosphere unless physically touching the target (range C).

Sonic weapons will work underwater if designed for that medium. Underwater sonic weapons get double range, but their statistics are otherwise identical.

\subsection{Sonic Nauseators}\label{subsec:sonic_nauseators}
These weapons use acoustic heterodyning technology to process ordinary audible sound into a complex ultrasonic signal. The original sound is bound within the column of ultrasonic frequencies, becoming a tight beam that can travel hundreds of yards with no distortion or loss of volume. It causes pain, temporary hearing loss, and nausea. The weapons are not as reliable for self~-defense as other weapons, but are effective for riot control.

Nauseator beams are audible only to the target, and the beam is invisible. Nauseator range is multiplied by air pressure in atmospheres. It has no range in vacuum or underwater.

Nauseators emit a cone attack -- see \textit{Area and Spreading Attacks} (p. B413). The effect is a hearing~-based affliction attack that ignores DR, but has no effect on someone who cannot hear. A victim gets a HT roll to resist at the penalty noted for the weapon; add +5 for Protected Hearing and +3 beyond 1/2D range. Failure means suffering the disadvantages Hard of Hearing and the Moderate Pain (p. B428) irritating condition for minutes equal to the margin of failure on the target's HT roll. Failure by 5 or more results in Deafness (making the target immune to further attacks) and retching (p. B429), plus loss of sphincter control, resulting in the Bad Smell disadvantage until cleaned up. The weapons are sometimes nicknamed ``bowel disruptors'' due to these unpleasant consequences.

\subsubsection{Nauseator Weapons}\label{subsubsec:nauseator_weapons}
\textit{Nausea Carbine:}\label{itm:nausea_carbine} A short rifle~-sized weapon. 

\textit{Nausea Pistol:}\label{itm:nausea_pistol} A pistol~-sized version.

\textit{Tactical Nauseator:}\label{itm:tactical_nauseator} A tripod or vehicle~-mounted riot~-control weapon.

\subsection{Sonic Screamers}\label{subsec:sonic_screamers}
These lethal sonic weapons fire a beam that vibrates, heats, and even liquefies the target. Although the primary beam is an inaudible subsonic or ultrasonic frequency, the nickname comes from the tooth~-jarring whine produces as a side. Particularly baroque sonic designs may even have an audio trigger, modulating the user's battle cry or singing into an energy pulse!

Screamers deliver a cone attack -- see \textit{Area and Spreading Attacks} (p. B413) -- that ``shakes and bakes'' victims, doing corrosion damage. Living targets suffer the symptoms of Hard of HEaring (p. B109) if the damage exceeds 1/2 HP or Deafness if over 2/3 HP; this doesn't heal until the injury that caused it recovers.

\subsubsection{Screamer Weapons}\label{subsubsec:screamer_weapons}
\textit{Screamer Carbine:}\label{itm:screamer_carbine} A short, stubby weapon with a large, bell~-shaped aperture; this is the most common screamer. 

\textit{Screamer Pistol:}\label{itm:screamer_pistol} A pistol~-sized version, also called a ``sonic disruptor pistol.''

\textit{Tactical Screamer:}\label{itm:tactical_screamer} A heavy semi~-portable weapon used by power troops, or mounted on a tripod or vehicle. It is also called a ``tripod screamer.''

\subsection{Sonic Stunners}\label{subsec:sonic_stunners}
These advanced stunners fire a narrow, intense beam of ultrasonic sound that can shut down the target's nervous system. Unlike a nauseator, a sonic stunner can affect someone who is deaf.

A hit requires a HT roll to resist at the penalty noted for the weapon. Add +3 beyond 1/2D range, and +1 per 5 DR the victim has at the point struck. If she fails, she suffers the Unconsciousness (p. B429) incapacitating condition for minutes equal to the margin of failure. The beam is narrow enough that is a limb or extremity is hit, it is incapacitated instead of the victim being rendered unconscious.

\subsubsection{Sonic Stun Weapons}\label{subsubsec:sonic_stun_weapons}
\textit{Sonic Stun Cannon:}\label{itm:sonic_stun_cannon} A semi~-portable weapon, usually tripod~- or vehicle~-mounted. 

\textit{Dinosaur Stunner:}\label{itm:dinosaur_stunner} A powerful stunner capable of stopping an elephant.

\textit{Sonic Stinger:}\label{itm:sonic_stinger} A nonlethal alternative to the holdout laser, the stinger is a tiny sonic stunner that can be disguised as an everyday item or strapped to the wrist. Its construction means that when the power cells are removed, it is indistinguishable from a civilian electronic device to ordinary scanners.

\textit{Sonic Stun Pistol:}\label{itm:sonic_stun_pistol} A handgun~-sized sonic stunner. Some police departments issue them as standard sidearms.

\textit{Sonic Stun Rifle:}\label{itm:sonic_stun_rifle} A basic stun rifle.

\multicolinterrupt{
    \begin{table}[H]
        \hrule height 1pt\medskip
        \subsection{\textit{Sonic Weapon Table}}
        \noindent BEAM WEAPONS (PISTOL) (DX-4, other Beam Weapons-4, or Guns (Pistol)-4)
        \centering
        \small
        \rowcolors{1}{}{\colorweaponry}
        \begin{tabularx}{\linewidth}{lcXccXcXcXcX}
            \textbf{Weapon} & \textbf{Damage} & \textbf{Acc} & \textbf{Range} & \textbf{Weight} & \textbf{RoF} & \textbf{Shots} & \textbf{ST} & \textbf{Bulk} & \textbf{Rcl} & \textbf{Cost} & \textbf{LC} \\
            % name & damage & acc & range & weight & rof & shots & st & bulk & rcl & \$ & LC \\ 
            Sonic Stinger & HT-1(5) aff & 1 & 2/6 & 0.02/A & 1 & 18(3) & 1 & 0 & 1 & \$15 & 4 \\ 
            Sonic Stunner & HT-2(5) aff & 1 & 10/30 & 0.3/B & 1 & 22(3) & 3 & -1 & 1 & \$120 & 4 \\ 
            Sonic Stun Pistol & HT-3(5) aff & 3 & 30/100 & 1.8/C & 1 & 66(3) & 4 & -2 & 1 & \$650 & 4 \\ 
        \end{tabularx}\medskip

        \rowcolors{1}{}{\colorweaponry}
        \noindent {\normalsize BEAM WEAPONS (PROJECTOR) (DX-4, other Beam Weapons-4)}
        \begin{tabularx}{\linewidth}{lcXcrccXcXrX}
            \textbf{Weapon} & \textbf{Damage} & \textbf{Acc} & \textbf{Range} & \textbf{Weight} & \textbf{RoF} & \textbf{Shots} & \textbf{ST} & \textbf{Bulk} & \textbf{Rcl} & \textbf{Cost} & \textbf{LC} \\
            % name & damage & acc & range & weight & rof & shots & st & bulk & rcl & \$ & LC \\ 
            Nausea Carbine & HT-4 aff (1 yd) & 6 & 17/50 & 5/2C & 1 & 56(3) & 5† & -3 & 1 & \$2,000 & 4 \\ 
            Nausea Pistol & HT-3 aff (1 yd) & 3 & 9/27 & 1.8/C & 1 & 66(3) & 4 & -2 & 1 & \$650 & 4 \\ 
            Screamer Carbine & 4d cor (1 yd) & 6 & 33/100 & 5/2C & 1 & 56(3) & 5† & -3 & 1 & \$4,000 & 4 \\ 
            Screamer Pistol & 3d cor (1 yd) & 3 & 18/54 & 1.8/C & 1 & 66(3) & 4 & -2 & 1 & \$1,300 & 4 \\ 
        \end{tabularx}\medskip

        \rowcolors{1}{}{\colorweaponry}
        \noindent {\normalsize BEAM WEAPONS (RIFLE) (DX-4, other Beam Weapon-4, or Guns (Rifle)-4)}
        \begin{tabularx}{\linewidth}{lcXcrccXcXrX}
            \textbf{Weapon} & \textbf{Damage} & \textbf{Acc} & \textbf{Range} & \textbf{Weight} & \textbf{RoF} & \textbf{Shots} & \textbf{ST} & \textbf{Bulk} & \textbf{Rcl} & \textbf{Cost} & \textbf{LC} \\
            % name & damage & acc & range & weight & rof & shots & st & bulk & rcl & \$ & LC \\ 
            Dinosaur Stunner & HT-6(5) aff & 6 & 130/400 & 20/Dp & 1 & 83(3) & 10† & -5 & 1 & \$10,000 & 3 \\ 
            Sonic Stun Rifle & HT-4(5) aff & 6 & 60/180 & 5/2C & 1 & 56(3) & 5† & -3 & 1 & \$2,000 & 4 \\ 
        \end{tabularx}\medskip

        \rowcolors{1}{}{\colorweaponry}
        \noindent {\normalsize GUNNER (BEAMS) (DX-4, other Gunner-4)}
        \begin{tabularx}{\linewidth}{lcXcrccXcXrX}
            \textbf{Weapon} & \textbf{Damage} & \textbf{Acc} & \textbf{Range} & \textbf{Weight} & \textbf{RoF} & \textbf{Shots} & \textbf{ST} & \textbf{Bulk} & \textbf{Rcl} & \textbf{Cost} & \textbf{LC} \\
            % name & damage & acc & range & weight & rof & shots & st & bulk & rcl & \$ & LC \\ 
            Tactical Nauseator & HT-8 aff (3 yd) & 9 & 70/200 & 70/Dp & 10 & 100(5) & 18M & -8 & 1 & \$35,000 & 2 \\ 
            Tactical Screamer & 8d cor (3 yd) & 9 & 130/400 & 70/Dp & 10 & 35(5) & 18M & -8 & 1 & \$70,000 & 2 \\ 
            Sonic Stun Cannon & HT-8(5) aff & 9 & 230/700 & 70/Dp & 10 & 100(5) & 18M & -8 & 1 & \$32,000 & 2 \\ 
        \end{tabularx}
        \label{tab:sonic_weapon}
    \end{table}
}

\section{Plasma Weapons}\label{sec:plasma_weapons}

\subsection{Flamers}\label{subsec:flamers}
These weapons fire a low~-velocity jet of high temperature plasma. Hydrogen fuel is fed into a magnetic containment chamber, heated and compressed to form a plasma, then released as a continuous stream.

Flamers inflict burning damage, but not tight~-beam burning damage.

\subsubsection{Flamer Weapons}\label{subsubsec:flamer_weapons}
\textit{Assault Flamer:}\label{itm:assault_flamer} This rifle~-sized plasma weapon is often used by armored infantry involved in spaceship boarding actions and house~-to~-house fighting.

\textit{Hand Flamer:}\label{itm:hand_flamer} This large pistol is used as a military sidearm or a terror weapon.

\textit{Heavy Flamer:}\label{itm:heavy_flamer} An energy~-based flamethrower with a backpack power supply.

\textit{Semi~-Portable Flamer:}\label{itm:semi-portable_flamer} Also called a ``tripod flamer,'' this heavy, semi~-portable infantry weapon can be terrifying even to a fighter in heavy armor. A heavy flamer can be mounted on a tripod or carried by a soldier. 

\multicolinterrupt{
    \begin{table}[H]
        \hrule height 1pt\medskip
        \subsection{\textit{Plasma Flamer Table}}
        \small
        \rowcolors{1}{}{\colorweaponry}
        \noindent {\normalsize BEAM WEAPONS (PROJECTOR) (DX-4, other Beam Weapons-4)}
        \centering
        \begin{tabularx}{\linewidth}{lcXcrccXcXrX}
            \textbf{Weapon} & \textbf{Damage} & \textbf{Acc} & \textbf{Range} & \textbf{Weight} & \textbf{RoF} & \textbf{Shots} & \textbf{ST} & \textbf{Bulk} & \textbf{Rcl} & \textbf{Cost} & \textbf{LC} \\
            % name & damage & acc & range & weight & rof & shots & st & bulk & rcl & \$ & LC \\
            Assault Flamer & 5d burn & Jet & 50/150 & 5.6/2C & 1 & 28(3) & 5† & -3 & 1 & \$2,300 & 2 \\ 
            Hand Flamer & 4d burn & Jet & 30/90 & 3.3/2C & 1 & 56(3) & 6 & -2 & 1 & \$1,200 & 3 \\ 
            Heavy Flamer & 8d burn & Jet & 130/390 & 20/Dp & 1 & 35(5) & 10† & -5 & 1 & \$10,000 & 1 \\  
        \end{tabularx}\medskip

        \rowcolors{1}{}{\colorweaponry}
        \noindent {\normalsize GUNNER (BEAMS) (DX-4, other Gunner-4)}
        \begin{tabularx}{\linewidth}{lcXcrccXcXrX}
            \textbf{Weapon} & \textbf{Damage} & \textbf{Acc} & \textbf{Range} & \textbf{Weight} & \textbf{RoF} & \textbf{Shots} & \textbf{ST} & \textbf{Bulk} & \textbf{Rcl} & \textbf{Cost} & \textbf{LC} \\
            % name & damage & acc & range & weight & rof & shots & st & bulk & rcl & \$ & LC \\ 
            Semi~-Portable Flamer & 6d×3 burn & Jet & 150/450 & 70/Ep & 1 & 31(5) & 18M & -8 & 1 & \$35,000 & 1 \\ 
        \end{tabularx}
        \label{tab:plasma_flamer}
    \end{table}
}


\subsection{Plasma Guns}\label{subsec:plasma_guns}
These weapons use a laser to zap a hydrogen pellet into a high~-temperature plasma state. The plasma is magnetically confied for an instant, focused into a bolt, and then released at hypersonic velocities. When fired in atmopshere, the plasma bolt will ride a laser beam, which is used to create an evacuated channcel, ensuring the plasma does not explode immediately upon contact with air.

Plasma bolts have greater range, force, and accuracy than a flamer beam, but dissipate rapidly compared to laser or particle beams. However, they deliver a powerful explosive punch, thanks to their combination of thermal and kinetic energy effects, and are among the most energy~-efficient beam weapons in terms of sheer destructive energy. The ionized plasma bolt can also short out electrical systems. Plasma bolts are bright and create a loud report as the bolt burns through air, followed by a noisy explosion when it strikes the target.

The technology underlying plasma weapons limits them, currently, to heavy weapons. A plasma gun inflicts burning damage with the explosive damage modifier. This is \textit{not} tight~-beam burning damage. Unlike most beam weapons, plasma guns have significant recoil.

Plasma weapons use special power cells which include an integrated magazine of hydrogen fuel pellets. These cells are not interchangeable with those of other weapons or devices.

\subsubsection{Personal Plasma Guns}\label{subsubsec:personal_plasma}
\textit{Heavy Plasma Gun:}\label{itm:heavy_plasma_gun} Favored by powered troopers as an assault rifle, or as a squad support weapon.

\subsubsection{Mounted Plasma Guns}\label{subsubsec:mounted_plasma}
\textit{Plasma Cannon:}\label{itm:plasma_cannon} This heavy vehicle~-mounted weapon is a short~-ranged but effective alternative to particle beams and lasers. 

\textit{Plasma Gatling Cannon:}\label{itm:plasma_gatling_cannon} A light~-weight multibarrel plasma cannon with a high rate of fire.

\textit{Semi~-Portable Plasma:}\label{itm:semi-portable_plasma} A powerful weapon designed for use on a tripod mount or by heavy battlesuits.

\multicolinterrupt{
    \begin{table}[H]
        \hrule height 1pt\medskip
        \subsection{\textit{Plasma Gun Table}}
        \small
        \rowcolors{1}{}{\colorweaponry}
        \centering
        \noindent {\normalsize BEAM WEAPONS (RIFLE) (DX-4, other Beam Weapons-4, or Guns (Rifle)-4)}
        \begin{tabularx}{\linewidth}{lcXcrccXcXrX}
            \textbf{Weapon} & \textbf{Damage} & \textbf{Acc} & \textbf{Range} & \textbf{Weight} & \textbf{RoF} & \textbf{Shots} & \textbf{ST} & \textbf{Bulk} & \textbf{Rcl} & \textbf{Cost} & \textbf{LC} \\
            % name & damage & acc & range & weight & rof & shots & st & bulk & rcl & \$ & LC \\
            Heavy Plasma Gun & 3d×5(2) burn ex & 8+3 & 750/2,250 & 20/Dp & 3 & 20(5) & 15† & -6 & 2 & \$40,000 & 1 \\
        \end{tabularx}\medskip

        \footnotesize
        \rowcolors{1}{}{\colorweaponry}
        \noindent {\normalsize GUNNER (BEAMS) (DX-4, or other Gunner-4)}
        \begin{tabularx}{\linewidth}{lcXcrccXcXrX}
            \textbf{Weapon} & \textbf{Damage} & \textbf{Acc} & \textbf{Range} & \textbf{Weight} & \textbf{RoF} & \textbf{Shots} & \textbf{ST} & \textbf{Bulk} & \textbf{Rcl} & \textbf{Cost} & \textbf{LC} \\
            % name & damage & acc & range & weight & rof & shots & st & bulk & rcl & \$ & LC \\ 
            Plasma Cannon & 6d×25(2) burn ex & 12 & 7,500/22,500 & 5,000/10Fp & 1 & 40(5) & 240M & -10 & 2 & \$2,000,000 & 1 \\
            Plasma Gatling Gun & 6d×5(2) burn ex & 12 & 1,500/4,500 & 250/5Ep & 10 & 100(5) & 50M & -9 & 2 & \$320,000 & 1 \\
            Semi~-Portable Plasma Gun & 20d(2) burn ex & 12 & 1,000/3,000 & 70/Ep & 3 & 100(5) & 27M & -8 & 2 & \$140,000 & 1 \\
        \end{tabularx}
        \label{tab:plasma_gun}
    \end{table}
}