This section presents the gases and drugs most commonly used in combat, including lethal and nonlethal biochemical weapons, as well as chemical obscurants.

\section{Gases and Clouds}\label{sec:gases_clouds}
These come in varieties, from sleep gas an nerve gas to smoke and prismatic smokes. They create a cloud with a radius depending on the dispersal mechanism (see below). Chemical clouds may disperse within a few seconds or linger for minutes, depending on the wind. Most chemical clouds last for 300 seconds before dispersing; in winds of one mile per hour or more, divide this duration by the wind speed in mph. Most chemicals have no effect once dispersed, but some virulent poison gases cause injury even when greatly diluted.

The usual dispersion methods are a biochemical warhead (p. \pageref{tab:biochemical_aerosol}), an aerosol spray (p. \pageref{itm:pocket_aerosol}), or a vortex ring projector (p. \pageref{sec:vortex_ring_projectors}).

\subsection{Riot Gas}\label{subsec:riot_gas}
A non~-lethal incapacitating gas often used for crowd control. Any living being within the cloud who breathes the gas must make a HT-4 roll to resist every second. If the roll fails, he is nauseated (p. B428) for as long as he remains in the cloud. If it fails by 5 or more, he will become violently ill, retching (p. B429) for as long as he remains in the cloud; after leaving it, he will be nauseated for minutes equal to his margin of failure. \$2 per dose. LC3.

\subsection{Musk}\label{subsec:musk}
This malodorous fluid boasts a chemical formula similar to skunk oil. Highly persistent and almost impossible to wash away, it is used by police to mark demonstrators or fleeing suspects, and can also be a self~-defense weapon! Anyone sprayed suffers the Bad Smell disadvantage. The effects wear off after two weeks. Each hour of washing with detergents can reduce the duration of the stench by one day. A sealed suit protects the wearer but not the suit. \$2 per dose. LC4.

\subsection{Nerve Gas, Lethal}\label{subsec:nerve_gas_lethal}
Nerve gases are aerosolized liquids which disrupt the enzyme that transmits nerve signals. After exposure, the nerves become uncontrollable, resulting in a loss of motor function, breathing problems, pain, vomting, convulsions, and death.

This is an area~-effect contact agent with no delay and a HT-6 roll to resist (HT-3 if touching a contaminated area after the initial attack). Failure to resist inflicts 1d toxic damage. This is repeated at one~-minute intervals until six cycles have passed.

Loss of 1/3 HP results in coughing and the Neurological Disorder (Mild) disadvantage. Loss of 1/2 HP results in being nauseated plus the Neurological Disorder (Severe) disadvantage. Loss of 2/3 HP adds the Neurological Disorder (Crippling) disadvantage. The victim suffers only one disorder due to the nerve gas, with the severity increasing as she loses HP. The severity of the disorder is decreased as the victim recovers HP, and the disorder is removed when the HP lost has recovered to less than 1/3 HP. \$10 per dose. LC0.

\subsection{Sleep Gas}\label{subsec:sleep_gas}
An advanced sedative, such as an engineered variant of the heroin molecule, mixed with a skin~-penetrating agent. It causes rapid incapacitation. It is a contact agent that requires a HT-6 roll to resist. Failure results in unconsciousness lasting for minutes equal to the margin of failure, followed by ordinary sleep. \$0.50 per dose. LC2.

\subsection{Smoke}\label{subsec:smoke}
Smoke is used to obscure or mark an area. Screening smoke is white, gray, or sand~-colored and gives a -10 penalty for visually aimed attacks or sighting through them (see Obscure, p. B72); it also blocks ladar. Smoke clouds take one second per five yards of burst radius to form. They linger for one to four minutes, depending on weather conditions.

\textit{Colored Smoke:}\label{itm:colored_smoke} Used to mark targets or landing zones, but also difficult to see through (-7 penalty). \$0.1 per dose.

\textit{Hot Smoke:}\label{itm:hot_smoke} Has the same effects as normal smoke. It also penalizes Infravision, Hyperspectral Vision, and Night Vision. \$0.15 per dose. LC4.

\textit{Prism Smoke:}\label{itm:prism_smoke} Has the same effects as hot smoke, but also blocks most lasers. It has no effect on X~-ray or gamma~-ray lasers. \$0.2 per dose. LC4.

\textit{Electromagnetic Smoke:}\label{itm:electromagnetic_smoke} Has the same effects as hot smoke, but is also effective against Radar and Imaging Radar. \$0.3 per dose. LC4.

\subsection{Anti~-Tangler Aerosol}\label{subsec:anti-tangler_aerosol}
This dissolves stick foam (tangler) bonds in one second. \$1 per dose. LC4.

\subsection{Mask}\label{subsec:mask}
This agent neutralizes a wide spectrum of signature traces left behind by living beings. Any Forensics roll to detect chemical traces left by an individual or to track people by scent suffers a penalty of -6 if the trail passes through a Masked area. The masking agent itself is easily identified and tacked, making it somewhat less helpful to spray yourself with it! \$30 per dose. LC2.

\subsection{Paralysis Gas}\label{subsec:paralysis_gas}
This is an advanced nerve gas. It is a nonlethal area contact agent. For every turn spent in a para~-gas cloud, the victim must make a HT-6 roll to resist. If they fail by 1 or 2, they fall down and cannot move that turn. If they fail by 3 or more, they fall and are paralyzed for minutes equal to the margin of failure. On a critical failure, the paralysis gas causes 1d damage and results in a coma (p. B429). \$10 per dose. LC2.

\subsection{Pheromone Spray}\label{subsec:pheromone_spray}
Pheromone spray is a biochemical agent which enhances sexual attractiveness to members of the same species; aliens, Ravens, and uplifted animals are almost never affected. It is a respiratory agent that requires a HT-2 roll to resit. Failure results in the Lecherousness (CR 9) disadvantage for as long as the victim is in the cloud, plus minutes equal to the margin of failure. \$20 per dose. LC3.

\subsection{Radiant Prism}\label{subsec:radiant_prism}
A combination of prism and electromagnetic smoke. It lasts half as long, but also impairs infrared~- and radar~-aimed attacks or sighting (-5 penalty). If this smoke is breathed without a filter, it inflicts one point of damage per second. \$3 per dose. LC3.

\section{Foams and Liquids}\label{sec:foams_liquids}
These agents may be dispensed by liquid projectors or oin biochemical liquid warheads.

\subsubsection{Firefoam}\label{subsubsec:firefoam}
These fire~retardant chemicals put out any fire dealing 2d damage or less within its area of effect, and temporarily reduces the damage of larger fires by 2d for 3d seconds. \$1 per dose.

\subsubsection{Metal Embrittlement Agent (MEA)}\label{subsubsec:mea}
This category of chemical agents induce rapid corrosion. Each agent is designed to weaken a specific metal, inflicting 3d corrosion damage per hour to any object mostly made of that alloy, or with exposed vital parts made of it. If an SM+2 or larger object is completely within the area of effect, multiply the damage by the object's SM. The effect continues for 12 hours or until the object is decontaminated. \$5 per dose. LC2.

\section{Poisons}\label{sec:poisons}
Poisons may also be delivered by a hypo or by drug rounds, or as a contact poison (below).

\subsection{Nerve Poison}\label{subsec:nerve_poison}
This is also available as a drug -- a single dose injected into the body (by hypo, needler, etc.) requires a HT-7 roll to resist. Failure inflicts 1d toxic damage. This is repeated at one~-minute intervals, until six cycles have passed.

Loss of 1/3 HP results in coughing and the Neurological Disorder (Mild) disadvantage. Loss of 1/2 HP results in being nauseated plus Neurological Disorder (Severe) disadvantage. Loss of 2/3 HP adds the Neurological Disorder (Crippling) disadvantage. The victim suffers only one disorder due to the nerve poison, with the severity increasing as he loses HP. The severity of the disorder is decreased as the victim recovers HP, and the disorder is removed when the HP lost is recovered to less than 1/3 HP. \$10 per dose. LC0.

\subsection{Sleep Poison}\label{subsec:sleep_poison}
A sleep dose for hypnos and dart guns is available. The victim must roll vs. HT-6.

Failure results in the subject becoming drowsy (p. B428), while failure by 5 or more results in unconsciousness, lasting for minutes equal to the margin of failure. \$0.50 per dose. LC2.

\subsection{Contact Poisons}\label{subsec:contact_poisons}
Contact versions of both nerve and sleep poisons may be placed on a blade (but not a vibroblade), smeared on a flat surface such as a doorknob, etc. As contact poisons, these are less effective. The HT roll not to succumb is at +2. Contact versions cost 10 times as much. If applying the poison in haste as a Ready maneuver (otherwise taking a minute per application), roll against DX or Poison skill to avoid accidentally dosing yourself. LC1.

\section{Metabolic Nanoweapons}\label{sec:metabolic_nanoweapons}
These nanomachines are designed to enter a living body and wreck havoc. They won't effect someone with immunity to metabolic hazards, such as a machine. Metabolic nanoweapons can be delivered the same way as any other poison:

\textit{Blood Agent:} This is a liquid spray that must enter a mucous membrane (eyes, mouth, open wound, etc.) to have effect. Use the \textit{Blood Agent} rules (p. B437). Double normal cost.

\textit{Contact Agent:} A nanoweapon mist designed to penetrate skin. Double cost for a gel that may be smeared onto an object (takes 1 minute, but may applied quickly with a Ready maneuver with a successful roll against DX or Poisons skill; failure means you dose yourself), 10 times normal cost as a gas. Use \textit{Contact Agent} rules (p. B437).

\textit{Digestive Agent:} A pill that can be dissolved in food or drink. Use the \textit{Digestive Agent} rules (p. B437). Normal cost.

\textit{Follow~-Up Poison:} The nanoweapon must be injected, often via a hypo or drug projectile. Use the \textit{Follow~-Up Poison} rules (p. B437). Normal cost.

\textit{Respiratory Agent:} A mist of active nanoparticles that must be breathed to have effect. Use the \textit{Respiratory Agent} rules (p. B437). Five times normal cost.

\subsection{Nanoburn}\label{subsec:nanoburn}
A nanotech nerve agent using a suspension of nanomachines designed to invade the body and break down bodily functions. Nanoburn is effective against all carbon~-based life forms. A HT~-6 roll is required to avoid being paralyzed for three minutes times the margin of failure. If paralyzed, the victim takes 1d-1 toxic damage every three minutes over the next 30 minutes. Normal nerve poison antidotes are ineffective, but someone more skilled could possibly create a targeted cure (likely requiring a difficult skill roll). \$5 per dose. LC1.

\subsection{Nanotracers}\label{subsec:nanotracers}
These nanomachines function like a homing beacon (p. 105) except that they diffuse within the body. They are very difficult to remove without blood filtration (which requires a life support unit).

It takes one minute for nanotracers to spread through the body before they can begin signaling. They may use a radio signal, or they may cause the body to exude coded chemical cues which can be tracked by appropriate chemsniffers or someone with Discriminatory Smell. These will persist for a day or more, giving a +5 bonus to any tracking rolls to anyone who knows what the cues are and can detect them.

Diagnostic nano can also find nanotracers: roll each hour of searching, at the penalties listed above. If diagnostic nano has identified them, Aegis nano can automatically destroy them. \$100 per dose.