\section{Warbots and Combat Androids}\label{sec:warbots_combat_androids}
A warbot is a fighting machine designed to replace soldiers and supplemental combat vehicles.

A combat android is a humanoid machine that can use the same equipment and facilities as ordinary soldiers. 

\subsection{Combat Android}\label{subsec:combat_android}
\hfill \large{\textbf{371 points}}\normalsize

This is a humanoid combat machine, strong and heavily armored. \\

\begin{hangparas}{1em}{1}

    \textbf{Attributes:} ST+10 [100]; DX+3 [60]; HT+2 [20].

    \textbf{Secondary Characteristic Modifiers:} None.

    \textbf{Advantages:} Absolute Direction [5]; Detect (Radio, Lasers, and Radar; Signal Detection, +0\%) [20]; Discriminatory Hearing [15]; Doesn’t Breathe [20]; Hyperspectral Vision [25]; Machine [25]; Sealed [15]; Silence 1 [5]; Temperature Tolerance 20 (-85°F to 210°F) [20]; Ultrahearing [5]; Vacuum Support [5]. 60 points chosen from among Ambidexterity [5], Appearance [var.], Combat Reflexes [15], Enhanced Time Sense [45], High Pain Threshold [10].

    \textbf{Perk:} Accessory (Microframe computer) [1].

    \textbf{Disadvantages:} Electrical [-20]; Restricted Diet (Very Common, power cells) [-10].
    
\end{hangparas}

\subsubsection{Lenses}\label{subsubsec:combat_android_lenses}
Select \textit{one} of these model age lenses. Then choose a machine intelligence lens (p \pageref{sec:machine_intelligence_lenses}) and biomorphic lens (p. \pageref{sec:biomorphic_lens}), and consider one of the optional lenses below.\\

\begin{hangparas}{1em}{1}
    \textit{Old Model} (+145 points): Add DR 30 [150]; Maintenance (one person, weekly) [-5]. \$300,000, 150-300 lb., 2D/8 hr. LC2.

    \textit{Modern Model} (+231 points): Add DR 45 [225], Maintenance (one person, bi~-weekly) [-3], Reduced Consumption 2 [4], and Telescopic Vision 1 [5]. \$200,000, 100~-300 lb., 2D/24hr. LC2.
    % \textit{Cutting Edge Model} (+329 points): Add DR 45

\end{hangparas}
\subsubsection{Optional Lenses}\label{subsubsec:combat_android_optional}
\begin{hangparas}{1em}{1}
    \textit{Combat Exoskeleton} (-20 points): The robot resembles a metallic skeleton. Add Numb [-20], -0.1 CF.

    \textit{Infiltrator} (+40 points): The robot is covered with living flesh and appears human. Add 30 (outer layer)(Ablative, -80\%)[30] and Mimicry [10]. +0.2 CF.

    \textit{Chameleon} (+21 points): Add Chameleon 3 (extended, Infraviion, and Ultraviion, +40\%) [21]. +0.02 CF.

    \textit{Nuclear~-Powered} (+20 points): Add Doesn't Eat or Drink [10]; \textit{remove} Restricted Diet (Very common, power cells) [-10]. +0.1 CF.

    \textit{Weapon Mount} (+2 points): Add Extra Arm 1 (weapon Mount, -80\%) [2]. +0.02 CF.\\
\end{hangparas}

\subsection{Warbot}\label{subsec:warbot}
\hfill\large \textbf{290 points}\normalsize

The warbot is a nonhumanoid fighting machine the size of a subcompact car. It weighs half a ton (without weapons) and is available in submarine, walking tank, and aircraft versions. All models have a pair of manipulator arms.\\

\begin{hangparas}{1em}{1}
    \textbf{Attribute Modifiers:} ST+15 (Size, -30\%)[105]; DX+2 [40].

    \textbf{Secondary Characteristic Modifiers:} SM+3; HP+15 (Size, -30\%) [21]; Per+5 [25].

    \textbf{Advantages:} Extra Arms 3 (Weapon Mount, -80\%) [6]; Hyperspectral Vision [25]; Lifting ST +15 (Size, -30\%) [32] Machine [25]; Payload 5 [5]; Protected Senses (Hearing, Vision) [10]; Radiation Tolerance 5 [10]; Sealed [15].
    
    \textbf{Perk:} Accessory (Microframe computer) [1].
    
    \textbf{Disadvantages:} Electrical [-20]; Restricted Diet (Very Common, E cell) [-10].
    
    \textbf{Availability:} \$200,000, 1,000 lbs. \textit{plus} the cost of its brain. LC2.
\end{hangparas}

\subsubsection{Lenses}\label{subsubsec:warbot_lenses}
Select \textit{one} of these model age lenses, plus a configuration lens. Then choose a machine intelligence lense (p. \pageref{sec:machine_intelligence_lenses}).

\begin{hangparas}{1em}{1}
    \textit{Old Model} (+115 points): Add DR 50 (Cannot wear armor, -40\%) [150], Maintenance (3 person, weekly) [-15], and Numb [-20].

    \textit{Modern Model} (+229 points): Add DR 75 (Cannot wear armor, -40\%) [225], Maintenance (one person, weekly) [-5], Reduced Consumption 2 [4], and Telescopic Vision 1 [5].
\end{hangparas}

\subsubsection{Configuration Lenses}\label{subsubsec:warbot_config}
Select \textit{one} of these lenses.

\begin{hangparas}{1em}{1}
    \textit{Submarine} (+62 points): Basic Move becomes Water Move; ground Move is 0. Add Absolute Direction [5], Aquatic [0], and Enhanced Move (Water) 1 [20], Pressure Suppot 1 [5], and Sonar (Increased Range 10×, +30\%; LPI +10\%; Targeting, +20\%) [32].

    \textit{Walking Tank} (+87 points): An insectoid ground combat machine. Add Absolute Direction [5], Enhanced Move 1 (Ground) [20], Extra Legs (4 legs) [5], Radar (Increased Range 10×, +30\%; LPI, +10\%; Multi~-Mode, +50\%; Targeting, +20\%) [42], Super Jump 1 [10], and Vacuum Support [5].

    \textit{Vertol} (+142 points): This robot can fly and hover using ducted fans. Basic Move becomes Air Move; ground Move is 0. Add 3D Spatial Sense [10], Aerial [0], Enhanced Move (Air) 3 [60], Flight (Small wings, -10\%) [36], Noisy 3 [-6], and Radar (Increased Range 10¥, +30\%; LPI, +10\%; Multi-Mode, +50\%; Targeting, +20\%) [42].

    \textit{Vertol (Contragrav)} (+140 points): The machine uses contragravity gwhel~-generators for lift and thrust. Its Basic Move becomes Air Move; ground Move is 0. Add Aerial 0], [Enhanced Move (Air) 3 [60], Flight (Planetary, -5\%) [38], and Radar (Increased Range 10¥, +30\%; LPI, +10\%; Multi-Mode, +50\%; Targeting, +20\%) [42]. +0.5 CF.

\end{hangparas}

\section{Robot Weapons}\label{sec:robot_weapons}
Robotic missiles are designed to destroy the target in a self~-destructive attack. 
%Robot mines are simple automated weapons are simple automated weapons that wait for targets to appear -- sometimes for years or millenia -- before making their attack

\subsection{Genius Missile}\label{subsec:genius_missile}
The most advanced homing missiles are small, autonomous combat robots. They seek out and destroy their targets using programmed tactics such as loitering and stealthy low~-altitude approaches. In game rules they're trained animals. 

Instructing a genius missile requires an Artillery (Guided Missile) skill roll. Use the guidelines on p. B458 for what the missile can do. Missiles are very good at recognizing sensory profiles of particular targets, and can receive new target information and other updates through their communication links.

Genius missiles are also useful as reconnaissance machines.

\subsection{Hunter Missile}\label{subsec:hunter_missile}
An arm~-sized missile powered by a turbojet engine. It can fly at up to 1,000 mph, but can't slow down below 1/4 its speed. A hunter missile's payload may be any 64mm warhead. It can be fired from a 64mm missile launcher, such as the IML or MLAWS (p. \pageref{subsubsec:infantry_missile_launcher}). It flies for one minute and then will crash and self~-destruct.

A hunter missile uses a low~-probability intercept multi~-mode radar (2,000~-yard range) as its main sense. It can also detect laser, radar, and radio emissions and use that to find targets. It can receive command updates via radio, and use inertial guidance to fly to map coordinates.

The hunter missile's maximum straight~-line range is 16 miles.\\

\begin{hangparas}{1em}{1}
    \textbf{ST} 3; \textbf{DX} 14; \textbf{IQ} 5; \textbf{HT} 12.

    \textbf{HP} 6; \textbf{Will} 5; \textbf{Per} 12; \textbf{Speed} 6; \textbf{Dodge} 9; \textbf{Move} 0 (Ground).

    SM-4; 5 lb.

    \textbf{Traits:} Absolute Direction; Aerial; AI; Automaton; Blindness; Deafness; Detect (Lasers, Radio, and Radar, Signal Detection); Electrical; Enhanced Move 2 (Air speed 480); Flight (Cannot Hover; Limited Use, Fast Reload, 1 minute; Air Move 120); Injury Tolerance (No Head, No Neck); Mute; No Manipulators; No Sense of Taste/Smell; Noisy 4; Numb; Payload 3; Radar (LPI, Multi-Mode); Radio (Burst, Secure).

    \textbf{Cost:} \$500. LC2.

\end{hangparas}

\subsection{Striker Missile}\label{subsec:striker_missile}
A larger, smarter, and faster version of the hunter missile. It has a maximum speed of 2,000 mph and a maximum range of 32 miles. Its radar has a 4,000~-yard range, but it can turn that off and use Hyperspectral Vision instead. A striker missile’s Payload may be any 100mm warhead. It can be fired from any 100mm missile launcher such as the Tactical Missile Launcher (p. \pageref{subsubsec:tml_100mm}).\\

\begin{hangparas}{1em}{1}
    \textbf{ST} 6; \textbf{DX} 14; \textbf{IQ} 6; \textbf{HT} 12.
    
    \textbf{HP} 12; \textbf{Will} 5; \textbf{Per} 12; \textbf{Speed} 6; \textbf{Dodge} 9; \textbf{Move} 0
    (Ground).
    
    SM -2; 17 lb.
    
    \textbf{Traits:} Same as Hunter Missile except delete Blindness, add Hyperspectral Vision, upgrade to Enhanced Move 3 (Air speed 480), and give Radar (Increased Range ×2).
    
    \textbf{Skills:} Aerobatics-10, Observation-11.
    
    \textbf{Cost:} \$3,400. LC1.
\end{hangparas}

\subsection{Floater Missile}\label{subsec:floater_missile}
Similar to the striker Missile, but its reactionless thrusters and contragravity, gwhel~-generator technology enhance maneuverability and range (320 miles).\\

\begin{hangparas}{1em}{1}
    \textbf{ST} 3; \textbf{DX} 14; \textbf{IQ} 6; \textbf{HT} 12.
    
    \textbf{HP} 6; \textbf{Will} 6; \textbf{Per} 13; \textbf{Speed} 8; \textbf{Dodge} 11; \textbf{Move} 0 (Ground).
    
    SM -4; 5 lbs.
    
    \textbf{Traits:} Absolute Direction; Aerial; AI; Automaton; Blindness; Deafness; Detect (Lasers, Radio, and Radar, Signal Detection); Electrical; Enhanced Move 2 (Air speed 480); Flight (Limited Use, Fast Reload, 10 minutes; Air Move 120); Injury Tolerance (No Head, No Neck); Mute; No Manipulators; No Sense of Taste/Smell; Noisy 4; Numb; Payload 3; Radar (LPI, Multi-Mode); Radio (Burst, Secure).
    
    \textbf{Skills:} Aerobatics-12, Observation-11.
    
    \textbf{Cost:} \$5,000. LC1.
\end{hangparas}

\subsection{Devourer Swarm}\label{subsec:devourer_swarm}
These swarmbots have small diamond jaws; a swarm can chew through almost any barrier or armor, given time. They inflict 1d(2) corrosion damage per second to anyone caught within the swarm. This is considered an area~-effect attack, and only sealed DR will protect against it. \$8,000 per square yard. LC1.

\subsection{Gremlin Swarm}\label{subsec:gremlin_swarm}
This swarm is equipped with tiny drills and cutters. It is programmed to crawl inside electronic or mechanical devices, then jam up the works by slicing through wires, eating circuits, and so on. Only sealed machinery or electronics, or devices lacking mall moving parts, will be safe. The sabotage is not immediately obvious.

Each square yard of swarm does one point of damage per turn to unsealed machinery, ignoring armor DR. The machinery acquires a malfunction number (p. B407) or 17, with an extra -1 each time it loses 10\% of its HP. Check nonweapon devices for malfunction when they are turned on and each minute they are in use.

Damage caused by gremlins doesn't physically destroy an object, but is treated like other damage for repair purposes. \$2,000 per square yard. LC2.

\subsection{Sentry}\label{subsec:sentry}
These microbots are equipped with weapons optimized for combating other microbots. Each hex inflicts 2d damage per turn on other microbot swarms. \$5,000 per square yard. LC3.

\subsection{Stinger Swarm}\label{subsec:stinger_swarm}
These microbots have stinging needles with soporific venom. The swarm does one point of Fatigue damage per second to living beings (only) in contect with it unless they have Sealed protection. \$1,500 per square yard. LC2.

\subsection{Terminator Swarm}\label{usbsec:terminator_swarm}
These microbots have tiny jaws or poison needles. The swarm does one point of toxic damage per turn to living beings (only) in contact with it, unless they have Sealed protection. \$1,500/square yard. LC1.