In combat, any edge can mean the difference between life and death -- and technology is a great way to get that edge. This section presents devices and modifications to enhance almost any weapon

\begin{calloutbox}
    \subsection{Smartgun Electronics}\label{subsec:smartgun_electronics}
    %\addcontentsline{toc}{subsection}{Smartgun Electronics}
    Every modern firearm has a laser sight (p. \pageref{subsec:multispectral_laser_sight}), a HUD link (\hyperref[subsec:hud_link]{below}), a recognition grip or transponder ring (p. TODO), a tiny computer (p. \pageref{itm:tiny_com}), and a diagnostic computer (p. \pageref{subsec:diagnostic_computer}) for free. These electronics are powered by an integral B cell, which is included in the basic weight of the gun.
\end{calloutbox}

\section{Targeting Systems}\label{sec:targeting_systems}
These help the shooter find their target and hit it.

\subsection{HUD Link}\label{subsec:hud_link}   
Connected to a heads~-up display (p. \pageref{itm:terminal_hud}), this shows augmented~-reality targeting imagery in the user's field of view. The link shows him exactly where his firearm is pointing (+1 Acc within 300 yards, not cumulative with the Acc bonus for other targeting systems), the number of shots reamining, and -- if using a laser sight or other active targeting device -- the distance to the target. The user can exploit this to see around corners, exposing only his weapon.

\subsection{Multispectral Laser Sight}\label{subsec:multispectral_laser_sight}
This device projects a low~-powered eye~-safe laser beam, placing a laser spot at the point where the weapon will hit. 

A laser sight gives a +1 to skill when used out to the weapon's 1/2D range, provided the dot is visible to the shooter. It can be set to uas any one of these frequencies:
\\

\textit{Visible Light:} This projects a visible red, blue, or orange spot. The laser beam itself is only visible in dusty or smoky environments.

\textit{Infrared:} An infrared laser beam projects a dot that is invisible without an infrared or hyperspectral vision system.

\textit{Ultraviolet:} The dot of this ultraviolet laser beam is invisible without an ultraviolet or hyperspectral vision system.

\subsection{Compact Targeting Scope (CTS)}\label{subsec:compact_targeting_scope}
This video sighting system provides hyperspectral vision. It has telescopic optics for normal viewing in daylight, and interfaces with the weapon's HUD sight. It provides a +2 bonus to aimed shots.

The scope can also be used as a passive sensor, providing Hyperspectral Vision with Restricted Vision (Tunnel Vision). It has 4× magnification. The user must aim the weapon at the target she is observing. \$1,000, 0.5 lb., A/100 hr. LC4.

\subsection{Enhanced Targeting Scope (ETS)}\label{subsec:enhanced_targeting_scope}
A powerful video sighting system used by snipers or heavy weapon gunners. It provides hyperspectral imaging (p. \pageref{subsec:hyperspec_imaging_sensor}), plus telescopic optics for normal viewing in daylight. It interfaces with the weapon's HUD sight.

The weapon's sight automatically measures wind conditions, air temperature, and local gravity conditions, adjusting the weapon's velocity to compensate.

The scope adds a +3 bonus to aimed shots. Used as a passive sensor, it provides Hyperspectral Vision with Restricted Vision (Tunnel Vision) with 8× magnification. The user must aim their weapon at the target they're observing. \$8,000, 2 lb., B/400 hr. LC4.

\subsection{Tactical Programs}\label{subsec:tactical_programs}
These programs augment the tactical or strategic acumen of combat personnel by automating error~-prone tasks. They assit the user without replacing him.

\subsubsection{Silhouette}\label{subsubsec:silhouette}
This optical recognition program specializes in identifying targets of interest and providing background or technical data. The quantity and accuracy of supporting information depends on the databases used. High~-quality commercial databases offer expensive subscriptions and constantly updated content, but lack detail. Military databases are usually encrypted and contain very detailed information, including hyperspectral emission profiles, countermeasure tactics, and usage instructions. Military databases require Military Rank or Security Clearance. Complexity 5; double normal cost.

\subsubsection{TacNet}\label{subsubsec:tacnet}
A software tool (p. \pageref{subsec:software_tools}) useful for combat troops, TacNet helps a leader monitor a combat force by tracking and displaying their positions, firing arcs, blind spots, command relationships, and more. This gives a bonus to Tactics if all parties are in communication. Complexity 5 (+1 Tactics), LC3 or Complexity 6 (+2 Tactics), LC2. 10 times normal cost.

\subsubsection{Targeting}\label{subsubsec:tactical_program_targeting}
This software tool augments the capabilities of a HUD link (above) by improving target acquisition speed, ballistic modeling, environmental compensation (adjusting for air pressure, wind, humidity, temperature, etc.), and prioritizing targets for threat assessment. THe program gives a bonus to a single Gunner or Guns specialization if used with a HUD link. Complexity 3 (+1 skill) or Complexity 4 (+2 skill). Five times normal cost. LC2.

\subsubsection{Target Tracking}\label{subsubsec:target_tracking_program}
Used in conjunction with a sensor system (see \textit{\nameref{ch:sensors}}, p. \pageref{ch:sensors}) such as a radar, radio direction finder, or hyperspectral optics, this tracks up to 10 distinct targets or emission sources at a time. It displays size, signal strength, bearing, vectors, and other appropriate information on a moving~-map display. Complexity 2; five times normal cost. Add +1 to Complexity and double cost per tenfold increase in tracking ability. LC4.

\subsection{Targeting with Active Sensors}\label{subsec:targeting_with_active_sensors}
The most accurate way to aim a weapon is to connect a targeting program (above) to a ``tactical'' active sensor (see \textit{\nameref{ch:sensors}}, p. \pageref{ch:sensors}) that has locked onto a target. This feeds real~-time ranging data to the gunner and shows the gunner exactly how to move the weapon (or vehicle, if a fixed weapon) to hit the target.

This can only be used for a mounted weapon (i.e., one using Gunner skill). The combination of targeting program and active sensor gives the maximum possible targeting bonus. \textit{Replace} all bonuses for scopes, computers, sensors, etc. with a bonus equal to the weapon's base Acc, up to a maximum of +9. (Acc does still increase normally with Aim maneuvers.)

In order to gain this bonus, the target must be in range of the active sensor, and the program must be able to provide data directly to either the vehicle operator or whoever is operating the weapon's mount.

\section{Other Accessories}
These accessories can be added to most weapons.

\subsection{Accessory Rails}\label{subsec:accessory_rails}
Fire arms often have accessory rails for attaching optional systems such as sights and grenade launchers. Up to four accessory railsper weapon are allowed (under barrel, over barrel, side of stock, top of stock) but this will vary with weapon size and configuration. \$100 and 0.2 lb. each.

\subsection{Gyrostabilized Weapon Harness}\label{subsec:gyrostabilized_weapon_harness}
This articulated weapon harness (below) cancels the penalty for a Move and Attack (see p. B365). It is \$1,000, plus \$200 and 1 lb. per pound of loaded weight. LC4.

\subsection{Access Control}\label{subsec:access_control}
This electronic access system limits usage to authorized persons. The weapon will not fire for unauthorized users. Access control can be assigned to individual owners, but in military and paramilitary organizations it is common to set it so everyone in a unit can share the same weapons. Deactivating or reprogramming the safety system requires an Armoury (Small Arms) or Electronics Operation (Security) roll at -2 penalty. The first attempt takes 10 seconds; subsequent attempts require 10 minutes per try.
\\

\textit{Transponder Ring:}\label{itm:transponder_ring} A ring worn by the user that contains a radio transmitter with a one~-inch range. The transmitter sends a coded authorization message to the weapon, which will not fire unless the correct ring is worn. The ring may be permanently built into an armored suit glove, if desired. \$100. LC4.

\textit{Recognition Grip:}\label{itm:recognition_grip} A multi~-function biometric scanner built into the grip. IT can respond to palm prints or voice prints. It may also require both identifiers for maximum security. \$100. LC4.

\subsubsection{Self~-Destruct Anti~Theft}\label{subsubsec:self-destruct_anti-theft}
A miniature biosensor in the weapon's handgrip automatically scans the genetic pattern of the holder. If the pattern matches one of the authorized users in its memory, the weapon will fire. If not, the weapon will lock its firing circuits and begin a destruct sequence. It may or may not warn its holder!

To abort the destruct sequence, the unrecognized holder must give the weapon's computer a verbal authorization code. If the correct code is not given in 10 seconds, the gun self~-destructs, doing 6d×4 explosion damage.

With the correct code (a single word and number combination) the weapon can be reprogrammed to accept the biopattern of the holder. Each code is unique to each weapon. Special codes are also possible, such as one to delete biopatterns, or one which causes the weapon to destroy itself immediately when fired. Any attempt to circumvent the anti~-theft system requires proper tools and a roll against Electronics Operation (Security)-3. Each attempt takes half an hour; failure activates the destruct sequence, while critical failure causes an immediate explosion. \$100. LC3.

\subsection{Articulated Weapon Harness}\label{subsec:articulated_weapon_harness}
This is used to steady very heavy weapons. It straps on and has a chest plate in front, with a supporting arm and three hydraulic joints positioned to allow universal motion and easy suspension. It has the same effect as a bipod (ST requirement of the weapon is reduced by 2/3 and the weapon counts as braced), but can be used while standing up or moving. The user must still operate the weapon normally, using his own hands to aim and fire it.

The harness must be built for a specific weapon, and is generally limited to weapons with Bulk -4 or more. It is \$50 and 0.5 lb. per pound of loaded weight for the weapon it is built for -- e.g., a harness for a 20~-lb. machine gun is \$1,000, 10 lb. LC4.

\subsection{Diagnostic Computer}\label{subsec:diagnostic_computer}
These smart integrated electronics give +1 to skill rolls to fix damage or malfunctions. Diagnostic computers are standard in all modern firearms at no extra cost. Bought separately, \$10, neg. weight. LC4.

\subsection{D~-Tag}\label{subsec:d-tag}
This is a tiny receiver built into a weapon or other item. Upon receiving a coded signal on a specific radio frequency, it sends out a return signal. D~-tags are often built into police equipment, and all major arms corporations (excluding ExoCaliber) include them standard in their products. A successful Electronics Operation (Security) roll is required to find it; a second roll (at -2) must be made to deactivate it without disabling the weapon or notifying the authorities. Bought separately it costs \$20, neg. weight. LC4.

\subsection{IFF Interrogator}\label{subsec:iff_interrogator}
Friendly fire casualties are a constant problem on chaotic battlefields. An IFF interrogator identifies friends and foes before a soldier pulls the trigger on the wrong target.

This uses an eye~-safe multispectral, invisible signal beam to transmit an identification number, communication response frequency, and an encrypted code at the target.

If the target is wearing an IFF system (p. TODO), then it can decipher the code and transmit a brief message in reply. The interrogator then identifies the target as friendly, unidentified, or known hostile. Feedback is displayed on the soldier's HUD sight or augmented reality display. Older models may instead use a blinking LEDs to indicate.

IFF systems have some disadvantages: over~-reliance on technical identification, difficulty using the IFF interrogator in cluttered environments, and the potential for compromising the user's presence. The range of the IFF system is also limited: they have a range of 1,000 yards. Beyond this range, an Electronics Operation (Sensors) roll is required to get a clear identification, with potentially disastrous results in the case of filure. \$100.

\subsection{Power Holster}\label{subsec:power_holster}
This is available for any pistol~-type weapon or knife. It consists of three parts: a wrist sensor unit, a homing sensor on the handgrip of the weapon, and a break~-away holster. When the wrist sensor detects nerve impulses that mean the wearer wants to draw, the holster ejects the wepaon toward the hand. This lets the weapon be readied instantly. Each make of item requires a separate holster. A power holster adds +5 to Knife, Pistol, or Ammo specialization of Fast~-Draw. \$1,000, B/100 uses. LC4.

\subsection{Sniper Mirror}\label{subsec:sniper_mirror}
A laser gunner using a visible~-light laser may set up a high~-quality optical mirror for ambushes. The sniper can fire at the target's image in the mirror; the beam will reflect off and strike the target. The mirror can be remotely controlled with a communicator.

The range is equal to the range of the target to the mirror, plus the range from the mirror to the sniper. The sniper is at -4 to skill when performing this maneuver.

When strategically placed (usually requiring a Tactics or Traps roll), these mirrors allow a laser sniper to fire around corners, and may confuse the enemby about the direction from which fire is coming. The standard mirror is about two feet across when in use, but folds to the size of a paperback book. \$500, 1 lb. LC4.

\subsection{Tripod}\label{subsec:tripod}
A tripod may be added to any mounted weapon (M notation next to ST), allowing it to be set up on the ground rather than on a vehicle.

Ignore a weapon's ST requirement when it is tripod~-mounted. Removing the weapon from its tripod or reattaching it takes at least three Ready maneuvers.

A tripod provides a 180\degree arc of fire and allows the weapon to be elevated or depressed. The weapon requires two hands to use, and the user must usually sit or kneel behind the tripod. A typical tripod can mount a weapon that requires ST 25 or less, or any non~-weapon sensor that weighs up to 125 pounds. \$1,250, 25 lb. LC4.

\subsubsection{Powered Tripod Mount}\label{subsubsec:powered_tripod_mount}
A tripod can have an electric motor built into it. If the weapon has a sensor such as a radar or motion detector plugged into it (see \textit{Plug~-in Gadgets}, p. TODO), it can be remotely controlled via computer. If the computer has appropriate AI software, it can fire autonomously. A typical powered tripod can fire any weapon that requires ST 25 or less, or direct any non~weapon sensor up to 125 lb. \$5,000, 50 lb. D/100 hr. LC4.

\subsection{Shoulder Servomount}\label{subsec:shoulder_servomount}
This is a strap~-on half~-backpack with a gyrostabilized servo arm. It holds a single weapon over the user's shoulder. The weapon is aimed with a heads~-up display, and can swivel to fire at any target in front of the user.

The device has the same effect as a gyrostabilized weapon harness (p. \pageref{subsec:gyrostabilized_weapon_harness}), with the addition that the user does not use her hands to control the weapon. This is equivalent to the Extra Arm (Weapon Mount) advantage.

A servomount weapon should be used with a HUD. If not, the user fires the weapon at -2 penalty, and may not take Aim maneuvers. An AI can also control a servomount, freeing up the user for other activities, such as firing a handheld gun.

It's possible to wear up to two shoulder servomounts, one over each shoulder. The gear is heavy, so shoulder servomounts are most often used by battlesuit troopers, or by nonhuman or disabled warriors who lack usable limbs.

A shoulder servomount is \$5,000 plus an extra \$1,000 and 3 lb. per pound of weapon loaded weight. Thus, a servomount for a seven~-pound weapon is \$12,000 and 21 lb. LC3.

\subsection{Smartgrip}\label{subsec:smartgrip}
A smart~-matter pistol grip and trigger can be added to any firearm. It automatically adjusts to the user's strength and hand shape. This makes the weapon easier to fire, reducing the ST requirement byt 1. \$500, LC4.