The simplest way to kill or injure at a distance is with a projectile. Guns and launchers can carry inert slugs, explosives, or chemical weapons. The difference between guns and launchers is that launchers fire a self~-propelled projectiles, such as rocket, that continue to accelerate after it has left the weapon.

Guns and launchers are described with the name of the weapon followed by a designation for the ammunition it fires. The designation is a projectile diameter in millimeters and a letter code used to differentiate it from others of the same diameter. The damage on the weapon tables assumes a solid projectile, but all guns and launchers (except ice guns) may also fire weapons with more exotic warheads. See \textit{Warheads and Ammunition}, p. TODO.

\subsection{Ammunition Tables}\label{subsec:guns_launchers_ammunition_tabls}
Projectile weapons require ammunition. The weight of a loaded magazine of ammunition is given in the Weapon Tables, after the weapon's weight. The price of ammunition is not included, however, and adventurers may also wish to buy individual  rounds.

Ammunition Tables provide the following information about individual rounds of ammunition:

\textit{Name:} The name of the ammunition, e.g., 7mmCL.

\textit{WPS:} The weight per shot, in pounds.

\textit{CPS:} The cost per shot, in dollars. This is increased if using specialized warheads (p. TODO)

\textit{LC:} The legality class of the ammunition (if firing ordinary solid projectiles).

Different weapons can't share magazines except where indicated, but if the ammunition is identical, it's possible to remove individual rounds from one magazine and load them into another; e.g., ammo taken from any 7mmCL weapon will work in any other 7mmCL weapon.

\section{Conventional and ETC Guns}\label{sec:conventional_etc_guns}
THese weapons use the expanding gases from a burning chemical propellant to push a projectile down a barrel. 

\subsection{Conventional Small Arms}\label{subsec:conventional_small_arms}
They use light polymer~-cased or caseless telescoped ammunition, in which a projectile is embedded into a block of solid propellant. This reduces the ammunition's weight and bulk so that more shots can be carried. The propellant is ignited with an electrical system; this is integrated into the weapon's smartgun electronics and uses the same power cell.

\textit{Preloaded Barrels:} Some conventional guns replace their ammunition feed and ejection systems with alternating propellant charges and projectiles stacked \textit{inside} the gun barrel. These are fired electronically, singly or in very rapid sequence. The theoretical rate of fire can exceed a million rounds per minute, but the shots that fit into a barrel limit the effective rate of fire! In practice, the rounds can be fired fast enough that any recoil impulse is minimized. The whole barrel must be changed to reload; most guns of this sort have more than one barrel.

\subsubsection{Pistol}\label{subsubsec:convetional_pistols}
\textit{Heavy Pistol, 10mmCLP:}\label{itm:heavy_pistol_10mmclp} This powerful pistol uses the same round as the machine pistol (below).

\textit{Holdout Pistol, 7.5mmCLP:}\label{itm:holdout_pistol_7.5mmclp} This is a small, easily concealed semi~-automatic pistol.

\textit{Magnum Pistol, 15mmCLP:}\label{itm:magnum_pistol_15mmclp} This semi~-automatic pistol fires a powerful magnum round. Its size makes it hard to conceal, and only a strong person can shoot accurately with it.

\textit{Medium Pistol, 7.5mmCLP:}\label{itm:medium_pistol_7.5mmclp} The standard semi~-automatic pistol, with a sturdy plastic and alloy frame and a high~-capacity magazine.

\subsubsection{Submachine Guns}\label{subsubsec:conventional_submachines}
These are compact, fully~-automatic assault weapons with pistol grips, folding front foregrips, and retractable telescoping stocks.

\textit{Machine Pistol, 10mmCLP:}\label{itm:machine_pistol_10mmclp} This weapon fires the same medium~-velocity pistol~-caliber round as the 10mm pistol. It is favored as it has good stopping power, but errant rounds are unlikely to tear through walls (or targets) and hit bystandards.

\textit{Personal Defense Weapon (PDW), 5.7mmCL:}\label{itm:pdw_5.7mmcl} A PDW fires a small, high~-velocity bullet that resembles a miniature rifle round, with better accuracy and range than the pistol ammo used in a submachine gun. This weapon has a big magazine that runs horizontally alongside the weapon. An ergonomic handgrip completely encloses the firing hand.

\textit{Urban Assault Weapon (UAW), 10mmCLP:}\label{itm:uaw_10mmclp} A double~-barrel weapon with a 10mm machine pistol and 18.5mm shotgun (use the underbarrel shotgun statistics).

\subsubsection{Rifles}\label{subsubsec:conventional_rifles}
These weapons incorporate shoulder stocks, and are designed to be used two~-handed. Too large to holster, they come with carrying slings.

\textit{Anti~Material Rifle (AMR), 15mmCL:}\label{itm:anti-material_rifle_15mmcl} The 15mm AMR is a large~-caliber sniper weapon powerful enough to cripple light vehicles more than a mile away. This weapon becomes especially fearsome when upgraded with electrothermal or liquid propellant. The rifle's Acc assumes an integral 8× telescopic sight (+3 bonus).

\textit{Assault Carbine, 7mmCL:}\label{itm:assault_carbine_7mmcl} This bullpup~-configuration assault rifle is a basic but effective infantry weapon.

\textit{Gatling Carbine, 5.7mmCL:}\label{itm:gatling_carbine_5.7mmcl} This triple~-barreled, electric~-motor~-driven chaingun boasts a carbine format no larger than an ordinary assault rifle. It fires the same 5.7mm round as the PDW (p. \pageref{itm:pdw_5.7mmcl}). Its long magazine slides and locks into the back of the weapon. A separately loaded B cell provides power for 19,500 shots.

\textit{Hunting Rifle, 7mmCL:}\label{itm:hunting_rifle_7mmcl} This plastic and alloy semi~-automatic rifle fires the same high~-velocity ammunition as the assault carbine.

\textit{Payload Rifle, 25mmCL:}\label{itm:payload_rifle_25mmcl} A bulky semi~-automatic rifle, similar to an anti~-material rifle, that fires a medium~-velocity 25mm cannon shell. This provides a long~-ranged alternative to a grenade launcher. It has a very effective muzzle brake.

\textit{Storm Carbine, 10mmCL:}\label{itm:storm_carbine_10mmcl} This weapon fires a more powerful 10mm caseless round. Its drawbacks include heavier ammunition and noticeably higher recoil.

\textit{Storm Rifle, 10mmCLR:}\label{itm:storm_rifle_10mmclr} A heavier semi~-automatic version of the storm carbine, this fires a higher~-velocity, full~-sized (``10mm Caseless Long Rifle'') bullet. 

\subsubsection{Machine Guns}\label{subsubsec:conventional_machine_guns}
These automatic weapons are designed to be fired in long bursts from a bipod or tripod mount. They use an ammunition belt, which is sometimes contained within a cassette. When firing on the move, machine guns can be carried in an articulated weapon harness or a gyrostabilized weapon harness (p. TODO).

\textit{Assault Cannon, 25mmCL:}\label{itm:assault_cannon_25mmcl} This is a tripod~- or vehicle~-mounted automatic cannon firing medium~-velocity shells, similar to those of the payload rifle (above).

\textit{Light Support Weapon (LSW), 7mmCL:} This light machine gun comes with a folding bipod for accurate prone firing. The LSW normally employs a belt feed, but it fires the same bullet as the assault carbine (above), and can use its magazines if necessary.

\textit{Minigun, 7mmCL:}\label{itm:minigun_7mmcl} This portable, tripod~-mounted gatling gun boasts six rotating barrels and an electric action, firing up to 100 rounds per second. A separately loaded C cell powers it for up to 15 minutes.

\textit{Storm Chaingun, 10mmCLR:}\label{itm:storm_chaingun_10mmclr} This is an electric~-motor~-driven, machine~-gun version of the storm rifle (above). It uses a 60~-shot belt contained within an ammo cassette. It can also use the same 12~-shot 10mmCLR magazines as the storm rifle, but it cannot fire storm~-carbine ammunition. The storm chaingun incorporate a folding bipod for accurate prone firing. A separately loaded B cell provides 15 minutes of power.

\textit{Heavy Chaingun, 15mmCL:}\label{itm:heavy_chaingun_15mmcl} This electric~-motor~-driven, single~-barrel machine gun fires the same round as the anti~-material rifle. Normal humans can't handle its weight without a tripod, but powered troopers can use it as a handheld weapon. A separately loaded C cell provides 15 minutes of power.

\subsubsection{Shotguns}\label{subsubsec:conventional_shotguns}
Shotguns are a special category of slugthrower: low~-powered, short~-barrel smoothbores firing large rounds, often with multiple projectiles. Most fire 18.5mm (12 gauge) plastic~-cased ammo.

\textit{Civ Shotgun, 18.5mmPC:}\label{itm:civ_shotgun_18.5mmpc} A semi~-automatic shotgun. It is fitted with a plastic shoulder stock.

\textit{Close Assault Weapon (CAW), 18.5mmPC:}\label{itm:caw_18.5mmpc} A fully~-automatic assault shotgun favored for house~-to~-house fighting.

\textit{Underbarrel Shotgun, 18.5mmPC:}\label{itm:underbarrel_shotgun_18.5mmpc}A modular pump~-action shotgun that can be clamped under any weapon with Bulk -3 or more. Use the Bulk, ST, and sighting bonuses of the weapon it is installed in. 

\textit{Shotgun Pistol, 18.5mmPC:}\label{itm:shotgun_pistol_18.5mmpc} A wide~-bore pistol that fires shotgun ammunition. It is ideal for house-to-house work or for firing from a vehicle. It’s also a favorite police undercover weapon, despite its substantial recoil.

\subsubsection{Mortars and Grenade Launchers}\label{subsubsec:mortars_grenade_launchers}
\textit{Underbarrel Grenade Launcher (UGL), 25mmPC:}\label{itm:ugl_25mmpc} This is a tube~-fed pump~-action grenade launcher firing medium~-velocity plastic-cased shells. It may be clamped under the barrel of any weapon with Bulk -3 or more. Use the Bulk, ST, and sighting bonuses of the weapon it is installed in.

\textit{Underbarrel Grenade Launcher (UGL), 40mmPLB:}\label{itm:ugl_40mmplb} This grenade launcher fires low~-velocity shells. Like its 25mm counterpart, it’s designed to be clamped under another weapon with Bulk -3 or more. Each ``magazine'' is actually a preloaded barrel stacked with five 40mm shells and propellant charges. It can fire up to three grenades before any recoil impulse is felt. Use the Bulk, ST, and sighting bonuses of the weapon it is installed in.

\textit{Mortar Box, 40mmPLB:}\label{itm:mortar_box_40mmplb} A four~-tube version of the 40mm UGL. Designed for remote control firing, it has a cable jack and its own short~-range radio (p. \pageref{subsec:radio_comms}).

\textit{Mortar Box, 64mmPLB:}\label{itm:mortar_box_64mmplb} A larger version of the 40mm mortar box, consisting of a pod holding six mortar barrels, each containing five stacked 64mm shells. This potent ``area denial weapon'' can deliver as many as 30 shots in a single salvo!

\subsubsection{Cannon}\label{subsubsec:conventional_cannon}
\textit{Tank Cannon, 100mm:}\label{itm:tank_cannon_100mm} A medium tank gun with an automatic loader. It is often upgraded with liquid propellant or electrothermal options, or loaded with APEP (p. TODO) ammunition.

\subsubsection{Light Anti-Armor Weapons}\label{subsubsec:light_anti-armor_weapons}
Splat Gun, 15mmPLB (TL9): Designed to destroy light armored vehicles and battlesuit troopers, this is a favorite weapon of mercenaries fighting on low~-tech worlds. It is a bulky, multi-barrel weapon resembling a short, thick bazooka, with a pistol grip, a padded shoulder stock, and a bipod. Nicknamed the ``splat gun,'' it has six preloaded barrels stacked with 15mm shells and propellant. Its electronic ignition can fire up to 30 shells before any recoil impulse is felt. The shooter can also fire a smaller number of shells by adjusting a selector switch (this is a Ready action).

\multicolinterrupt{
    \begin{table}[H]
        \hrule height 1pt\medskip
        \subsection{\textit{Conventional Smallarm Table}}
        \noindent GUNS (PISTOL) (DX-4, or most other Guns at -2)
        \centering
        \small
        \rowcolors{1}{}{\colorweaponry}
        \begin{tabularx}{\linewidth}{lcXccXcXcXrc}
            \textbf{Weapon} & \textbf{Damage} & \textbf{Acc} & \textbf{Range} & \textbf{Weight} & \textbf{RoF} & \textbf{Shots} & \textbf{ST} & \textbf{Bulk} & \textbf{Rcl} & \textbf{Cost} & \textbf{LC} \\
            % name & damage & acc & range & weight & rof & shots & st & bulk & rcl & \$ & LC \\
            Heavy Pistol, 10mmCLP & 3d pi+ & 2 & 180/2,00 & 2.5/0.7 & 3 & 20+1(3) & 10 & -2 & 3 & \$540 & 3 \\
            Holdout Pistol, 7.5mmCLP & 2d pi- & 1 & 100/1,200 & 1/0.2 & 3 & 18+1(3) & 6 & -1 & 2 & \$240 & 3 \\
            Magnum Pistol, 15mmCLP & 4d+1 pi++ & 2 & 235/2,600 & 3/1 & 3 & 9+1(3) & 11 & -3 & 4 & \$870 & 3 \\
            Medium Pistol, 7.5mmCLP & 2d+2 pi- & 2 & 150/1,900 & 2/0.5 & 3 & 30+1(3) & 9 & -2 & 2 & \$450 & 3 \\
        \end{tabularx}\medskip

        \rowcolors{1}{}{}
        % \hiderowcolors
        \noindent GUNS (SMG) (DX-4, or most other Guns at -2)
        \begin{tabularx}{\linewidth}{lcXccXcXcXrc}
            \textbf{Weapon} & \textbf{Damage} & \textbf{Acc} & \textbf{Range} & \textbf{Weight} & \textbf{RoF} & \textbf{Shots} & \textbf{ST} & \textbf{Bulk} & \textbf{Rcl} & \textbf{Cost} & \textbf{LC} \\
            % name & damage & acc & range & weight & rof & shots & st & bulk & rcl & \$ & LC \\ 
            \rowcolor{\colorweaponry}
            Machine Pistol, 10mmCLP & 3d pi+ & 2 & 180/2,000 & 3/1 & 10 & 30+1(3) & 10 & -2 & 3 & \$750 & 2 \\
            Personal Defense Weapon, 5.7mmCL & 4d pi- & 4 & 350/3,000 & 4.5/1 & 10 & 100+1(5) & 9† & -3 & 2 & \$1,000 & 2 \\
            \rowcolor{\colorweaponry}
            Urban Assault Weapon, & & & & & & & & & & & \\
            \rowcolor{\colorweaponry}
            \hspace{1em} \textit{SMG barrel}, 10mmCLP & 3d pi+ & 4 & 200/2,100 & 8/1 & 10 & 40+1(3) & 9† & -3 & 3 & \$2,100 & 2 \\
            \rowcolor{\colorweaponry}
            \hspace{1em} \textit{Shotgun barrel}, 18.5mmPC & 4d+4 pi++ & 2 & 100/500 & --/0.75 & 2 & 5+1(3i) & 10† & -- & 1 & & \\
        \end{tabularx}\medskip

        \rowcolors{1}{}{\colorweaponry}
        \noindent GUNS (RIFLE) (DX-4, or most other Guns at -2)
        \begin{tabularx}{\linewidth}{lcXccXcXcXrc}
            \textbf{Weapon} & \textbf{Damage} & \textbf{Acc} & \textbf{Range} & \textbf{Weight} & \textbf{RoF} & \textbf{Shots} & \textbf{ST} & \textbf{Bulk} & \textbf{Rcl} & \textbf{Cost} & \textbf{LC} \\
            % name & damage & acc & range & weight & rof & shots & st & bulk & rcl & \$ & LC \\
            Anti~-Material Rifle, 15mmCL & 15d pi++ & 6+3 & 2,000/9,000 & 30/2 & 3 & 10(3) & 12B† & -6 & 4 & \$8,000 & 3 \\
            Assault Carbine, 7mmCL & 6d pi & 4 & 700/4,000 & 7/1.5 & 15 & 50+1(3) & 9† & -4 & 2 & \$1,600 & 2 \\
            Gatling Carbine, 5.7mmCL & 4d pi- & 4 & 350/3,000 & 10/2 & 40 & 200(5) & 9† & -4 & 2 & \$2,400 & 1 \\
            Hunting Rifle, 7mmCL & 6d+1 pi & 5 & 750/4,200 & 7/0.3 & 3 & 10+1(3) & 9† & -5 & 2 & \$800 & 3 \\
            Payload Rifle, 25mmCL & 10d pi++ & 4 & 700/8,500 & 38/10 & 3 & 8+1(3) & 12B† & -6 & 4 & \$8,000 & 2 \\
            Storm Carbine, 10mmCL & 7d pi+ & 4 & 700/2,100 & 8/2 & 10 & 50+1(3) & 10† & -4 & 3 & \$1,800 & 2 \\
            Storm Rifle, 10mmCLR & 9d pi+ & 5 & 1,300/5,800 & 10/1.2 & 3 & 12+1(3) & 10† & -5 & 3 & \$2,700 & 3 \\
        \end{tabularx}\medskip

        \rowcolors{1}{}{\colorweaponry}
        \noindent GUNS (SHOTGUN) (DX-4, or most other Guns at -2)
        \begin{tabularx}{\linewidth}{lcXccXcXcXrc}
            \textbf{Weapon} & \textbf{Damage} & \textbf{Acc} & \textbf{Range} & \textbf{Weight} & \textbf{RoF} & \textbf{Shots} & \textbf{ST} & \textbf{Bulk} & \textbf{Rcl} & \textbf{Cost} & \textbf{LC} \\
            % name & damage & acc & range & weight & rof & shots & st & bulk & rcl & \$ & LC \\
            Civilian Shotgun, 18.5mmPC & 4d+4 pi++ & 3 & 100/500 & 6/0.75 & 3 & 5+1(3) & 10† & -5 & 4 & \$450 & 3 \\
            Close Assault Weapon, 18.5mmPC & 4d+4++ & 3 & 100/500 & 10/1.5 & 10 & 10+1(3) & 11† & -5 & 4 & \$800 & 2 \\
            Shotgun Pistol, 18.5mmPC & 4d pi++ & 1 & 100/500 & 4/0.7 & 3 & 5+1(3) & 10 & -3 & 5 & \$330 & 3 \\
            Underbarrel Shotgun, 18.5mmPC & 4d+4 pi++ & 2 & 100/500 & 1.5/0.75 & 2 & 5+1(3i) & 10† & -- & 4 & +\$300 & 3 \\
        \end{tabularx}\medskip
        \label{tab:conv_smallarms}
    \end{table}

    
    \begin{table}[H]
        \hrule height 1pt\medskip
        \subsection{\textit{Infantry Support Weapons Table}}
        \noindent GUNS (GRENADE LAUNCHER) (DX-4, or most other Guns at -4)
        \centering
        \small
        \rowcolors{1}{}{\colorweaponry}
        \begin{tabularx}{\linewidth}{lcXccXcXcXrc}
            \textbf{Weapon} & \textbf{Damage} & \textbf{Acc} & \textbf{Range} & \textbf{Weight} & \textbf{RoF} & \textbf{Shots} & \textbf{ST} & \textbf{Bulk} & \textbf{Rcl} & \textbf{Cost} & \textbf{LC} \\
            % name & damage & acc & range & weight & rof & shots & st & bulk & rcl & \$ & LC \\
            Underbarrel Grenade Launcher, 25mmPC & 4d pi++ & 4 & 360/2,200 & 1.5/0.66 & 1 & 3(3) & 10 & -- & 3 & +\$300 & 1 \\
            Underbarrel Grenade Launcher, 40mmPLB & 1d pi++ & 2 & 75/450 & 3/2 & 3 & 5(5) & 10 & -- & 1 & +\$200 & 1 \\
        \end{tabularx}\medskip

        \rowcolors{1}{}{\colorweaponry}
        % \hiderowcolors
        \noindent {\normalsize GUNS (LIGHT MACHINE GUN) (DX-4, or most other Guns at -2)}
        \begin{tabularx}{\linewidth}{lcXccXcXcXrc}
            \textbf{Weapon} & \textbf{Damage} & \textbf{Acc} & \textbf{Range} & \textbf{Weight} & \textbf{RoF} & \textbf{Shots} & \textbf{ST} & \textbf{Bulk} & \textbf{Rcl} & \textbf{Cost} & \textbf{LC} \\
            % name & damage & acc & range & weight & rof & shots & st & bulk & rcl & \$ & LC \\ 
            Light Support Weapon, 7mmCL & 6d pi & 5 & 700/4,000 & 15/5 & 15 & 200(5) & 9B† & -5 & 2 & \$3,000 & 1 \\ 
            Storm Chaingun, 10mmCLR & 9d pi+ & 5 & 1,300/5,800 & 20/6 & 10 & 60(5) & 11B† & -6 & 3 & \$11,000 & 1 \\ 
        \end{tabularx}\medskip

        \rowcolors{1}{}{\colorweaponry}
        \noindent {\normalsize GUNS (LAW) (DX-4, or most other Guns at -2)}
        \begin{tabularx}{\linewidth}{lcXccXcXcXrc}
            \textbf{Weapon} & \textbf{Damage} & \textbf{Acc} & \textbf{Range} & \textbf{Weight} & \textbf{RoF} & \textbf{Shots} & \textbf{ST} & \textbf{Bulk} & \textbf{Rcl} & \textbf{Cost} & \textbf{LC} \\
            % name & damage & acc & range & weight & rof & shots & st & bulk & rcl & \$ & LC \\
            Splat Gun, 15mmPLB & 3d+2 pi++ & 4 & 220/2,000 & 20/10 & 30 & 30(30) & 10† & -6 & 1 & \$3,000 & 1 \\ 
        \end{tabularx}\medskip
        \label{tab:infantry_support}
    \end{table}

    \begin{table}[H]
        \hrule height 1pt\medskip
        \subsection{\textit{Mounted Weapons Table}}
        \noindent ARTILLERY (CANNON) (IQ-5)
        \centering
        \small
        \rowcolors{1}{}{\colorweaponry}
        \begin{tabularx}{\linewidth}{lcXccXcXcXrc}
            \textbf{Weapon} & \textbf{Damage} & \textbf{Acc} & \textbf{Range} & \textbf{Weight} & \textbf{RoF} & \textbf{Shots} & \textbf{ST} & \textbf{Bulk} & \textbf{Rcl} & \textbf{Cost} & \textbf{LC} \\
            % name & damage & acc & range & weight & rof & shots & st & bulk & rcl & \$ & LC \\
            Mortar Box, 40mmPLB & 1d pi++ & 2 & 75/450 & 12/8 & 4×4 & 16(20) & 12M & -6 & 1 & \$1,000 & 1 \\
            Mortar Box, 64mmPLB & 6d×2 pi++ & 3 & 360/3,00 & 160/80 & 6×5 & 30(30) & 25M & -10 & 1 & \$6,000 & 1 \\
        \end{tabularx}\medskip

        \rowcolors{1}{}{\colorweaponry}
        % \hiderowcolors
        \noindent {\normalsize GUNNER (CANNON) (DX-4, or other Gunner-4)}
        \begin{tabularx}{\linewidth}{lcXccXcXcXrc}
            \textbf{Weapon} & \textbf{Damage} & \textbf{Acc} & \textbf{Range} & \textbf{Weight} & \textbf{RoF} & \textbf{Shots} & \textbf{ST} & \textbf{Bulk} & \textbf{Rcl} & \textbf{Cost} & \textbf{LC} \\
            % name & damage & acc & range & weight & rof & shots & st & bulk & rcl & \$ & LC \\ 
            Tank Cannon, 100mmCL & 6d×25 pi++ & 6 & 3,000/10,000 & 2,500/40 & 1 & 1(4) & 150M & -10 & 4 & \$100,000 & 1 \\
        \end{tabularx}\medskip

        \rowcolors{1}{}{\colorweaponry}
        \noindent {\normalsize GUNNER (MACHINE GUN) (DX-4, other Gunner-4)}
        \begin{tabularx}{\linewidth}{lcXccXcXcXrc}
            \textbf{Weapon} & \textbf{Damage} & \textbf{Acc} & \textbf{Range} & \textbf{Weight} & \textbf{RoF} & \textbf{Shots} & \textbf{ST} & \textbf{Bulk} & \textbf{Rcl} & \textbf{Cost} & \textbf{LC} \\
            % name & damage & acc & range & weight & rof & shots & st & bulk & rcl & \$ & LC \\
            Assault Cannon, 25mmCL & 10d pi++ & 4 & 700/8,500 & 62/34 & 8 & 34(5) & 20M & -8 & 2 & \$17,000 & 1 \\
            Heavy Chaingun, 15mmCL & 15d pi++ & 6 & 2,000/9,000 & 75/12 & 12 & 50(5) & 20M & -8 & 2 & \$34,000 & 1 \\
            Minigun, 7mmCL & 6d pi & 5 & 700/4,000 & 33/10 & 100 & 400(5) & 15M & -7 & 2 & \$14,000 & 1 \\
        \end{tabularx}\medskip
        \label{tab:mounted_weapons}
    \end{table}

}

\subsection{\textit{Conventional Ammunition Table}}
\begin{table}[H]
    \subsubsection{Pistol Ammo}
    \centering
    \rowcolors{1}{}{\colorweaponry}
    \begin{tabularx}{\columnwidth}{XlXrXrXrX}
    % \caption{Caption}
         & \textbf{Ammo} && \textbf{WPS} && \textbf{CPS} && \textbf{LC} & \\
         % & Ammo && WPS && \$ && LC & \\
         & 7.5mmCLP && 0.006 && \$0.12 && 3 & \\
         & 10mmCLP && 0.014 && \$0.28 && 3 & \\
         & 15mmCLP && 0.060 && \$1.2 && 3 & \\
    \end{tabularx}\smallskip

    \raggedright
    \subsubsection{Rifle and PDW Ammo}
    \rowcolors{1}{}{\colorweaponry}
    \begin{tabularx}{\columnwidth}{XlXrXrXrX}
    % \caption{Caption}
         & \textbf{Ammo} && \textbf{WPS} && \textbf{CPS} && \textbf{LC} & \\
         % & Ammo && WPS && \$ && LC & \\
         & 5.7mmCL && 0.009 && \$0.18 && 3 & \\
         & 7mmCL && 0.027 && \$0.54 && 3 & \\
         & 10mmCL && 0.04 && \$0.8 && 3 & \\
         & 10mmCLR && 0.06 && \$1.2 && 3 & \\
         & 15mmCL && 0.2 && \$4 && 3 & \\
    \end{tabularx}\smallskip

    \raggedright
    \subsubsection{Shotgun Ammo}
    \rowcolors{1}{}{\colorweaponry}
    \begin{tabularx}{\columnwidth}{XlXrXrXrX}
    % \caption{Caption}
         & \textbf{Ammo} && \textbf{WPS} && \textbf{CPS} && \textbf{LC} & \\
         % & Ammo && WPS && \$ && LC & \\
         & 18.5mmPC && 0.092 && \$1.8 && 3 & \\
    \end{tabularx}\smallskip

    \raggedright
    \subsubsection{Payload Rifle and Cannon Ammo}
    \rowcolors{1}{}{\colorweaponry}
    \begin{tabularx}{\columnwidth}{XlXrXrXrX}
    % \caption{Caption}
         & \textbf{Ammo} && \textbf{WPS} && \textbf{CPS} && \textbf{LC} & \\
         % & Ammo && WPS && \$ && LC & \\
         & 25mmCL && 1 && \$20 && 2 & \\
         & 100mmCL && 40 && \$400 && 1 & \\
    \end{tabularx}\smallskip

    \raggedright
    \subsubsection{Splat Gun Ammo}
    \rowcolors{1}{}{\colorweaponry}
    \begin{tabularx}{\columnwidth}{XlXrXrXrX}
    % \caption{Caption}
         & \textbf{Ammo} && \textbf{WPS} && \textbf{CPS} && \textbf{LC} & \\
         % & Ammo && WPS && \$ && LC & \\
         & 15mmPLB && 0.27 && \$7 && 2 & \\
    \end{tabularx}\smallskip

    \raggedright
    \subsubsection{Grenade Launcher and Mortar Ammo}
    \rowcolors{1}{}{\colorweaponry}
    \begin{tabularx}{\columnwidth}{XlXrXrXrX}
    % \caption{Caption}
         & \textbf{Ammo} && \textbf{WPS} && \textbf{CPS} && \textbf{LC} & \\
         % & Ammo && WPS && \$ && LC & \\
         & 25mmPC && 0.22 && \$4.4 && 3 & \\
         & 40mmPLB && 0.4 && \$10 && 3 & \\
         & 64mmPLB && 2 && \$40 && 2 & \\
    \end{tabularx}\smallskip
    \label{tab:conventional_ammo}
\end{table}

\subsection{Electrothermal~-Chemical (ETC)}\label{subsec:electrothermal-chemical}
These weapons augment chemical energy with electrical power. A controlled plasma burn provides a smoother and more complete utilization of propellant, increasing the projectile velocity without a significant increase in recoil.

ETC weapons are not shown on the weapon table. Instead, all conventional slugthrowers are also available in ETC~-boosted versions

ETC guns have 1.5 times the piercing damage and range of a conventional caseless~-propellant gun. They are also twice as expensive.

They require electrical power as well as ammunition, although this power requirement is much less than an electromagnetic gun or beam weapon. The grip or stock of an ETC slugthrower incorporates a removable A cell (for pistols), B cell (for SMGs, PDWs, shotguns, rifles), or C cell (for heavy weapons) to provide electrical power. Each power cell can fire 10 magazines of ammunition.

\subsection{Liquid~-Propellant Slugthrowers}\label{subsec:liquid-propellant_slugthrowers}
Liquid propellants are an advanced option for chemical propellant. Propellant and oxidizer are kept in a separate bottle, then squirted into the firing chamber and ignited electrically when the rigger is pulled. Binary propellants are often used; the chemicals are inert until combined in the firing chamber.

Liquid propellant is a bit more powerful and easier to store, but its chief advantage is precise control of propellant velocities. In addition to standard velocity they have two other options:
\\

\textit{Boosted velocity} dumps extra propellant into the firing chamber: increase the piercing damage by +1 per die and multiply range by 1.3. Each counts as 1.5 shots for purposes of draining the propellant bottle.

\textit{Low velocity} dumps much less propellant into the firing chamber, making the weapon subsonic. Reduce the piercing damage and range by half! Rolls to hear the weapon fire are made at -3. Each counts as 1/4 shot for draining the propellant bottle.\\

Liquid propellant weapons use the same statistics as conventional caseless weapons, but they get 1.5 times as many shots per magazine and are 1.5 times as expensive. A propellant bottle can fire three magazines of shots and takes five seconds to reload. Additional propellant bottles weigh as much as a normal loaded magazine.

\section{Gas~-Powered Air Guns}\label{sec:gas-powered_air_guns}
These use air or carbon dioxide, compressed and stored in liquid form. When the trigger is pulled, the liquid is released and expands into a gas, propelling the projectile. Gas~-powered air guns are quiet and have no muzzle flash. They are often used as sporting weapons, and tend to have a higher Legality Class than other weapons.

\subsubsection{Weapons}\label{subsubsec:gas-powered_weapons}
\textit{Needler, 3mm:}\label{itm:needler_3mm} A small~-caliber air gun that can fire a bullet, or a drugged dart holding one dose of any injectable biochemical poison. Also called a ``needle pistol.'' 

\textit{Needle Rifle, 3mm:}\label{itm:needle_rifle_3mm} A higher~-powered air rifle, otherwise similar to the needle pistol.

\textit{Paint Carbine, 15mm:}\label{itm:paint_carbine_15mm} A large~-caliber, low~-velocity air gun used to fire plastic pellets containing paint or bio~-chemical liquid ammunition (p. TODO). It is electrically powered (a B cell can fire 10 magazines of ammunition) and capable of automatic fire. It may be designed as a replica of an actual rifle or carbine.

\textit{Paint Pistol, 15mm:}\label{itm:paint_pistol_15mm} A large~-caliber, low~-velocity air gun used to fire plastic pellets containing paint or bio~-chemical liquid ammunition (p. TODO). Some models are designed as replicas of pistols.

\textit{Tangler, 25mm:}\label{itm:tangler_25mm} A compressed gas gun about the size of a shotgun, with a folding stock. It fires a 25mm projectile at a very low velocity. It usually fires tangler (p. TODO) ammunition, but can also fire other 25mm warhead rounds or solid metal slugs.

\textit{Tangler Pistol, 25mm:}\label{itm:tangler_pistol_25mm} A pistol~-sized tangler that uses a less powerful compressed air charge. 

\textit{Wrist Needler, 3mm:}\label{itm:wrist_needler_3mm} A needler designed to be strapped to the wrist and concealed up a sleeve. It incorporates a simple neural input sensor reading muscle signals. A trained shooter can fire it with no more effort than pointing a finger, but it’s tricky to use without practice. Double penalties for lack of familiarity.

\textit{Ice Gun:}\label{itm:ice_gun} These use compressed gas to fire needles of frozen liquid. The needles dissolve without a trace in the target’s body. They are intended for survival or assassination. Each 20~-shot magazine includes a self~-contained refrigeration unit. Pour a cup of water into the magazine, activate the refrigeration unit, and in half an hour, 20 new ice needles will be ready to fire. A single C cell can freeze 100 magazines’ worth of ice needles.

An ice gun may also deliver drugged rounds. A dose of any hypo~-injected drug or poison can be pre-frozen into a sliver and fired, with the normal follow-up effect if it penetrates. Add the cost of 20 doses of that drug or poison.

\textit{Partisan Needler, 3mm:}\label{itm:partisan_needler_3mm} This spring-rifle weapon is designed for low~-tech guerrilla fighters, or for use by people planning a long stay in cultures that can’t produce sophisticated ammo. The solar~-powered flywheel foundry in the stock makes its own ammunition. It can produce 140 needles in an hour using a 2×3×1-inch metal block (\$1), which can be made by any village blacksmith with access to ore. After that, it must recharge for 10 hours in the sun.

\subsubsection{Option: Non-Metallic}\label{subsubsec:gas-powered_non-metallic}
All these weapons except the partisan needler may be made of non-metallic materials for +0.5 CF, allowing an unloaded weapon to bypass ordinary metal detectors.

\multicolinterrupt{
    \begin{table}[H]
        \hrule height 1pt\medskip
        \subsection{\textit{Conventional Smallarm Table}}
        \noindent GUNS (PISTOL) (DX-4, or most other Guns at -2)
        \centering
        \small
        \rowcolors{1}{}{\colorweaponry}
        \begin{tabularx}{\linewidth}{lcXccXcXcXrc}
            \textbf{Weapon} & \textbf{Damage} & \textbf{Acc} & \textbf{Range} & \textbf{Weight} & \textbf{RoF} & \textbf{Shots} & \textbf{ST} & \textbf{Bulk} & \textbf{Rcl} & \textbf{Cost} & \textbf{LC} \\
            % name & damage & acc & range & weight & rof & shots & st & bulk & rcl & \$ & LC \\
            Needler, 3mmN & 1d+2 pi- & 1 & 50/150 & 1/0.5 & 3 & 100(3) & 7 & -2 & 2 & \$500 & 3 \\
            Paint Pistol, 15mm & 1d-4 pi++ & 1 & 14/90 & 1/0.5 & 3 & 20+1(3i) & 8 & -2 & 2 & \$100 & 4 \\
            Tangler Pistol, 25mmT & 1d pi++ & 1 & 20/130 & 2/0.5 & 1 & 4+1(3i) & 10 & -3 & 2 & \$300 & 4 \\
            Wrist Needler, 3mmN & 1d-2 pi- & 1 & 25/100 & 0.1/0.03 & 3 & 6(3) & 3 & -1 & 2 & \$200 & 3 \\
            Ice Gun, 3mm ice & 1d-1(0.2) pi- & 1 & 50/150 & 1/0.2 & 3 & 20(3) & 7 & -2 & 2 & \$600 & 2 \\
        \end{tabularx}\medskip

        \rowcolors{1}{}{\colorweaponry}
        \noindent {\normalsize GUNS (RIFLE) (DX-4, or most other Guns at -2)}
        \begin{tabularx}{\linewidth}{lcXccXcXcXrc}
            \textbf{Weapon} & \textbf{Damage} & \textbf{Acc} & \textbf{Range} & \textbf{Weight} & \textbf{RoF} & \textbf{Shots} & \textbf{ST} & \textbf{Bulk} & \textbf{Rcl} & \textbf{Cost} & \textbf{LC} \\
            % name & damage & acc & range & weight & rof & shots & st & bulk & rcl & \$ & LC \\
            Needle Rifle, 3mmN & 2d pi- & 4 & 75/300 & 5/0.5 & 3 & 100(3) & 7† & -4 & 2 & \$600 & 4 \\
            Paint Carbine, 15mm & 1d-4 pi++ & 2 & 20/130 & 4/1 & 10 & 50+1(3i) & 6† & -2 & 2 & \$400 & 4 \\
            Tangler, 25mmT & 1d pi++ & 2 & 30/190 & 5/1 & 3 & 8+1(3i) & 7† & -4 & 2 & \$600 & 4 \\
            Partisan Needler, 3mmN & 2d pi- & 4 & 75/300 & 12/0.7 & 3 & 140(3) & 10† & -5 & 2 & \$1,500 & 4 \\
        \end{tabularx}\medskip
    \end{table}

    \begin{table}[H]
        \subsection{Air Gun Ammunition Table}
        \centering
        \rowcolors{1}{}{\colorweaponry}
        \begin{tabularx}{\columnwidth}{lXrXrXcXX}
            \textbf{Ammo} && \textbf{WPS} && \textbf{CPS} && \textbf{LC} && \\
            % & Ammo && WPS && \$ && LC && \\
            3mmN && 0.005 && \$0.1 && 4 && \\
            15mm && 0.025 && \$0.5 && 4 && \\
            25mmT && 0.12 && \$2.4 && 4 && \\
        \end{tabularx}
        % \caption{Caption}
        \label{tab:air_gun_ammo}
    \end{table}
}

\section{Electromagnetic Guns}\label{sec:electromag_guns}
These weapons use magnetic fields to accelerate projectiles to very high velocities. This translates into high accuracy, range, and kinetic damage. They do not require chemical propellant, which makes storing ammunition safer (less risk of fire or explosion) and reduces the magazine weight and volume.

The electromagnetic pulse produced when an electromagnetic gun fires may be detectable, but it will usually be difficult to localize. The only noise is the crack of the projectile breaking the sound barrier. Ammunition velocity can also be varied, exactly as for a liquid-propellant slugthrower (p. \pageref{subsec:liquid-propellant_slugthrowers}). The primary disadvantage of electromagnetic guns is their high power consumption.

Electromagnetic guns may use Gauss guns or railgun technology. Gauss guns – also called coilguns or massdrivers – accelerate a conductive projectile down a series of coils via a quickly changing magnetic field, and can achieve very high rates of fire. Railguns use two conductive rails to generate a current flow that accelerates a saboted projectile to high velocities. In game terms, both use the same rules, differing only in their combat statistics. Railguns usually do more damage and have superior range to equivalent-size Gauss guns, but tend to have slower rate of fire.

\subsubsection{Pistols}\label{subsubsec:electromagnetic_pistols}
\textit{Gauss Minineedler, 3mm:}\label{itm:gauss_minineedler_3mm} One of the smallest machine pistols available, this is an ultra~-compact holdout version of the Gauss needler.

\textit{Gauss Needler, 3mm:}\label{itm:gauss_needler_3mm} A short-ranged but rapid~-firing machine pistol.

\textit{Gauss Pistol, 4mm:}\label{itm:gauss_pistol_4mm} A long-barreled hyper~-velocity pistol with more kinetic energy than a 15mm magnum pistol, but only a fraction of the recoil.

\subsubsection{Submachine Guns}\label{subsubsec:electromagnetic_submachine_guns}
\textit{Gauss Machine Pistol, 4mm:}\label{itm:gauss_machine_pistol_4mm} The Gauss machine pistol’s compactness, high rate of fire, and stopping power make it popular with military officers, special forces, and terrorists.

\textit{Gauss Personal Defense Weapon (PDW), 4mm:}\label{itm:gauss_pdw_4mm} A compact assault weapon that accelerates bullets to a velocity between that of the Gauss pistol and Gauss rifle. 

\subsubsection{Rifles}\label{subsubsec:electromagnetic_rifles}
\textit{Sniper Railgun, 7mm:}\label{itm:sniper_railgun_7mm} An early sniper railgun used by and against battlesuits and combat robots, or for shooting down aircraft. It fires a 7mm dart at 10,000 feet per second, with twice the power of a 15mm sniper rifle. It has a comparatively low recoil, and can be fired without a bipod.

\textit{Portable Railgun, 10mm:}\label{itm:portable_railgun_10mm} This long~-barreled, semi~-automatic Gauss rifle fires 10mm slugs at hypersonic velocities. Used as a heavy sniper rifle, its advantage over conventional weapons is its larger ammunition capacity and lighter weight, especially when loaded.

\textit{Gauss Needle Rifle, 3mm:}\label{itm:gauss_needle_rifle_3mm} This weapon fires 3mm darts at very high rate of fire.

\textit{Gauss Rifle, 4mm:}\label{itm:gauss_rifle_4mm} The standard infantry rifle for most militaries across the universe. It is an automatic weapon that accelerates a 4mm bullet to almost 5,000 feet per second. 

\subsubsection{Shotguns}\label{subsubsec:electromagnetic_shotguns}
\textit{Gauss Close Assault Weapon (CAW), 18.5mm:}\label{itm:gauss_caw_18.5mm} Essentially a Gauss auto-shotgun, this is a fearsome close~-combat weapon firing a swarm of 12~-gauge projectiles at 150\% of the velocity of a conventional shotgun.

\textit{Gauss Shotgun Pistol, 18.5mm:}\label{itm:gauss_shotgun_pistol_18.5mm} Similar to the Gauss CAW (above), but in pistol format. This big~-bore, snub~-nosed semi-automatic is a favorite police sidearm, due to the many types of warheads it can fire.

\subsubsection{Machine Guns}\label{subsubsec:electromagnetic_machine_guns}
\textit{Gauss Minigun, 4mm:}\label{itm:gauss_minigun_4mm} This weapon spits out high~-velocity projectiles at up to 10,000 rounds per minute. It is used as a heavy machine gun and point~-defense weapon. The cryogenic cooling jacket surrounding the barrel and the huge ammo cassette allow sustained automatic fire.

\textit{Gauss Heavy Machine Gun (HMG), 7mm:}\label{itm:gauss_hmg_7mm} This tripod~-mounted 7mm machine gun fires the same round as the Gauss sniper rifle from a 200~-round ammo cassette.

\textit{Gauss Light Support Weapon (LSW), 4mm:}\label{itm:gauss_lsw_4mm} A heavy~-barrel version of the Gauss rifle, used as a machine gun or battlesuit sidearm. It can fire 3,000 rounds per minute.

\subsubsection{Cannon, Grenade Launchers, and Mortars}\label{itm:electromagnetic_cannon_grenade_launchers_mortars}
\textit{Electromag Grenade Launcher (EMGL), 40mm:}\label{itm:emgl_40mm} An EMGL is a stubby, shotgun~-like Gauss gun, similar in shape to 20th~-century grenade launchers.

\textit{Electromag Auto Grenade Launcher (Auto EMGL), 40mm:}\label{itm:auto_emgl_40mm} A bulky weapon firing the same round as the EMGL, but at higher velocities. It’s used as a tripod~-mounted infantry support weapon, or by powered troopers.

\textit{Electromag Mortar, 64mm:}\label{itm:electromag_mortar_64mm} This heavy base~-mounted tube is a standard semi~-portable infantry artillery piece. It’s also found mounted in vehicle turrets.

\textit{Railgun, 40mm:}\label{itm:railgun_40mm} An electromagnetic cannon with a very long barrel, firing a projectile at hypersonic velocities. It’s a suitable main gun for a tank or small warship.

\textit{Underbarrel Electromag GL, 25MM:}\label{itm:underbarrel_electromag_gl_25mm} This is a Gauss grenade launcher that can be attached under any weapon with Bulk -3 or more. It’s also called a mini~-GL. Use the Bulk, ST, and sighting bonuses of the weapon it is installed in.

\multicolinterrupt{
    \begin{table}[H]
        \hrule height 1pt\medskip
        \subsection{\textit{Electromagnetic Gun Table}}
        \centering
        \small
        % \raggedleft
        \noindent {\normalsize ARTILLERY (CANNON) (IQ-5)}
        \rowcolors{1}{}{\colorweaponry}
        \begin{tabularx}{\linewidth}{lcXccXcXcXrcc}
            \textbf{Weapon} & \textbf{Damage} & \textbf{Acc} & \textbf{Range} & \textbf{Weight} & \textbf{RoF} & \textbf{Shots} & \textbf{ST} & \textbf{Bulk} & \textbf{Rcl} & \textbf{Cost} & \textbf{LC} & \textbf{Notes}\\
            % name & damage & acc & range & weight & rof & shots & st & bulk & rcl & \$ & LC \\
            Electromag Mortar, 64mm & 6d×3 pi++ & 4 & 1,000/6,000 & 50/10 & 1 & 4(5) & 12M & -10 & 2 & \$40,000 & 1 & [4] \\
        \end{tabularx}\medskip

        \rowcolors{1}{}{\colorweaponry}
        \noindent {\normalsize GUNS (PISTOL) (DX-4, or most other Guns at -2)}
        \begin{tabularx}{\linewidth}{lcXccXcXcXrcc}
            \textbf{Weapon} & \textbf{Damage} & \textbf{Acc} & \textbf{Range} & \textbf{Weight} & \textbf{RoF} & \textbf{Shots} & \textbf{ST} & \textbf{Bulk} & \textbf{Rcl} & \textbf{Cost} & \textbf{LC} & \textbf{Notes}\\
            % name & damage & acc & range & weight & rof & shots & st & bulk & rcl & \$ & LC & Notes \\
            Gauss Minineedler, 3mm & 1d(3) pi- & 1 & 50/200 & 0.1/0.03 & 4 & 25(3) & 3 & -1 & 2 & \$800 & 3 & [1] \\
            Gauss Pistol, 4mm & 3d(3) pi- & 3 & 500/2,100 & 2/0.5 & 3 & 40(3) & 9 & -2 & 2 & \$1,700 & 3 & [2] \\
        \end{tabularx}\medskip

        \rowcolors{1}{}{\colorweaponry}
        \noindent {\normalsize GUNS (SMG) (DX-4, or most other Guns at -2)}
        \begin{tabularx}{\linewidth}{lcXccXcXcXrcc}
            \textbf{Weapon} & \textbf{Damage} & \textbf{Acc} & \textbf{Range} & \textbf{Weight} & \textbf{RoF} & \textbf{Shots} & \textbf{ST} & \textbf{Bulk} & \textbf{Rcl} & \textbf{Cost} & \textbf{LC} & \textbf{Notes}\\
            % name & damage & acc & range & weight & rof & shots & st & bulk & rcl & \$ & LC & Notes \\
            Gauss Machine Pistol, 4mm & 3d(3) pi- & 3 & 500/2,100 & 3/0.5 & 20 & 40(3) & 9 & -2 & 2 & \$2,600 & 2 & [2] \\
            Gauss Needler, 3mm & 2d(3) pi- & 2 & 100/300 & 1.5/0.5 & 12 & 100(3) & 7† & -2 & 2 & \$2,000 & 2 & [2] \\
            Gauss PDW, 4mm & 4d(3) pi- & 6+1 & 700/2,900 & 4.6/1 & 16 & 80(3) & 9† & -3 & 2 & \$3,600 & 2 & [3] \\
        \end{tabularx}\medskip

        \rowcolors{1}{}{\colorweaponry}
        \noindent {\normalsize GUNS (RIFLE) (DX-4, or most other Guns at -2)}
        \begin{tabularx}{\linewidth}{lcXccXcXcXrcc}
            \textbf{Weapon} & \textbf{Damage} & \textbf{Acc} & \textbf{Range} & \textbf{Weight} & \textbf{RoF} & \textbf{Shots} & \textbf{ST} & \textbf{Bulk} & \textbf{Rcl} & \textbf{Cost} & \textbf{LC} & \textbf{Notes}\\
            % name & damage & acc & range & weight & rof & shots & st & bulk & rcl & \$ & LC & Notes \\
            Sniper Railgun, 7mm & 6d×2(3) pi & 7+3 & 2,400/10,000 & 20/1.4 & 1 & 30(3) & 11B† & -6 & 2 & \$18,000 & 2 & [4] \\
            Gauss Needle Rifle, 3mm & 2d+1(3) pi- & 4 & 500/2,000 & 6/1 & 20 & 100(3) & 8† & -3 & 2 & \$3,000 & 2 & [3] \\
            Gauss Rifle, 4mm & 6d+2(3) pi- & 7+2 & 1,200/4,800 & 8.5/1.4 & 12 & 60(3) & 10† & -4 & 2 & \$7,100 & 2 & [3] \\
            Portable Railgun, 10mm & 5d×3(3) pi+ & 7 & 3,000/12,000 & 20/1.5 & 3 & 25(3) & 10† & -6 & 3 & \$18,000 & 1 & [3] \\
        \end{tabularx}\medskip

        \rowcolors{1}{}{\colorweaponry}
        \noindent {\normalsize GUNS (SHOTGUN) (DX-4, or most other Guns at -2)}
        \begin{tabularx}{\linewidth}{lcXccXcXcXrcc}
            \textbf{Weapon} & \textbf{Damage} & \textbf{Acc} & \textbf{Range} & \textbf{Weight} & \textbf{RoF} & \textbf{Shots} & \textbf{ST} & \textbf{Bulk} & \textbf{Rcl} & \textbf{Cost} & \textbf{LC} & \textbf{Notes}\\
            % name & damage & acc & range & weight & rof & shots & st & bulk & rcl & \$ & LC & Notes \\
            Gauss CAW, 18.5mm & 8d pi++ & 4 & 200/1,000 & 10/1.5 & 15 & 30(3) & 10† & -4 & 3 & \$2,400 & 2 & [3] \\
            Gauss Shotgun Pistol, 18.5mm & 8d pi++ & 2 & 200/1,000 & 3/0.5 & 3 & 10(3) & 10 & -3 & 4 & \$2,000 & 3 & [3] \\
        \end{tabularx}\medskip

        \rowcolors{1}{}{\colorweaponry}
        \noindent {\normalsize GUNS (GRENADE LAUNCHER) (DX-4, or most other Guns at -4)}
        \begin{tabularx}{\linewidth}{lcXccXcXcXrcc}
            \textbf{Weapon} & \textbf{Damage} & \textbf{Acc} & \textbf{Range} & \textbf{Weight} & \textbf{RoF} & \textbf{Shots} & \textbf{ST} & \textbf{Bulk} & \textbf{Rcl} & \textbf{Cost} & \textbf{LC} & \textbf{Notes}\\
            % name & damage & acc & range & weight & rof & shots & st & bulk & rcl & \$ & LC & Notes \\
            EMGL, 40mmG & 4d pi++ & 3 & 150/1,000 & 10/3 & 1 & 3(5) & 8† & -5 & 2 & \$7,000 & 1 & [3] \\
            Underbarrel EMGL, 25mmG & 4d pi++ & 4+2 & 360/2,200 & 2/1 & 1 & 3(3) & 10 & -- & 2 & +\$1,000 & 1 & [3] \\
        \end{tabularx}\medskip

        \rowcolors{1}{}{\colorweaponry}
        \noindent GUNS (LMG) (DX-4, or most other Guns at -2)
        \begin{tabularx}{\linewidth}{lcXccXcXcXrcc}
            \textbf{Weapon} & \textbf{Damage} & \textbf{Acc} & \textbf{Range} & \textbf{Weight} & \textbf{RoF} & \textbf{Shots} & \textbf{ST} & \textbf{Bulk} & \textbf{Rcl} & \textbf{Cost} & \textbf{LC} & \textbf{Notes}\\
            % name & damage & acc & range & weight & rof & shots & st & bulk & rcl & \$ & LC & Notes \\
            Gauss LSW, 4mm & 6d+2(3) pi- & 7+2 & 1,200/4,800 & 20/7 & 20 & 300(5) & 12B† & -5 & 2 & \$13.000 & 1 & [3] \\
        \end{tabularx}\medskip

        \rowcolors{1}{}{\colorweaponry}
        \noindent {\normalsize GUNNER (CANNON) (DX-4, or other Gunner at -4)}
        \begin{tabularx}{\linewidth}{lcXccXcXcXrcc}
            \textbf{Weapon} & \textbf{Damage} & \textbf{Acc} & \textbf{Range} & \textbf{Weight} & \textbf{RoF} & \textbf{Shots} & \textbf{ST} & \textbf{Bulk} & \textbf{Rcl} & \textbf{Cost} & \textbf{LC} & \textbf{Notes}\\
            % name & damage & acc & range & weight & rof & shots & st & bulk & rcl & \$ & LC & Notes \\
            Auto EMGL & 8d pi++ & 4 & 300/2,000 & 64/10 & 1 & 20(5) & 14† & -8 & 2 & \$54,000 & 1 & [4] \\
            Railgun, 40mm & 6d×25(3) pi++ & 8 & 8,000/29,000 & 4,000/150p & 20 & 200(5) & 57M & -10 & 2 & \$630,000 & 1 & [5] \\
        \end{tabularx}\medskip
        \label{tbl:electromagnetic_gun}

        \rowcolors{1}{}{\colorweaponry}
        \noindent {\normalsize GUNNER (MACHINE GUN) (DX-4, or other Gunner at -4)}
        \begin{tabularx}{\linewidth}{lcXccXcXcXrcc}
            \textbf{Weapon} & \textbf{Damage} & \textbf{Acc} & \textbf{Range} & \textbf{Weight} & \textbf{RoF} & \textbf{Shots} & \textbf{ST} & \textbf{Bulk} & \textbf{Rcl} & \textbf{Cost} & \textbf{LC} & \textbf{Notes}\\
            % name & damage & acc & range & weight & rof & shots & st & bulk & rcl & \$ & LC & Notes \\
            Gauss HMG, 7mm & 16d(3) pi & 8 & 3,000/12,000 & 64/20 & 20 & 200(5) & 20M & -8 & 2 & \$44,000 & 1 & [4] \\
            Gauss Minigun, 4mm & 10d(3) pi- & 8 & 1,800/7,200 & 64/20 & 100 & 1,000(5) & 20M & -8 & 2 & \$44,000 & 1 & [4] \\
        \end{tabularx}
    \end{table}

    \noindent [1] Powered by a B cell.
    
    \noindent [2] Powered by two B cells.
    
    \noindent [3] Powered by a C cell.
    
    \noindent [4] Powered by a D cell.
    
    \noindent [5] External power.
    
    \noindent The weapon's power cell provides enough energy for firing its specified number of Shots, and is included in the weight.\smallskip

    \hrule height 1pt\smallskip
}

\begin{table}[H]
    \subsection{Electromagnetic Gun Ammunition Table}
    \centering
    \rowcolors{1}{}{\colorweaponry}
    \begin{tabularx}{\columnwidth}{lXrXrXcX}
        \textbf{Ammo} && \textbf{WPS} && \textbf{CPS} && \textbf{LC} & \\
        % & Ammo && WPS && \$ && LC && \\
        3mm && 0.004 && \$0.04 && 3 & \\
        4mm && 0.006 && \$0.06 && 3 & \\
        7mm && 0.024 && \$0.24 && 3 & \\
        10mm && 0.08 && \$0.8 && 3 & \\
        18.5mm && 0.037 && \$0.37 && 3 & \\
        25mmG && 0.09 && \$0.9 && 3 & \\
        40mmG && 0.33 && \$5 && 3 & \\
        40mm && 6 && \$60 && 2 & \\
        64mm && 2 && \$20 && 2 & \\
    \end{tabularx}
    % \caption{Caption}
    \label{tab:electromagnetic_ammo}
\end{table}

\section{Gyrocs}\label{sec:gyrocs}
Gyrostabilized rocket launchers fire spin~-stabilized rockets the size of bullets. Ancient rocket pistols such as the Gyrojet were notably inaccurate and slow to accelerate. Modern developments in rocket fuels and micro~-electromechanical systems stabilize even unguided rockets, and allow miniaturized homing systems at extra cost. (Not all ``gyrocs'' actually use gyrostabilization -- some have smart skins that steer them in flight via tiny aerodynamic bumps or fins.)

Since they are propelled by a rocket motor, gyrocs have a flat trajectory with a maximum range similar to the 1/2D range. Gyroc launchers are also light compared to conventional guns -- almost half a typical gyroc weapon’s weight is its ammunition. They’re effectively recoilless, and quieter than ordinary guns. The hissing sound the rockets make is hard to localize: a Hearing roll is needed to spot the firer by sound alone.

Gyrocs have a few disadvantages. They’re less accurate than conventional bullets. Also, like most rockets, they take some time to accelerate: divide their piercing damage by 3 at one or two yards and by 2 at three to 10 yards. This limits their utility as civilian or police weapons unless using specialized (e.g., explosive) ammunition. Gyroc ammo is also bulky and expensive, which limits the number of shots their magazines can be loaded with. Users often rely on homing ammunition (see \textit{Gyroc Micromissiles}, below), substituting precision for volume of fire.

\subsubsection{Gyroc Weapons}\label{subsubsec:gyroc_weapons}
Gyrocs are available in several configurations. Typical gyroc weapons include:

\textit{Gyroc Carbine, 15mm:}\label{itm:gyroc_carbine_15mm} This is a popular infantry weapon, especially when loaded with armor~-piercing explosive rockets (such as HEMP ammunition, p. TODO).

\textit{Gyroc Launch Pistol, 15mm:}\label{itm:gyroc_launch_pistol_15mm} A semi~-automatic magazine~-fed rocket pistol.

\textit{Gyroc Light Support Weapon, 15mm:}\label{itm:gyroc_lsw_15mm} An electrically powered machine gun-sized gyroc with a large ammunition cassette and full automatic fire capability. A B cell provides up to 15 minutes continuous fire.

\textit{Gyroc Pistol, 15mm:}\label{itm:gyroc_pistol_15mm} A simple and compact weapon -- basically a four~-shot revolver. Different rockets can be loaded in each chamber.

\textit{Holdout Gyroc, 15mm:}\label{itm:holdout_gyroc_15mm} Also called the ``sleeve gyroc,'' this is an single~-shot rocket launcher. It’s often worn attached above the wrist.

\textit{Underbarrel Gyroc, 15mm:}\label{itm:underbarrel_gyroc_15mm} An alternative to a grenade launcher, this compact weapon is designed to be clamped onto (or built into) an assault rifle (any weapon with -3 or greater Bulk) for extra firepower. Use the Bulk, ST, and sighting bonuses of the weapon it is installed in.

\subsubsection{Gyroc Micromissiles}\label{subsubsec:gyroc_mircomissiles}
Gyrocs are often equipped with homing projectiles (sometimes called ``micromissiles'' or ``viper gyrocs'') -- see Homing Projectiles, p. TODO. Micromissiles are quite expensive, so troops may not be issued full magazines of them, receiving a few as ``silver bullets'' in addition to the regular gyroc ammo load.

\multicolinterrupt{
    \begin{table}[t]
        \hrule height 1pt\medskip
        \subsection{\textit{Gyroc Launcher Table}}
        \centering
        \noindent\centering GUNS (Gyroc) (DX-4, or most other Guns at -4)
        \small
        \rowcolors{1}{}{\colorweaponry}
        \begin{tabularx}{\linewidth}{lcXccXcXcXrcc}
            \textbf{Weapon} & \textbf{Damage} & \textbf{Acc} & \textbf{Range} & \textbf{Weight} & \textbf{RoF} & \textbf{Shots} & \textbf{ST} & \textbf{Bulk} & \textbf{Rcl} & \textbf{Cost} & \textbf{LC} & \textbf{Notes} \\
            % name & damage & acc & range & weight & rof & shots & st & bulk & rcl & \$ & LC & Notes \\
            Gyroc Carbine, 15mm & 6d pi++ & 2 & 1,900 & 4/1 & 3 & 10(3) & 7† & -3 & 1 & \$500 & 2 & \\
            Gyroc Launch Pistol, 15mm & 6d pi++ & 1 & 1,900 & 2/0.7 & 3 & 6(3) & 10 & -2 & 1 & \$300 & 3 & \\
            Gyroc LSW, 15mm & 6d pi++ & 2 & 1,900 & 12/3 & 10 & 30(5) & 10† & -4 & 1 & \$1,400 & 1 & \\
            Gyroc Pistol, 15mm & 6d pi++ & 1 & 1,900 & 1/0.4 & 3 & 4(3i) & 9 & -2 & 1 & \$200 & 3 & \\
            Holdout Gyroc. 15mm & 6d pi++ & 0 & 1,900 & 0.25/0.1 & 1 & 1(3i) & 6 & -1 & 1 & \$50 & 3 & \\
            Underbarrel Gyroc, 15mm & 6d pi++ & 2 & 1,900 & 1.5/0.7 & 3 & 6(3) & 6† & -- & 1 & \$150 & 2 & [1] \\
        \end{tabularx}\medskip
        \label{tab:gyroc_launcher}
        \begin{flushleft}
            [1] May be attached to any weapon of Bulk -3 to -6; use that weapon's Bulk.
        \end{flushleft}
    \end{table}


    \begin{table}[t]
        \subsection{Gyroc Ammunition Table}
        \centering
        \rowcolors{1}{}{\colorweaponry}
        \begin{tabularx}{\columnwidth}{lXrXrXcX}
            \textbf{Ammo} && \textbf{WPS} && \textbf{CPS} && \textbf{LC} & \\
            % Ammo && WPS && \$ && LC && \\
            15mm gyroc && 0.1 && \$5 && 3 & \\
        \end{tabularx}
        % \caption{Caption}
        \label{tab:gyroc_ammo}
    \end{table}
}

\section{Rockets and Missiles}\label{sec:rockets_missiles}
These are missile launchers larger than the gyroc weapons. The standard weapons are solid propellant rockets.

\subsubsection{Infantry Missile Launcher (IML)}\label{subsubsec:infantry_missile_launcher}
This is a single~-shot launch tube with a pistol grip and an electronics system. It holds one mini~-missile, but can be reloaded after each shot if extra missiles are carried. It is light enough (six pounds loaded) that every soldier could carry one.

The launcher fires a supersonic missile with a 64mm warhead. It produces a dangerous backblast when fired, doing 2d burning damage to everyone within a cone up to two yards behind the launcher.

Each missile costs \$100 without a warhead; homing missiles (p. TODO) cost more. The usual warhead is a solid ``kinetic kill'' projectile inflicting the listed piercing damage. The warhead costs \$10; multiply this figure for the more expensive warheads listed under \textit{Warheads and Ammunition} (p. TODO).

\subsubsection{Multiple Light Anti-Armor Weapon System (MLAWS), 64mm}\label{subsubsec:mlaws_64mm}
The MLAWS is a six~-tube launcher with a loaded weight of 35 pounds. It is quite hefty, but its lack of recoil allows an ordinary person to fire it. The MLAWS is used as a squad support weapon, although it’s not uncommon to see them attached to post mounts on vehicles or hung under the pylons of attack aircraft. The MLAWS fires the same missile as an IML (see above), with the same options and backblast hazard.

\subsubsection{Tactical Missile Launcher (TML), 100mm}\label{subsubsec:tml_100mm}
This bulky launch tube holds a single pre~-packaged missile. An unguided rocket costs \$400; missiles with guidance systems cost more. The basic warhead is a 100mm solid ``kinetic kill'' projectile that inflicts the listed piercing damage. This costs \$40; multiply this figure for the more expensive warheads listed under \textit{Warheads and Ammunition} (p. TODO). It has a potentially lethal backblast when fired, doing 4d burning damage to everyone within a cone up to three yards behind the launcher.

\multicolinterrupt{
    \begin{table}[t]
        % \hrule height 1pt\medskip
        \subsection{\textit{Missile Launcher Table}}
        \noindent ARTILLERY (GUIDED MISSILE) (IQ-5, or other Artillery at -4)
        \centering
        \small
        \rowcolors{1}{}{\colorweaponry}
        \begin{tabularx}{\linewidth}{lcXccXcXcXrc}
            \textbf{Weapon} & \textbf{Damage} & \textbf{Acc} & \textbf{Range} & \textbf{Weight} & \textbf{RoF} & \textbf{Shots} & \textbf{ST} & \textbf{Bulk} & \textbf{Rcl} & \textbf{Cost} & \textbf{LC} \\
            % name & damage & acc & range & weight & rof & shots & st & bulk & rcl & \$ & LC \\
            IML, 64mm & 6d×5 pi++ & 3 & 750/6,000 & 4/2 & 1 & 1(5) & 7† & -4 & 1 & \$2,000 & 1 \\
            MLAWS, 64mm & 6d×5 pi++ & 3 & 750/6,000 & 35/12 & 1 & 6(5) & 11B† & -8 & 1 & \$23,000 & 1 \\
            TML, 100 & 6d×25 pi++ & 3 & 1,500/15,000 & 35/25 & 1 & 1(20) & 11B† & -8 & 1 & \$10,000 & 1 \\
        \end{tabularx}\medskip
        \label{tab:missile_launcher}
        \begin{flushleft}
            All statistics are for ``baseline'' high~velocity rockets with solid warhead. Most weapons will fire homing projectiles (below) with a more specialized warhead.
        \end{flushleft}
        \hrule height 1pt
    \end{table}
}

\subsection{Homing Projectiles}\label{subsec:homing_projectiles}
Modern projectile weapons may contain sensors and steering systems that enable the projectile to home in on a target by itself.

Gyroc, missile, and rocket launchers often fire homing projectiles. Guns may fire homing projectiles if the homing system can fit in the bullet or shell -- this requires advanced technology for small caliber rounds and is not always available. Homing projectiles use the Homing Weapon rules (p. B413). The firer rolls against Artillery (Guided Missile) to aim. On a success, the missile gets its Acc bonus. The weapon's ``1/2D'' range is its speed in yards/second. The missile’s skill and type of homing attack depends on the type of homing systems installed:

\subsubsection{Infrared Homing (``Viper'')}\label{subsubsec:infrared_homing}
These inexpensive systems are available for 10mm or larger projectiles. 

They make a Homing (Infravision) attack. Projectiles 15mm or larger have a skill of 14, smaller projectiles have a skill of 13. +3 CF.

\subsubsection{Multi-Spectral Homing}\label{subsubsec:multi-spectral_homing}
These sophisticated guidance systems are available for
25mm or larger.

They can be set for ``passive'' homing, making a Homing (Hyperspectral Vision) attack. They can be set for ``anti~-radiation'' to track any radio or radar signals the target emits, making a Homing (Detect Radar and Radio) attack. Finally, they may be set for ``active'' homing, making a Homing (Imaging Radar) attack.

40mm or larger projectiles have a skill of 15, smaller projectiles have a skill of 14. +9 CF.

\subsubsection{Brilliant Weapons}\label{subsubsec:brilliant_weapons}
These are robotic missiles capable of autonomous flight and target selection. Unlike a normal homing weapon, which the user locks onto a target he can see or otherwise detect, a brilliant weapon is simply released to look for targets on its own. See \textit{Robot Weapons} (p. TODO) for examples of various brilliant weapons.

\section{Hand Grenades}\label{sec:hand_grenades}
Traditional hand grenades are convenient and deadly weapons in close combat – and a powered suit (p. TODO) or robotic body can throw them much further than humanly possible!

There are three standard grenade sizes:
\\

\textit{Hand Grenade:}\label{itm:hand_grenade} This is the standard grenade, about the size of a baseball. It has the same effect as a 64mm warhead. \$40, 1 lb.

\textit{Mini Hand Grenade:}\label{itm:mini_hand_grenade} An easy~-to~-conceal grenade the size of a golf ball. It has the effect of a 40mm warhead. \$10, 0.25 lbs.

\textit{Thimble Grenade:}\label{itm:thimble_grenade} A tiny grenade one inch in diameter. It has the same effect as a 25mm warhead. \$2.5, 0.06 lbs.

The effect of a grenade and its LC depends on the grenade’s warhead. See \textit{Warheads and Ammunition} (p. TODO). The cost given is the base cost for a high explosive fragmentation grenade. Other warhead types may have a multiple to cost.

Standard grenades have an activator handle and a two-second delay. To use the grenade, take one second to ``pull the pin'' and arm the grenade. The grenade will explode two seconds after the user releases the grenade (usually by throwing it).

\subsection{Smart Grenades}\label{subsec:smart_grenades}
These grenades incorporate a computer chip and microcommunicator (p. \pageref{sec:comms}). A smart grenade can be controlled by any computer terminal, usually a wearable system. To activate them, the user must first press an arming switch on the grenade (this is manual, to prevent unauthorized remote activation). The grenade sends out a signal, and if the user is in range, a grenade arming display pops up on the user’s interface. She can then select any menu option for the grenade.

The options are: a specified time delay (up to two weeks), command detonation (detonates by radio command; each grenade carried has its own frequency), impact fusing (goes off if struck, dropped, or thrown against a hard surface), or anti~-tamper fusing (as per command or delay, but goes off if touched). The user can reprogram the grenade if she uses its unique code, or she can lock the grenade so that its commands cannot be changed.

It takes three Ready maneuvers to program a smart grenade. Smart grenades also have a conventional pin that can be pulled, turning the grenade into an ordinary grenade that will go off two seconds after the grip is released. Sometimes a regular fuse is enough, especially when there’s no time to mess around with computer menus!

All hand grenades can be smartat no additional expense.

Smart grenades may have a message option – see \textit{Message Bombs} (p. \pageref{subsec:message_bomb}).

\subsection{Saucer Grenades}\label{subsec:saucer_grenades}
These grenades come in a aerodynamic disk shape, and are sheathed in a flexible rubberized plastic. They are armed the same way as other grenades, and come in both ordinary and smart versions. Their effect is the same as a mini~-grenade, but they’re bulkier due to their shape; only one can fit in a large pocket.

Use Throwing skill to hurl them, but instead of using the throwing rules, treat them as a thrown weapon with the statistics shown below. The rubberized sheath allows them to be bounced around corners: roll at -3 to get the grenade to do this. If a saucer grenade misses and scatters (p. B414), and an obstacle blocks it before it travels the full scatter distance, the grenade will bounce back the remaining yards in the opposite direction.

\subsection{Limpet Mines}\label{subsec:limpet_mines}
Limpets are similar to hand grenades, but are not balanced for throwing. Instead, they can stick (or unstick) to almost any surface upon receiving the correct communicator pulse. They can also be used as handheld weapons (with any preset delay) by slapping them on a target, from a human to a starship.

Limpets may be worn on armor as defensive decoys: e.g., limpets filled with prismatic smoke can be set to trigger instantly if laser sensors detect a laser beam. To remove a limpet without the proper code, roll vs. ST-5, one try per second. Pulling one off of flesh does one point of damage. Otherwise, limpet mines have the same statistics as smart grenades.

\multicolinterrupt{
    \begin{table}[H]
        \hrule height 1pt\medskip
        \subsection{\textit{Hand Grenade Table}}
        % \noindent ARTILLERY (GUIDED MISSILE) (IQ-5, or other Artillery at -4)
        \centering
        \small
        \rowcolors{1}{}{\colorweaponry}
        \begin{tabularx}{\linewidth}{lXcXcXccXccccXr}
            \textbf{Weapon} && \textbf{Damage} && \textbf{Acc} && \textbf{Range} & \textbf{Weight} && \textbf{RoF} & \textbf{Shots} & \textbf{ST} & \textbf{Bulk} && \textbf{Cost} \\
            % name & damage & acc & range & weight & rof & shots & st & bulk & \$ \\
            Hand Grenade && 64mm warhead && 0 && per ST & 1 && 1 & T(1) & 6 & -2 && \$40 \\
            Mini Hand Grenade && 40mm warhead && 0 && per ST & 0.25 && 1 & T(1) & 5 & -1 && \$10 \\
            Thimble Grenade && 25mm warhead && 0 && per ST & 0.06 && 1 & T(1) & 4 & -1 && \$2.50 \\
            Saucer Grenade && 40mm warhead && 2 && ×3/×5 & 0.5 && 1 & T(1) & 5 & -1 && \$40 \\
        \end{tabularx}\medskip
        \label{tab:hand_grenade}
        % \hrule height 1pt
    \end{table}
}