\section{Physical Weapons}\label{sec:physical_weapons}
These weapons inflict damage by cutting, crushing, or impaling their victim, or by delivering explosive devices. All modern weapons are \textit{fine} by default: -1 to break and +1 to cutting or impaling damage. Only \textit{one} weapon-quality grade and \textit{one} blade composition option can be applied to a weapon. 

\subsection{Karatands}\label{subsec:karatands}
These memory plastic glove are flexible, but harden into an edge when the user strikes someone. They have the same effect as brass knuckles, but they're not as obvious. They can also be installed in flexible armor. \$100 each, net. weight. LC3.

\subsection{Limpet Mine Dispenser}\label{subsec:limpet_mine_dispenser}
A close~-combat weapon designed to attach to a battlesuit or a robot's arm. It is a ``sleeve dispenser' for sticky limpet mines to slap onto the target. The mines attach themselves with molecular suction pads, then detonate after a preset interval.

To plant one, use Brawling or X. A successful hit does no immediate damage; instead it sticks a limpet mine onto the target.

The dispenser may be programmed to set mines with a time delay from 0 (going off at the end of the attacker's turn) to 100 seconds. Removing a limpet requires a Ready action and a successful ST roll, minus one~-tenth the DR of whatever the mine is stuck to or -20, whichever is less.

If the mine was stuck to flesh, it does 1 HP damage when pulled off. If a mine is slapped on a part that cannot be reached (for instance, the small of the back), it can't be removed without help.

Limpet mine dispenser magazines hold 10 limpet mines. Each mine has a 25mm warhead, and is identical to a shape~-charge limpet mine grenade. Limpet mines can be also stuck to the floor, walls, etc. for use as booby traps, but may not be thrown.

\subsection{Rocket Striker}\label{subsec:rocket_striker}
A great axe, pick, scythe, spear, or warhammer may be fitted with a rocket striker, a small liquid~-fuel engine that amplifies the force of the user's swing, thrust, or throw. A button the weapon's haft triggers the rocket engine; skilled users activate it at the right moment. It has enough fuel for 12 boosted attacks.

The rocket striker must be activated before the to~-hit roll. It adds +6 to Striking Strength. However, it also adds +3 to the weapon's ST requirement -- it is easier to lose control of the weapon! This drawback does not apply to thrown spears. Add \$500 and 1 lb. LC3.

\subsection{Superfine Blade}\label{subsec:superfine_blade}
This is a weapon-quality grade (see \textit{Melee Weapon Quality}, p. B274). Superfine blades are advanced alloy, ceramic, or crystalline blades superior to steel. Any edged weapon that does cutting or impaling damage can have a superfine blade. It adds +2 to cutting and impaling damage and has a (2) armor divisor. Superfine blades are at -3 to break when parrying (see \textit{Parrying Heavy Weapons}, p. B376). Superfine blades are six times normal cost. LC4.


\subsection{Monowire Blade}\label{subsec:monowire_blade}
This is a blade-composition option (see \textit{Blade Composition}, p. B275). Monowire weapons owe their superior cutting ability to a strand of super~-strong wire a few molecules thick, which is stretched along the edge of a reinforced sword or knife. 

Monowire blades inflict +2 cutting damage and get a (10) armor divisor. Since the monowire is only along a blade's edge, it cannot cut into a flat surface. Any melee or thrown weapon that inflicts cutting damage can be made into a monowire version for 10 times the normal cost. All blade-quality options are available, but they \textit{only} affect breakage chance, not weapon damage or armor divisor. LC3

\subsection{Monowire Whip}\label{subsec:monowire_whip}
This is a weighted length of monomolecular wire attached to a short handle. It is a dangerous weapon, especially in the hands of an unskilled user (who may lose control of the weapon and injure themself with it). A control allows the wielder to vary length from one to seven yards, changing both reach and ready time. Adjusting the length requires a Ready maneuver.

When used to snare an opponent or weapon, the whip cuts into its target, inflicting thrust+1d(10) cutting damage every turn it is pulled taut until the victim escapes. A ``drop weapon'' critical miss indicates the wielder hit themself or a friend. For other rules, see p. B406. LC2.

\subsection{Monowire Switchblade}\label{subsec:monowire_switchblade}
This weapon combines elements of both a monowire blade and whip. It consists of a weighted monomolecular memory wire attached to a powered knife hilt. As long as the hilt feeds an electrical current into the ``smart'' wire, the wire remains rigid like a sword. Toggle switches in the hilt allow the user to play out more wire to vary the blade from 0 inches (retracting into the hilt) to 15 feet, or to turn the current on or off. If the current is off, the wire becomes a flexible razor~-sharp monowire whip. Changing length or switching the current on and off requires a Ready maneuver.

As a rigid weapon, the monowire switchblade's reach may vary from C to 5. It does swing +1d +R(10) cutting damage, where R is the current reach (treat C as 0). It cannot thrust. The switchblade requires Force Sword skill when rigid. It can parry normally. The user must have enough room to swing the weapon: reach 3 to 5 isn't possible without many yards of vertical or horizontal space. As a flexible weapon, the reach may vary from 1 to 5 yards, and it functions like a monowire whip (p. \pageref{subsec:monowire_whip}). If it runs out of power, the memory wire can no longer stay rigid, and the weapon functions only as a whip. B/10 hr. LC2.

\subsection{Vibroblade}\label{subsec:vibroblade}
This is a blade-composition option. These blade weapons vibrate thousands of times per second. Any edged weapon that does cutting or impaling damage can be a vibroblade. Turning on the vibro effect takes a Ready action. A successful Fast~-Draw roll activates it as the blade is drawn.

A vibroblade adds +1d to cutting damage and has a (3) armor divisor. This armor divisor increases to (5) if the blade is also superfine. If the vibro effect is turned off, it function like an ordinary blade (with the normal benefits of superfine construction, if applicable).

The blade vibrates so rapidly that its movement is invisible, and it is impossible to tell a vibroweapon from a regular weapon of the same type. A Hearing roll made from one yard away will detect a faint hum that marks a vibroweapon for anyone familiar with it. Anyone parrying (or whose weapon is parried by) a vibroblade will recognize its nature as the blade cuts into their own.

Vibroblades are powered by C cells; the cell powers them for 300/weapon weight seconds. Thuse, a half~-pound knife operates for 600 seconds. Vibroblades cost 10 times as much as regular weapons (30 times as much if it also superfine). LC3.

\subsection{Additional Melee Weapon Options}
The following options can also be applied to melee weapons:

\textit{Balanced:} +1 to skill. Multiply cost by 5.

\textit{Nanomaterials:} This is a blade-composition option. These weapons use advanced composites and metal laminates to create blades that are lighter, stronger, and hold an edge better than steel. Halve weight and double cost. Use \textit{original} weight of the weapon when checking for breaking. Most nanomaterial weapons are also very fine or superfine.

\textit{Poorly Balanced:} -1 to skill. Multiply cost by 0.5. Mutually exclusive with balanced.

\textit{Styled:} Many weapons are styled, especially if they are ceremonial or coveted tools. See \textit{Styling}, p. \pageref{subsec:styling}.

\textit{Vibrowire Blade:} This is a blade-composition option. It combines vibroblade technology with small monomolecular cutting teeth, with effects similar to a chainsaw -- a notable \textit{not} elegant weapon! Vibrowire blades add +2d to cutting damage, with a (5) armor divisor, or (10) if superfine. If it fails to penetrate the DR of the target, immediately check for weapon breakage. A broken blade whips around and strikes the wielder for 2d(5) cutting damage. Vibrowire blades cost 30 times as much as regular melee weapons.

\section{Energy Weapons}\label{sec:energy_weapons}
These include contact energy~-discharge weapons, as well as weapons that generate a blade of energy.

\subsection{Electric Stun Wands}\label{subsec:electric_stun_wands}
Also called shock clubs or stun sticks, these batons use low~-powered electric currents to disorganize nerve function -- an effect called electromuscular disruption. 

The victim gets a HT-5 roll to resist. Nonmetallic armor gives a bonus equal to its DR, for other armors the stun effect has a (0.5) armor divisor: add +2 to HT for every DR 1. On a failure, the victim's voluntary muscles convulse, and he is knocked down and paralyzed. He may roll vs. HT-5 each second to recover (armor provides no bonus to these rolls); however, the user may take a Concentrate maneuver to hold the baton in contact. This prevents recovery until it is removed, but drains a charge per second. 

Stun wands are wielded using Shortsword skill. They use a B cell and strike 20 times before losing power. They may be purchased either as batons or jointed for the same cost. Jointed only does the stun effect, while batons do damage as a baton (swing \textit{or} thrust cr). \$100, 1 lb. LC4.

\subsubsection{Zap Glove}\label{subsubsec:zap_glove}
A zap glove looks like a heavy glove, but it contains electrical insulation (for the wearer) and a high~-voltage generator. A person can attack with a zap glove by touching the victim. Boxing, Brawling, or Karate allow the zap and normal damage simultaneously; Judo, Wrestling, or a normal grapple apply the zap before any other effect. No attack roll is needed in social situations such as shaking hands.

A zap glove has two settings: ``stun'' and ``kil.'' Changing settings takes a ready maneuver. On ``stun,'' the effect is the same as an electric stun wand. On ``kill,'' the zap glove does 2d burning damage and uses the rules for lethal electrical damage (p. B432).

A B cell in the lining of the glove provides sufficient power for 10 zaps (each zap on ``kill'' setting counts as two). The glove protects the hand with DR 5. It cal also be built into existing armor or vacc suit gauntlets. This increases the armor's cost and weight by \$400 and one pound. LC3.

\subsection{Neurolash}\label{subsec:neurolash}
These contact neural disruptor weapons use neural induction technology to stimulate paralysis, pain, or orgasmic pleasure in the brain and nervous system.

Neurolashes deliver a HT-5 (2) affliction attack. Failure means the victim suffers a particular affliction for minutes equal to the margin of failure. The affliction suffered depends on the type of neurolash:

\textit{Agony:}\label{itm:neurolash_agony} The victim suffers the Agony incapacitating condition* (p. B428). After recovery, she suffers Moderate Pain (p. B428) for an equal length of time.

\textit{Ecstasy:}\label{itm:neurolash_ecstasy} As above, but the victim suffers Ecstasy* followed by Euphoria (p. B428).

\textit{Neural Stun:}\label{itm_neurolash_neural_stun} The victim suffers the Unconsciousness incapacitating condition (p. B429). 

\textit{Paralysis:}\label{itm_neurolash_paralysis} The victim suffers the Paralysis incapacitating condition (p. B429). 

\textit{Seizure:}\label{itm_neurolash_seizure} The victim suffers the Seizure incapacitating condition (p. B429). 

*If struck by the Agony or Ecstasy attack, a failure by 5+ causes a Heart Attack mortal condition (p. B429).

% \textit{Tunable Weapons:} Each extra setting after the first adds 0.5 CF. Changing settings is a Ready maneuver.
%
A neurolash is usually integrated into a baton or whip, but may be added to any melee weapon. A neurolash generator is not compatible with force blade, sonic, vibro, or monowire weapons. Add \$500, 0.5 lb., and a B cell (20 strikes). LC3.

\subsubsection{Neuroglove}\label{subsubsec:neuroglove}
The neuroglove delivers a neural shock by touch. It functions like a neurolash, but the largest contact area of the glove makes it more effective: it delivers a HT-6 (2) affliction attack. It can be used to strike with, or to ambush unsuspecting victims by shaking hands with them. Gloves of all neurolash varieties are available

A neuroglove resembles and ordinary winter glove, and has DR 2. Any damage to the hand that penetrates its DR has a 1~-in~-6 chance of wrecking it as a weapon. \$500, 0.5 lb., B cell (20 strikes). LC2.

\subsection{Sonic Shuriken}\label{subsec:sonic_shuriken}
This throwing weapon is designed for use by assassins and commandos. A sonic shuriken appears to be a one~-inch plastic disk. When activated and thrown it emits a disk of coherent sound twice its own diameter. Due to its small power source, the sonic blades only last for a second, but this is enough time for it to hit its target.

For an extra \$50, a sonic shuriken may be fitted to spray a drug, poison, or virus along the disk (two doses are required). This is a follow~-up attack -- if the shuriken penetrates armor, it delivers its payload. 

A sonic shuriken uses an A cell, which is completely drained after one use. It is reusable, if its power cell is replaced. LC2.