\section{Psi~-Interface Technology}\label{sec:psi-interface_technology}
Psi~-interface or ``psiberface'' technology is used to link complex psionic equipment with an operator's mind. Unless noted otherwise, all psychotronic equipment requires a psiberface connection. It is related to neural interface (p. \pageref{sec:neural_interfaces}) technology. All psi~-interface gear may also interface with anything that a neural interface can.

\subsection{Psiberface Port}\label{subsec:psiberface_port}
This is a cable socket in a psychotronic device that facilitates the attachment of a psiberface unit. Plugging a psiberface unit into the port takes two seconds. Many devices come with psiberface ports, but extras can be added: \$500, 0.25 lb. apiece. Wireless versions (with a range of about 100 yards) are double cost. LC4.

\subsection{Psiberface Helmet}\label{subsec:psiberface_helmet}
A psiberface version of a neural induction helmet (p. \pageref{itm:neural_induction_helmet}), this lightweight helmet is lined with psi-sensitive electrodes and neural-induction probes. Its 6'-long cable can plug into any psychotronic device with a compatible port. Donning a psiberface helmet takes two seconds. This functionality can be built into the helmet of armor or a vacc suit (1.25× cost). \$7,000, 2 lb. B/100 hr. LC4.

\subsection{Psiberface Implant}
A psiberface version of a neural interface implant (p. \pageref{subsec:neural_interface_implant}). There are two models available:

\subsubsection{Psiberface Jack}\label{subsubsec:psiberface_jack}
This is a socket implanted into the body with a psiberface port. This allows the user to connect with any psychotronic tech with a compatible port. Additionally, works as a neural jack (p. \pageref{subsubsec:neural_jack}).

\textit{Statistics:} Accessory (Psiberface Port) [1]; Cable Jack (Sensie, +80\%) [9]; \textit{10 points.}

\textit{Accessibility:} Minor procedure. \$8,000. LC3.

A neural jack can be upgraded to a psiberface jack as a Simple procedure for \$4,000.

\subsubsection{Wireless Psiberface}
This is a wireless psiberface implant that uses a radio with a 100 yd range. It also functions as a wireless neural interface (p. \pageref{subsubsec:wireless_neural_interface}), when used this way, it has a one~-mile range.

\textit{Statistics:} Accessory (Wireless Psiberface Port) [1]; Radio (reduced Range, ×1/10 -30\%; Secure, +20\%; Sensie, +80\%) [17]. \textit{18 points}

\textit{Accessibility:} Minor procedure. \$13,000. LC3.

A wireless neural interface can be upgraded to a wireless psiberface as a Simple procedure for \$8,000.

\subsection{Psiberface Field}\label{subsec:psiberface_field}
This works like a psiberface helmet but covers an area. Anyone entering the field is connected to the systems it controls. Chair-sized field: \$50,000, 25 lb. Larger field (usually built into a floor): a basic \$200,000 and 100 lb., plus \$10,000 and 100 lb. per square yard covered. External power. LC2.

\subsection{Brainlock}
A psiberface device may include a brainlock (p. \pageref{subsec:brainlocks}) at no extra cost.

\section{Psi~-Amplifiers}\label{sec:psi-amp}
``Psi~-amps'' are psychotronic devices that use targeted neural stimulation to boost one or more psionic talents. MOst benefit a single power; e.g., Telepath or Psychokinesis. Some designes amplify \textit{several} powers; switching between powers takes a second. A psi~amplifier is capable of increasing a psi's Talent beyond the standard four~-level limit. The extra skill can be and often is used to facilitate extra effort (\textbf{\textit{GURPS Psionic Powers}}, p. 7). When using a psi~-amp for extra effort, halve the FP cost: 1 FP instead of the usual 2 FP.

A psi-amp should be attuned to the user, and can only be attuned to one psi at a time. This takes an hour and requires a successful Electronics Operation (Psychotronics) roll. Failure wastes time but allows further attempts; critical failure damages the device. It is possible to use an amplifier that isn't properly attuned or that's attuned to someone else, but any roll of 15+ while doing so counts as a critical failure.

The power surge a psi experiences when using an amplifier can be dangerous. If he ever rolls a critical failure while using an enhanced ability, he suffers amplified psychotronic feedback in addition to the usual critical failure effects. This burns out the machine, which will require minor repairs (p. B484). Moreover, the user must make a HT roll at a basic +3 but with a penalty equal to the machine's psi Talent boost. Failure means he suffers a seizure (p. B429) for seconds equal to the margin, with the usual 1d FP loss afterward; failure by 5+ indicates a coma (p. B429). Critical failure further inflicts 2d burning damage per \textit{second} on him, bypassing all DR (it's his brain being fried!), until someone else pulls him free; if he survives, he must also roll vs. Will at -3 or suffer ``brain-burn.'' A brain~-burn victim is effectively reduced to a mindless state, though recovery is possible given proper care and treatment.

\subsection{Psi~-Amplifier Headband}\label{subsec:psi-amp_headband}
This compact device gives +2 to Talent for a single psi power. \$6,000, 1 lb., 2B/1 month. Per additional power it can boost: +\$3,000, +0.25 lb. LC3.

\subsection{Psi~-Amplifier Helmet}\label{subsec:psi-amp_helmet}
This medium~-powered psionic amplifier gives +4 to Talent for a single power: \$25,000, 4 lb., 2C/1 month. Per additional power it can boost: +\$10,000, +2 lb. LC3.

\subsection{Backpack Psi~-Amplifier}\label{subsec:backpack_psi-amp}
A portable psi~-boosting device that consists of a backpack-sized power pack connected to a helmet. It gives +6 to a single power: \$40,000, 25 lb., 2D/1 month. Per additional power it can boost: +\$20,000, +10 lb. LC3.

\subsection{Psi~-Amplifier Throne}\label{subsec:psi-amp_throne}
This is a throne-like chair with a helmet and computerized biofeedback monitors. The user sits in the chair and power floods through him, to be channeled into psionic energy. Unless the user is very powerful, machines that amplify Teleportation will move the user but not the amplifier! It gives +8 to the user's Talent for a single power. \$200,000, 1,000 lb., external power. Thrones that can amplify more than one power at once are available: +\$100,000, +500 lb. per extra power. LC3.

\subsection{Psi~-Amplifier Citadel}\label{subsec:psi-amp_citadel}
The ultimate psi-amplifier system! The user's body is protected within a life-support system, cryogenically cooled and placed in suspended animation. His \textit{brain}, however, is kept conscious, its functions amplified to an unheard-of degree and supercharged with a tidal wave of psychotronic energy: +10 to his Talent for a single power. Preparing the user (attaching him and synchronizing the cybernetic systems) or disconnecting from the device takes 10 minutes, halved on a successful Electronics Operation (Psychotronics) roll. No psiberface system is needed; it's integral to the citadel. \$1,000,000, 4,000 lb., external power. Citadels that can amplify more than one power at once are available: +\$500,000, +2,000 lb. per extra power. LC2.

\subsection{Universal Psi~-Amplifier}\label{subsec:universal_psi-amp}
It is possible to create amplifiers that can divide their talent boost among more than one power, as desired. Adjusting bonuses requires a Concentrate maneuver. \textit{Triple} the price of a single~-powered model.

\subsection{Dedicated Psi~-Amplifier}\label{subsec:dedicated_psi-amp}
Highly focused psi~-amplifiers can benefit specific \textit{abilities} instead of entire powers, boosting one particular psi skill rather than a Talent. This makes them significantly more potent: increase the bonus by +2. Other stats are unchanged. This is incompatible with the universal option.

\section{Psychotronic Generators}\label{sec:psychotronic_generators}
Psychotronic generators constitute an entire category of gadgets. Each duplicates the effect of one psi ability; it collects and focuses psionic energy for that specific purpose
only. Such a device might exist for any psionic ability that has an associated psi skill. In all cases, the operator must be integrated into the machine in some way -- touching it, strapped
into it, wielding it, etc.

Psychotronic generators come in endless shapes and sizes, but typical examples have metal or plastic cases that house electronic circuits, crystalline components, and perhaps organic elements. Devices that emulate abilities that affect the user are commonly built as helmets, backpacks, or belts. Machines that enhance or add senses often incorporate goggles, cameras, or visors -- or boxes or consoles with some form of audio or visual output. Contrivances that radiate a field over an area are typically stationary boxes or wearable modules, often sporting antennas. Gadgets that affect distant targets tend to resemble weapons or ray projectors. And those that must touch their subject incorporate prods, gauntlets, or electrodes.

Any such device works exactly as if the operator had the specified psi ability, with these exceptions:

\begin{enumerate}
    \item All rolls for the ability use Electronics Operation (Psychotronics) in place of the ability's psi skill, and psi techniques default to Electronics Operation at their usual penalties. This makes a psychotronic generator relatively easy to use: the operator needs to learn a single Average skill instead of several Hard ones. However, different types of generators are mutually unfamiliar (see \textit{Familiarity}, p. B169), and the GM should enforce any penalties rigorously. Users with psionic capabilities may add their psi Talent to rolls for suitable abilities, but their psi skills are of no value here.
    \item When using a psychotronic generator, a critical failure doesn't require a Will roll to avoid crippling the ability. Instead, roll against the generator's HT (usually 10). Failure indicates a breakdown. Getting it working again calls for minor repairs (p. B484) using Electronics Repair (Psychotronics).
    \item Psychotronic generators can be nursed toward extra effort, but are more fragile than living psis. Use a standard IQ-based Electronics Operation roll instead of a Will-based roll, and double the usual penalty. Any critical failure while using extra effort causes a malfunction and breakdown, in addition to whatever other critical failure effects the GM assesses.
    \item Psychotronic generators aren't cumulative with natural psi abilities. Similarly, they cannot be used in a gestalt with other generators (or other psis).
\end{enumerate}

\subsection{Design}\label{subsec:design_psychotronic_generators}
Use the Psychotronic Generators Table to determine a psychotronic generator's cost, weight, and other stats. Dollar cost increases with the point cost of the ability emulated. Compact designs cost more per point to build, so powerful generators tend to be larger.

Psychotronic generators that resemble beam weapons or the like often function as if their ability had the Weaponized limitation (\textit{\textbf{GURPS Psionic Powers}}, p. 21). To simplify calculations, it's easiest to pair Weaponized (-50\% or -80\%) with Accurate 10 (+50\%) or 16 (+80\%) to offset it, thereby keeping point cost -- and dollar cost -- the same, and ensuring that the newly Weaponized ability has a decent chance to hit. 

Generators are normally electrically powered, but can be self-powered for 1.5× cost. Either way, abilities that cost FP to use still cost FP, in addition to any electrical power the generator requires. The FP can be drained from the user or provided by an attached psychotronic battery (p. \pageref{subsec:psychotronic_battery}).

\subsection{Psychotronic Generators Table}
\textit{Size:} A descriptive term for the device; SM appears in parentheses. A semi-portable or large generator is too big to wield manually (at least for a human!); thus, any ``touch'' effect involves a platform, electrode helmet, bed, chair, etc. into or onto which the subject must be strapped or placed in order to be affected by the ability.

\textit{Cost:} The cost of a powered generator, figured from the point cost of the ability it emulates. Multiply this by 1.5 for a self-powered model that has no electrical power requirement.

\textit{Weight:} The weight of a standalone generator. Optionally, it might be integrated into a mundane device (gun, TV, goggles, etc.) that retain its normal functions, provided that the generator weighs no more than 1/3 of that item's original weight.

\textit{Power:} The electrical power requirement for a powered generator, giving six hours of operation on batteries or a day on power cells. Ignore this for self-powered gadgets!

\textit{LC:} The Legality Class if the effect is ostensibly benign -- weather control, healing, communication, etc. Halve this and round down if the most likely uses are criminal, military, or espionage activities (GM's decision). Generators that can harm or control individuals are LC2 or worse.

\multicolinterrupt{
\begin{table}[H]
    \centering
    \hrule height 1pt\smallskip
    \rowcolors{1}{}{\colormedical}
    \begin{tabularx}{\linewidth}{lXcXcXcXcX}
         \textbf{Size} && \textbf{Cost} && \textbf{Weight} && \textbf{Power} && \textbf{LC} & \\
         % size && \$ × point cost && lb. && power && LC & \\
         Mini (SM -6) && \$3,000 × point cost && 0.3 lb. && 2A/1 day && 4 & \\
         Small (SM -4) && \$2,500 × point cost && 3 lb. && 2B/1 day && 4 & \\
         Portable (SM -2) && \$2,000 × point cost && 30 lb. && 2C/1 day && 4 & \\
         Semi~Portable (SM 0) && \$1,500 × point cost && 300 lb. && 2D/1 day or external power && 3 & \\
         Large (SM +2) && \$1,000 × point cost && 3,000 lb. && E/1 day or external power && 3 & \\
    \end{tabularx}
    % \caption{Caption}
    \label{tab:psychotronic_generators}
\end{table}
\begin{calloutbox}
        \section{Examples of Psychotronic Generators}
    \begin{multicols}{2}
        \textit{Akashic Terminal:} A humming, hissing, liquid-cooled electromechanical device the size of a room, within which the subject is suspended, bathed in scanning rays, his possible futures flashing on a bank of monitors above him. Gives Prognostication 4. Large, \$33,000, 3,000 ls., external power. LC3.
    
        \textit{Astral Blade:} A large knife, covered with exotic patterns, whose hilt conceals a solid-state crystalline psychotronic generator that mirrors the knife in the astral plane. Gives Astral Sword 1 (and also works as a large knife). Mini, \$36,000, 1 lb. (including knife), self-powered. LC2.
    
        \textit{Psiberdeck:} Small electronic device resembling a 1980s game console, with attached head electrodes. Gives Netrunning 1. Small, \$50,000, 3 lb., 2B/1 day. LC4.
    
        \textit{Psycho-Surgery:} Sinister dentist chair-like device with a blank-faced helmet. The subject is strapped in; the operator uses an attached interface helmet and virtual-reality console. Gives Mental Surgery 1, Mindwipe 1, and Telereceive 1. Semi-portable, \$76,500, 300 lb., external power. LC1.
    
        \textit{Radionic Healing Crystal:} A small, geometrical crystal-and-metal device, resembling a futuristic salt shaker, that's passed over the subject's body to activate it. Gives Cure Disease 1. Mini, \$27,000, 0.3 lb., self-powered. LC4.
    
        \textit{Teleport Belt:} A thick metallic belt composed of linked platinum ovals and psi-charged quartz crystals, with a built-in power pack. Mentally controlled; allows the operator to teleport up to two miles. Gives Autoteleport 8. Mini, \$210,000, 0.3 lb., 2A/1 day. LC4.
    \end{multicols}
\end{calloutbox}
}

\section{Other Augmentation Devices}
These technologies offer alternative means of intensifying psionic power. They can be used in conjunction with psi~-amplifiers (p. \pageref{sec:psi-amp}).

\subsection{Gestalt Web}\label{subsec:gestalt_web}
A gestalt web machine is a large psychotronic device attached to two or more nearby psiberface units (p. \pageref{sec:psi-interface_technology}). It automatically links all psis using those psiberface units into a gestalt (\textbf{Psionic Powers}, p. 9). This requires no skill roll -- the effect is identical to the Gestalt Familiarity perk (\textbf{Psionic Powers}, p. 19). A gestalt web capable of linking two minds is \$1,000,000, 400 lb. Add \$20,000 and 10 lb. per additional mind it can accommodate. The psiberface systems are extra. External power. LC3.

\subsection{Psychotronic Battery}\label{subsec:psychotronic_battery}
This is a means of storing and draining psionic energy. It typically resembles a small metal or crystal object, usually a geometric solid, although it might be built into another device. It responds to the mental control of any psi who touches it, and can be set to ``positive'' or ``negative.''

On its negative setting, it drains psychic energy from the nearest sapient being within two yards. He loses 1 FP every 10 minutes and cannot recover his own lost FP. Draining continues until the battery has absorbed 10 FP, after which it is full and no longer drains energy. Left unused, energy in the battery bleeds off at the rate of 1 FP every 12 hours.

On its positive setting, any psi who's touching the battery may tap it. He can draw up to 1 FP per second from it, using this energy instead of or as well as his own FP to power psionic abilities. The battery cannot be used to energize anything \textit{but} psi; it's effectively a psionic Energy Reserve.

A baseline psychotronic battery like the one above is \$10,000, 0.1 lb. Ones that hold more than 10 FP are possible; every doubling of FP capacity multiplies cost \textit{and} weight by 10. LC3.

\subsubsection{Dedicated Psychotronic Battery}
Some psychotronic batteries supply energy useful only for one specific power (e.g., Telepathy) or ability (e.g., Telesend). Power-specific versions hold 1.5× the FP; ability-specific ones store 2× the FP. In either case, the user can draw 2 FP/second. Treat these as standard batteries in all other respects.

\subsection{Symbiotic Crystal}\label{subsec:symbiotic_crystal}
This is a ``living'' psychotronic crystal, typically the size and shape of a silver dollar. These are impossible to manufacture and are only found on a handful of planets, location of most of which are closely guarded secrets of the Witchhunters.

A symbiotic crystal acts as a focus to refine a psi's gifts, allowing greater precision. By touching the crystal and staring into its depths, the owner can focus one psi ability at a time through its pseudo~-mind, increasing his effective skill level by 1/3 (round down). For instance, a telepath focusing Mental Stab~-13 through a symbiotic crystal would have an effective Mental Stab skill of 17. Using the crystal as a focus always calls for an \textit{extra} Concentrate maneuver; add this to the usual time required to invoke the psi ability.

After using a crystal once, the psi becomes mentally bonded to it. He is not required to use it to enhance his skills, but no other being can ever do so. He's also able to sense the crystal's location over a distance. To determine sensing range, consult the \textit{Psionic Range Table} (\textbf{GURPS Psionic Powers}, p. 22); the psi's effective level for this purpose is his Will/2 + his highest psi talent, rounded \textit{down}.

While the crystal is within range of its owner, he experiences anybody else touching it as a violation of his mind. He must make an immediate Will roll to resist ill effects \\

{\color{Cerulean}
    Modifiers: -4 if the person touching it is a psi; +2 if the person touching it loves the owner, -2 if he hates him, no modifier otherwise.
}\\

Success means the psi experiences moderate pain (p. B428) while the crystal is being touched. On a fail, he suffers agony (p. B428) the entire time, and then for seconds afterward equal to his margin of failure. Critical failure causes a heart attack (p. B429).

A symbiotic crystal has SM -10, DR 8, and HP 1. If it's destroyed within the bonded psi's sensing range, the owner must roll against Will at -10 to avoid shock. On a success, he's merely stunned. Failure indicates a heart attack -- and if he survives, he lapses into a coma (p. B429) for weeks equal to his margin of failure. Critical failure means death!

A symbiotic crystal costs \$1,000,000 and has negligible weight. LC3.

\section{Anti-Psi Technology}
These devices restrain, disrupt, or protect against psionic powers. They're related to the Anti~-Psi power (\textbf{GURPS Psionic Powers}, pp. 23-26) -- and psi-amps and psychotronic generators for that power fll into this category, too.

\subsection{Electro-Psionic Neutralizer}\label{subsec:electro-psionic_neutralizer}
This device is a means of removing psionic powers from a subject -- likely a prisoner. It resembles an electroconvulsive therapy (``electroshock'') machine: a laptop~-sized control and power unit connected by a cable to a headphones-like set of electrodes. When attached to a psi's head and properly adjusted, a brief treatment can cripple his psi abilities.

Once the electrodes are in place, each neutralization session starts with an Electronics Operation (Psychotronics) roll by the operator, to calibrate the unit and synchornize it to the subject's brain. This takes 30 seconds. Then the neutralizer is activated, whereupon it delivers a two-second electrical pulse.

The subject gets a HT-6 roll to resist. Success means he merely loses 1 FP from the stress. Failure indicates he suffers an immediate seizure (p. B429, including loss of 1d FP) followed by moderate pain (p. B428) in the form of a headache that lasts until he has recovered all FP lost to the seizure. In addition, all of his psionic powers are \textit{crippled} indefinitely. A month after neutralization and every month thereafter, he may try a HT-4 roll fo reach power, with success meaning he regains it. This restores \textit{one} level of any ability that comes in levels, with the remainder returning at the rate of one level/week.

Crippling a psi power or ability with an electro-psionic neutralizer normally renders it completely unusuable. If the HT roll to resist fails by only 1, thought, the effects are partial and unpredictable -- roll instead on the table under \textit{Optional Crippling Rules} (\textbf{GURPS Psionic Powers}, p. 7).

Psionic science has also been able to identify which parts of the brain are associated with what gifts, meaning that a neutralizer can be tuned to affect only \textit{certain} powers or abilites. This requires both a scan of the brain (obtain with an EEG, p. \pageref{sec:eeg} from a diagnostic bed, medscanner, HyMRI, etc.) and a database with esper brain diagrams (generally included with the Electro~-Psionic Neutralizer). The Electronics Operation (Psychotronics) roll is at -2 to calibrate it to cripple one specific power or -4 for a particular ability. Attempting either increases calibration time to 10 minutes per attempt.

Complete suitcase~-sized device: \$10,000, 10 lb. 4C/4,000 uses. LC2.

\subsection{Null-Field Generator}\label{subsec:null-field_generator}
Also see \pageref{subsec:power_damper} for a related, weaker tool.

A null-field generator projects anti-psionic interference patterns that disrupt or absorb all natural uses of psi within the area covered. This works identically to the Psi Static advantage (p. B78). The null field's disruption applies both to psis inside the field attempting to use their abilities and to those outside the field trying to affect anything within it (e.g., a psi couldn't teleport into a null field from outside it). Psis who attempt to use their powers from within a null field or project their powers into it perceive it as a cold, oppressive ``dead zone.'' Size varies, but these examples are typical:

\textit{Pocket Null Field:}\label{itm:pocket_null_field} This device is about the size of a paperback book and often worn on a belt. It covers a two-yard radius around the user. \$2,000, 0.4 lb., 4B/1 month. LC3.

\textit{Portable Null Field:}\label{itm:portable_null_field} This suitcase-sized generator projects a null field over a 10-yard radius. It may be set to affect a smaller radius, if desired. People who fear psi-eavesdropping often use portable nulls as anti-surveillance devices. \$50,000, 10 lb., 2C/1 month. LC3.

\textit{Semi-Portable Null Field:}\label{itm:semi-portable_null_field} This generator fits in a truck bed and projects a null field over a 20-yard radius. It may be set to affect a smaller radius, if desired. \$200,000, 250 lb., E/1 month. LC3.

\textit{Null-Field Tower:}\label{itm:null-field_tower} This large generator, mounted in a tower 30' high, projects a powerful null field that blankets a 100-yard radius -- enough to protect a large installation or neighborhood. A series of such towers could nullify psi powers over an entire region! \$50,000,000, 1,000 lb., external power. LC2.

\subsection{Null-Neutralizer Node}\label{subsec:null-neutralizer_node}
This device creates a synchronized counter-field within a null field (above). In effect, it creates a ``hole'' in the null -- a circle where psi works normally -- by countering it with precisely matched anti-psionic signals. Use the stats for null-field generators, but double cost and halve the radius affected; e.g., a pocket null-neutralizer costs \$4,000 and has a one-yard radius.

\textit{Note:} These have \textit{no effect} on the power dampers mentioned on p. \pageref{subsec:power_damper}.

\subsection{Overload-Field Generator}\label{subsec:overload-field_generator}
This system generates an anti-psi interference field pulsing at a frequency that makes psi abilities in the area of effect fluctuate uncontrollably. The field is invisible and can pass through solid objects. All psi abilities within it behave exactly as if they had the Uncontrollable limitation (p. B116), triggering spontaneously in stressful situations. (\textit{Exception:} The diagnostic overload projector is more powerful; see below.) Any ability that's already Uncontrollable goes out of control at once and stays that way while the psi remains in the field. These effects end immediately upon leaving the field.

\textit{Pocket Overload Field:}\label{itm:pocket_overload_field} While this cigarette pack-sized device can be worn on a belt, it's small enough to be deployed covertly; e.g., hidden in a psi's desk or (with a Pickpocket roll) slipped into his pocket without him noticing. It may be activated by a timer or remotely via a receiver. It affects a two-yard radius. \$2,000, 0.4 lb., 4B/1 month. LC2.

\textit{Portable Overload Field:}\label{itm:portable_overload_field} This suitcase-sized generator projects a field over a 10-yard radius (or a smaller radius, if desired). \$50,000, 10 lb., 2C/1 month. LC2.

\textit{Semi-Portable Overload Field:}\label{itm:semi-portable_overload_field} This generator fits in a truck bed and projects a field over a 20-yard radius (or a smaller radius, if desired). \$200,000, 250 lb., E/1 month. LC2.

\textit{Overload-Field Tower:}\label{itm:overload-field_tower} This large generator, mounted in a 30'-tall tower, emits a field that covers a 100-yard radius. \$5,000,000, 1,000 lb., external power. LC1.

\textit{Diagnostic Overload Projector:}\label{itm:diagnostic_overload_projector} This unit generates a two-yard-long overload-field ray. It affects any psi in its path, but only if it irradiates the psi's head for at least 10 full seconds, and only while he remains in the beam. However, the field is more powerful than the others described here: the subject must make a Will roll every 10 seconds, with failure indicating that his powers aren't merely Uncontrollable but start to manifest regardless of stress. If he's subject to other emotional stress at the same time, the GM may impose a Will penalty; e.g., -3 for a captive who fears for his life if he doesn't escape. The diagnostic overload projector is often installed in a clinical setting, such as over an examination table or next to a prisoner strapped to a rack. Its usual purpose is to reveal psi ability (the ray is focused on the subject in the hope that he'll be forced to reveal his powers), but it can be used more subtly (e.g., disguised as a sun lamp, hair dryer, etc., perhaps as a trap to expose a secretive psi's abilities).\$200,000, 40 lb., external power. LC2.

\textit{Overload Grenade:}\label{itm:overload_grenade} This is a rugged, baseball-sized overload-field generator designed to be thrown like a grenade. It doesn't explode, but its integral power supply burns out after use. It creates an overload field that blankets a five-yard radius for one minute. It can't be turned off once activated, although the grenade can be destroyed (SM -8, DR 10, HP 4). Some versions also release tear gas or emit a loud siren howl to trigger stress! \$500, 1 lb. LC2.

\subsection{Psi-Impeder}\label{subsec:psi-impeder}
While this headgear is worn and undamaged, it projects a continuous psi-damping field that completely prevents the wearer from using any psionic abilities.

\textit{Psi-Impeder Band:} This simple electrode headband can be buckled tightly onto a psi's head. As it's fairly easy to remove, it's most useful if the subject is also physically restrained. One way to deal with a psi-impeder band if one's hands are restrained is to bang it against a solid object repeatedly -- it has only DR 2, HP 2. However, any damage affects the skull as well . . . the impeder's DR doesn't protect the wearer (although he gets his usual skull DR, normally DR 2). \$1,000, 0.25 lb., A/1 month. LC3.

\textit{Psi-Impeder Helmet:} This is a psi-impeder integrated into an open, armored skullcap that can be strapped and locked onto the subject's head, preventing easy damage or removal. The helmet protects its circuitry (and the user's skull!) with DR 8. \$1,250, 3 lb., 4A/1 month. LC3.

\subsubsection{Dedicated Psi-Impeder}\label{subsubsec:dedicated_psi-impeder}
Impeders may be available that block only one specific power (e.g., Telepathy). Cost is halved; other stats are unchanged.

\subsection{Psycho-Optic Filter}\label{subsec:psycho-optic_filter}
Through a combination of special lenses and electronic stimulation of the optic nerve, this technology modifies the user's incoming visual perceptions to filter out anomalous psionic sensory impressions. This enables him to see through any psionic illusion, obscuration, or invisibility that affects normal vision. 

The filter has a drawback, though: While it's on, the optic stimuli it uses subliminally leak into the user's normal perceptions, resulting in the periodic sensation that ``someone is watching'' out of the corner of his eye. This distorts his visual situational awareness (-2 to Perception rolls), prevents him from using the Danger Sense advantage (psionic or otherwise), and is mentally stressful (he can't regain lost FP). Switching the filter on or off takes a second.

Like many psychotronic devices, a psycho-optic filter only works if a living person is ``in the loop.'' It's useless to robots or automatic cameras, unless controlled by a psionic computer (p. TODO).

\textit{Psycho-Optic Filter Goggles:}\label{itm:psycho-optic_filter_goggles} These resemble bulky night-vision goggles with attached electrodes. The wearer suffers from No Peripheral Vision (p. B151) -- that is, his vision is limited to a 120\degree arc. \$10,000, 2 lb., 4B/1 month. LC3.

\textit{Psycho-Optic Filter Mode:}\label{itm:psycho-optic_filter_mode} A psycho-optic filter can be integrated into standard helmet-mounted passive visual goggles or any head-up display (suit, vehicle, etc.). This adds \$10,000 to cost and 1 lb. to weight. LC3.

\subsection{Psychotronic Para-Stealth}\label{itm:psychotronic_para-stealth}
Psionic research has identified the ways that certain shapes (such as pyramids) focus psi ability, while more-esoteric diagrams, glyphs, shapes, and materials can disrupt it. Psychotronic para-stealth is a passive surface configuration that exploits this interference to afford buildings, vehicles, robots, and body armor partial invisibility to psi. Any attempt to use a psionic sense (such as Clairvoyance, Danger Sense, or Telescan) to notice or detect an object that has such an exterior always requires a skill roll, at a penalty that depends on the para-stealth system's quality.

A minimal or basic para-stealth surface isn't especially remarkable to normal eyes -- perhaps a specialized paint job or an odd texture. Improved, radical, or total para-stealth inevitably means a weird appearance, though: bizarre angles, unusual colors, geometries that seem to be almost non-Euclidian, and/or strange patterns embossed on the object's exterior. Para-stealth systems can't be disguised or hidden ``below the skin'' without disrupting their special qualities. A Vision roll can notice something unusual about them. Psis who succeed at noticing items protected by para-stealth often describe them as blurred, ``wrong,'' or headache-inducing.

The following table lists the various grades of para-stealth. ``Psi'' applies to all rolls for psionic senses. ``Vision'' applies to \textit{normal} Vision rolls to notice something odd!

\begin{table}[H]
    \centering
    % \small
    \rowcolors{1}{}{\colormedical}
    \begin{tabularx}{\columnwidth}{lXcXcrc}
         \textbf{Para-Stealth} && \textbf{Psi} && \textbf{Vision} & \textbf{Cost*} & \textbf{LC} \\
         % para & psi_penalty & vision_mod & \$ & lc \\
         Minimal && -2 && -8 & \$1,000 & 4 \\
         Basic && -4 && -4 & \$4,000 & 4 \\
         Improved && -6 && 0 & \$20,000 & 3 \\
         Radical && -8 && +4 & \$100,000 & 3 \\
         Total && -10 && +8 & \$500,000 & 2 \\
    \end{tabularx}
    % \caption{Caption}
    \label{tab:para-stealth}
\end{table}

* Adjust for SM (\pageref{tab:adjust_for_sm}).

\section{Astral Technology}
Astral psychotronics are related to the Astral Projection power (\textbf{GURPS PSionic Powers} pp. 26-30). Psi-amplifiers and psychotronic generators for that power are also available.

\subsection{Astral Barrier-Field Generator}\label{subsec:astral_barrier-field_generator}
This machine generates an astral zone around itself that's impervious to outer-plane astral travel. The barrier is invisible except to the Astral Sight ability or to someone on the outer astral plane, where it manifests as a mirror-surfaced bubble that -- if gazed upon for too long -- begins to reflect frightening imagery drawn from the observer's subconscious. Staring at it can lead to hallucinations and insanity! Roll a Fright Check for every half hour spent contemplating the barrier, at a cumulative -1 per continuous hour.

The only way to pass an astral barrier is to face one's fear and discover a ``back door'' through it via the inner astral plane, which involves Astral Crossing (\textbf{GURPS Psionic Powers}, p. 29). This often requires a lengthy trip through a psychological maze, and a confrontation with inner demons or subconscious fears. Successfully navigating this gantlet brings the traveler to the other side of the barrier, but typically takes an hour or more of subjective time.

The generator is semi-portable device that can cover up to a 50-yard radius. \$500,000, 100 lb., 4C/2 weeks (or external power). LC3.

\subsection{Astral Duplicator}\label{subsec:astral_duplicator}
This device somewhat resembles a bizarre hybrid of photocopier and X-ray machine. It's designed to translate articles of equipment -- and even people -- into the astral plane by creating synthetic astral bodies for them.

In operation, an object placed on the duplicator's plate is irradiated with psionic energy. A flickering aura manifests around the item, gradually intensifying over several minutes as its artificial astral form is created. The article's astral copy appears in the outer astral plane, coincident with its location on the machine. It now exists on both planes; e.g., an astrally projecting psi could pick up an astral copy of a piece of gear and use it normally in the astral plane.

Forming an object's astral copy is a tricky procedure that requires 10 minutes and an Electronics Operation (Psychotronics) roll per attempt. Once duplication is successful, the copy can remain in the astral plane\ldots but only while the original remains untouched on the duplicator's translation plate. A ``silver cord'' connects the duplicate to its material form. Removing the original item from the plate or even touching it, or turning off the machine, dissolves the astral body. 

Living things can be placed on the plate and ``copied,'' too -- the device simply creates their astral projection for them. Their Move on the astral plane is IQ/2. However, such an astral body is dependent on the machine, as explained above for objects. This isn't a safe process! The duplicator's radiation drains 1d-2 FP (minimum 1 FP) per copying attempt, successful or not, and for every 10 minutes spent in astral form. In addition, when the synthetic astral body is dissolved, the sudden shock requires a HT-2 roll, with failure meaning unconsciousness for minutes equal to the margin, and failure by 5+ or critical failure resulting in a coma (p. B429).

This is a large, bulky device: \$2,000,000 and 400 lb. per pound of object (minimum 0.5 lb.) it can sustain in astral form. External power. LC3.

\subsection{Kirlian Sensor Field}\label{subsec:kirlian_sensor_field}
This is a psychotronic security system intended to detect astral intruders. Its low-powered electrostatic field causes any astral body moving through it (in the outer astral plane) to fluoresce visibly, appearing as a silhouette surrounded by a colorful flickering aura. To psis using Astral Sight, the field itself is visible as a sparkling mist: -1 to skill rolls to see through it.

The sensor field is generated by a pair of opposed plates that must be within three yards of each other. In buildings, these are often hidden in or otherwise attached to the floor and ceiling, or parallel walls. Once the system renders an astral body visible, other security devices installed can detect and react to it as they would any sighting; e.g., standard cameras can register the intruder.

A side effect of the field is that a person traversing it in the material world (rather than in the astral plane) may experience a slight buildup of static electricity. His hair might stand on end, or he may create a small sparks when he touches objects or people. The field might also disrupt sensitive electronics -- particularly computers -- unless they've been hardened.

A Kirlian sensor field installation in a building or a vehicle is \$180 and 9 lb. per square yard of ground coverage; e.g., a system protecting a corridor 10 yards long and 2 yards wide would cost \$180 × 10 × 2 = \$3,600 and weigh 9 lb. × 10 × 2 = 180 lb. The control console -- wired into the building or vehicle's electronics, and used to switch the field on or off -- is \$2,500, 20 lb. External power. LC4.

\subsection{OOBE Machine}\label{subsec:oobe_machine}
An out-of-body excursion (OOBE) machine psychotronically stimulates certain areas of the brain to induce astral travel. It typically consists of a bedlike platform to which the subject is strapped, plus attached electrodes (or a psiberface unit) and control modules. Once the user is connected to the device, the induction process takes 20 minutes as he's gradually reduced to unconsciousness and then awakens on the astral plane.

The user must either rely on an operator or set the duration of the ``trip'' beforehand; he has no control over the apparatus from the astral plane. Manual operation is safest, as the technician can monitor the subject's status, but the device \textit{can} be preprogrammed to let someone use it unassisted. Either way, make an Electronics Operation (Psychotronics) roll. Multiple travelers can be connected to the same machine; if so, roll separately for each, applying -1 per person past the first to \textit{all} rolls.

Success means the process works smoothly. The subject falls asleep partway through the process and then awakens in the outer astral plane, his astral body emerging from his sleeping form. All rules under \textit{The Astral Plane} (\textbf{GURPS Psionic Powers}, p. 27) apply. The visitor's Move is IQ/2. If he possesses Astral Projection abilities (other than Astral Travel) of his own -- e.g., Astral Sword -- then he can use these normally.

Failure means the subject doesn't form a proper astral body. He may have \textit{some} kind of ``out-of-body experience'' (e.g., feel as if he's floating, and then look down and see himself). However, the entire incident is completely subjective, and he has no control over his movement. In effect, he's sleeping -- and possibly dreaming an uncontrolled OOBE -- until the machine is switched off or a programmed trip ends.

Critical failure is more bizarre: The subject is inadvertently projected into the strange inner astral plane (\textbf{GURPS Psionic Powers}, p. 28). He's trapped there for the duration, unable to return -- and possibly experiencing the odd events and psychological terrors and revelations that are common in that realm. An OOBE machine can keep the subject in the astral plane for as long as it's powered up. There is some physiological stress, though: The user loses 1 FP per hour spent in the machine.

When a traveler's time is up -- or if the operator recalls him -- he's drawn back to his body by ``reeling in'' his silver cord. However, if the machine is turned off suddenly (or destroyed!) \textit{before} the subject can return, he experiences a traumatic shock to his system. He must roll vs. HT-4 to avoid suffering a seizure (p. B429) for seconds equal to margin of failure. Critical failure means a heart attack (p. B429) instead.

Complete system: \$400,000, 200 lb., external power. LC3.

% \section{Dream Technology}
% Dream~-tech is related to the Dream Control power, a sub~-power of Telepathy. Psi-amps and psychotronic generators related to it are available as well.

% \subsection{Dreamcorder}\label{subsec:dreamcorder}
% A dreamcorder module is attached to a dreamscanner (p. \pageref{subsec:dreamscanner}) or a dreamscaper (p. \pageref{subsec:dreamscaper}) to record the subject's dream experiences. Playing back the recording involves sleeping attached to a dreamscanner or dra

% \subsection{Dreamscanner}\label{subsec:dreamscanner}

% \subsection{Dreamscaper}\label{subsec:dreamscaper}

\section{Ergokinetic and Information Technology}
Ergokinetic psychotronics are related to the Ergokinesis power (\textbf{GURPS Psionic Powers}, pp. 30-37).

\subsection{P-Web Shield}\label{subsec:p-web_shield}
A very simple device, the P-web is a fine mesh of platinum-group metal alloy. Worn on the head -- built into a hat or a helmet to protect the webbing -- it grants total immunity to the Confuse ability of Ergokinesis. It also prevents the wearer from using Ergokinetic abilities (but affects no other type of psi). Add to any head: +\$1,200, +0.5 lb. LC4.

% \subsection{Psionic Computers}\label{subsec:psionic_computers}
% Recently, 

\section{Extrasensory Perception Technology}\label{sec:extrasensory_perception_technology}
These psychotronics are related to the ESP power (\textbf{GURPS Psionic Powers}, pp. 37-43).

\subsection{Deathscanner}\label{subsec:deathscanner}
A deathscanner is a form of trauma~-enhanced Retrocognition. It consists of two psiberface units (p. \pageref{sec:psi-interface_technology}) connected through a psychotronic scanning module. The The operator plugs into one psiberface; the other is for a \textit{corpse}. The scanner enables the user to examine the dead person's memories in the hour ro so prior to death! It picks up both physical sensory impressions and what the subject was actually thinking.

The device can only ``read'' a relatively fresh corpse - the subject must have died within the past 72 hours. As well, the brain must be more-or-less intact. Scanning is \textit{impossible} if the brain suffers total destruction (-10×HP), the victim was exposed to 5,000+ rads, or death resulted from a failed HT roll brought about by eye or skull injury.

Each attempt to reach the subject and sort through his memories requires 10 minutes and a roll against Electronics Operation (Psychotronics). The operator is at -1 per hour that the corpse has been dead. Success gives a general impression of the circumstances surrounding the person's death: what was going on in the last few minutes, what the victim saw and heard, etc. Further attempts may be made to learn more details.

Failure by 1-4 means the user picks up only a confusing mishmash of pain and fear, perhaps a constant repetition of frightening images from the last few seconds before death. This \textit{might} be useful if the cause of death is totally unknown, but it provides no clear information. Repeated attempts after a failure suffer a cumulative -1 to skill.

Failure by 5+ or critical failure means the user has been trapped in the dark whirlpool of the victim's death experience! Make a Fright Check at -5, with all usual effects. Any further attempts by that operator to probe the corpse are at -2.

\textit{Portable Deathscanner:}\label{itm:portable_deathscanner} This is a semi-portable scan-
ning helmet and terminal, capable of fitting in the trunk of a
car. It provides no skill bonus. \$200,000, 40 lb., M/6 hrs. or
4×C/1 day. LC3.

\textit{Laboratory Deathscanner:}\label{itm:laboratory_deathscanner} This is a large scanning device, similar in size to a hospital MRI system. It provides +2 to skill when using the deathscanner. Instead of or as well as displaying images via psiberface, it can translate them into digital media and project them as a movie. \$1,000,000, 1,000 lb., external power. LC3.

\textit{Event Recorder:}\label{itm:event_recorder_deathscanner} This addition to the deathscanner allows the creation of a sensie (p. \pageref{sec:sensies}) from the subject's dying memories. This only works if the brain has been dead for less than a day. The unit records backward from the moment of death until the scan quality deteriorates beyond recovery; total length rarely exceeds a few minutes. The recording could be used evidence at a trial, or even serve as a form of entertainment with the depraved! Added to deathscanner: +\$3,000. LC3.

\subsection{Psychometer}\label{subsec:psychometer}
This is a handheld sensor the size of a paperback book. It allows an Electronics Operation (Psychotronics) roll to detect the active use of psionic powers. It cannot determine whether someone is a psi unless he's currently using psi abilities.

A psychometer can be set to sweep a 60\degree{} arc at 1,000 yards or to perform a 360\degree{} degree scan at 200 yards. Each use requires 10 seconds of scanning to gather data. A failed skill roll means the user didn't focus the gadget properly -- it detects nothing, and repeated attempts suffer a cumulative -2 to skill until the operator takes 30 minutes to recalibrate the device.

When used to detect the general use of psi abilities, there's no special skill modifier. Success means the user detects all such psi phenomena within range. If set to search for a specific power (e.g., Telepathy and Telepathy-related psychotronics), the skill roll is at -2. After achieving a general fix, the operator can try to learn more specific information -- the kind of psi ability being used, approximately how powerful it is, etc. -- at 10\% of range. This requires 10 seconds of additional scanning and another skill roll, this one at -2. If there are multiple psi sources, the user can only focus on one of them at a time.

Sleek, high-tech unit: \$10,000, 2 lb., 4B/1 day. LC4.

For a larger~-scale, psi~-detector, see \textit{Psi Scanner} (p. \pageref{subsec:psiscanner}). These can be upgraded to incorporate the psychometer tech, add either +\$10,000 \textit{or} +0.5 CF, whichever is more. 

\section{Psychic Healing, Vampiric, and Biokinetic Devices}\label{sec:psychic_healing_vampiric_biokinetic_devices}
These psychotronic devices detect, emulate, and manipulate life~-energy auras and bio~-energy fields. They're related \textit{several} powers: Psychic Healing (\textbf{GURPS Psionic Powers}, pp. 46-49), Psychic Vampirism (\textbf{Psionic Powers}, pp. 49-52), and Biokinesis (\textbf{Psionic Powers}, pp. 72-73).

\subsection{Life-Transference Machine}\label{subsec:life-transference_machine}
This bed-sized psychotronic device transfers bio-energy between two living people, draining one to heal or invigorate the other. Both individuals must be strapped down on the platform and connected to the machine via a psiberface system. Make an Electronics Operation (Psychotronics) roll to set things up properly; each attempt takes one minute. Critical failure may mean that donor and recipient are reversed -- or that both parties are drained!

Once the machine is set up, it sucks life force from the donor at the rate of 1d+1 HP per minute. For every full 2 HP drained, 1 HP is transferred to the recipient, provided that he isn't already at maximum HP. At full HP, each HP transferred to him restores 1 FP instead. If he's at full HP and FP, he gains no benefit.

The draining process isn't painful but the donor will feel steadily weaker and sicker, exhibiting signs of shock: clammy skin, weak and rapid pulse, lethargy, and so on. No obvious external injuries appear as he loses HP, but the victim gradually suffers cellular damage and internal hemorrhage (which may be visible as bleeding from the nose, etc.). The machine's effect on an injured or ill recipient is far more dramatic: preternaturally accelerated healing.

A life-transference machine can't affect nonliving entities (such as machines) or the dead, with one exception: It can transfer life force to someone who has recently died of injuries (HP loss), provided that he has been dead for less than three minutes and isn't at or below -5×HP. If the machine raises his HP above -HP, then make a HT roll for him. Success means he comes back to life!

Complete system: \$2,000,000, 200 lb., external power. LC2.

\subsection{Psychospectral Imaging System}\label{subsec:psychospectral_imaging_system}
A psychospectral imaging system is an electronic camera capable of detecting the psionic auras surrounding living things, superimposing them over the observer's visual field. Resolution is lower than that of the Aura Reading psi ability, so diagnosis isn't possible (although obviously, someone who's dead won't possess an aura!). However, living things -- plants, animals, people, and other life forms larger than microorganisms -- are visible even in total darkness, through smoke and fog, and regardless of electronic countermeasures.

The system can't detect nonliving targets, see through solid objects (living or not), or sense life completely enclosed in non-living material (e.g., a car's occupants). However, a personal aura extends a short distance from the body -- about 0.25'' for a human -- so it's possible to detect that of someone clad in ordinary clothing or wearing body armor less bulky than a heavy battlesuit. Only a suit with an SM greater than its wearer's will mask his aura.

\textit{Psychospectral Goggles or Visor:}\label{itm:psychospectral_goggles_visor} Wearable, hands-free aura-imaging optics with a wide field of view. These can be added to a suit helmet as an integral feature or bought as separate strap-on goggles. Either limits the user's vision to a 120\degree{}
arc; he suffers from No Peripheral Vision (p. B151). \$2,000, 0.8 lb., B/1 day. LC4.

\textit{Psychospectral Camera:}\label{itm:psychospectral_camera} Aura-imaging electronic video camera for surveillance or recording. No display is included; operation requires a separate terminal, such as a computer system. It limits the user's vision to a 60\degree{} arc (treat as Tunnel Vision, p. B151) but incorporates a 4× zoom lens (Telescopic Vision 2). It's often installed in a rotating mount, tripod, etc., and may be mounted on a vehicle. It can also function as a standard digital camera. \$2,000, 2 lb., 4B/1 day. LC4.

\subsection{Thanatos-Field Generator}\label{subsec:thanatos-field_generator}
Also called a \textit{vampire field} or a \textit{death field}, a Thanatos field kills by  psionic means, draining the life force from living things. As it harms people without damaging electronics or machinery, it's a very useful -- if somewhat slow-acting -- weapon system. It has no effect on life forms with IQ 0: bacteria, plants, etc.

A Thanatos field is unaffected by solid objects, armor, or force fields. Anyone caught in it must make a Will-4 roll each second, with failure reducing HT by one \textit{and} costing 1 FP. Sufficient FP drain leads to HP loss (p. B426)\dots which the HT reduction makes deadly! Victims cannot heal FP or HP naturally while inside the field. Outside it, they recover normally, and HT returns at the rate of one point every 10 minutes. While the field is invisible, people within it experience a sense of fatigue and malaise -- although they usually blame this on general tiredness.

The field generator is a heavy, backpack-sized device. It has a spherical area of effect, the radius of which can be set anywhere between 10 and 100 yards (its maximum); changing the radius takes two seconds. \$200,000, 40 lb., 4C/1 day. LC1.

\subsubsection{Selective Thanatos-Field Generator}\label{subsubsec:selective_thanatos-field_generator}
This variant design gives the operator the option to tune the field to affect only nonsapient (IQ 1-5) or sapient (IQ 6+) victims. It can also be adjusted to affect only psis or non~-psis. \textit{Double} the price of a regular, non-selective field generator. LC2.

\subsubsection{Exterminator Field Generator}\label{subsubsec:exterminator_field_generator}
This field generator has safety interlocks that limit it to function only vs. \textit{nonsapient} (IQ 1-5) life forms. Roll against Electronics Repair (Psychotronics) at -4 to remove this limitation, turning it into a regular, non~-selective field. Any failure destroys the device. LC3.

\section{Psychokinetic Technology}\label{sec:psychokinetic_technology}
Psychokinetic devices work on similar principles to the Psychokinesis (PK) power (\textbf{GURPS Psionic Powers}, pp. 53-57).

\subsection{PK-Sensitive Materials}
Certain exotic compounds are unusually responsive to PK and to Telekinesis (TK) in particular, the most popular of which are extracted from the hide of telekinetic reptiles known as Telocs. These ``telekinesis-sensitive'' (TKS) molecules have several applications. Mo

\subsubsection{Kinetic Bubble}\label{subsubsec:kinetic_bubble}
This is a spherical container made of plastic that's impregnated with TKS molecules. Materials and shape combine to resonate with and amplify TK, making the bubble and its contents easier to lift telekinetically. Treat the container and anything placed within it as having 1/10 of their normal mass for the sole purpose of determining how much a psi can lift with the TK Grab ability (or optional Telekinetic Control ability). Actual weight and mass are unchanged.

A typical kinetic bubble is SM 0 and capable of holding up to 1 cubic yard: \$20,000, 0.25 lb. Larger bubbles are available; apply Adjusting for SM (p. \pageref{tab:adjust_for_sm}) to cost and weight. LC4.

\subsubsection{TKS Structure}\label{subsubsec:tks_structure}
Almost any structure can be made from a metal, concrete, or plastic composite that is impregnated with TKS molecules. Divide its effective mass by 10 for the sole purpose of lifting or moving it with TK. Cost is \$100 per pound of object weight. LC4.

\begin{ravenbox}
    \subsection{Telocs}
    Telocs, sometimes also called Tele-crocs, are a species of Raven which appear almost identically to crocodiles. The difference, though, is that telocs have telekinetic (and generally psychokinetic) abilities. They live in the asteroid belt known as the Bayuk Belt, a bizarre place most simply described as a space-baiyou. Three-dimensional teloc-infested waters weave between the swampy asteroids and a sickly humid atmosphere cloaks the entire belt.

    They use their telekinesis to horrifically twist their prey. They are hunted not only for the TKS molecules found in their hide, but also for their brains for use as psiborgs and for the extracts use in various psi-drugs.
\end{ravenbox}

\subsection{Psiberweave}\label{subsec:psiberweave}
Psiberweave is the generic name for any synthetic fabric impregnated with psi~-interactive biomolecules that are sensitive to psychokinetic impulses. Anyone who has the TK Grab (or Telekinetic Control) ability can ``tweak'' the molecules of his psiberweave garment to make instant changes to color and texture, up to and including turning it transparent. Within limits, he can even adjust cut. Texture changes and complex patterns require a skill roll; failure means unintended results that require repeated attempts to fix, at the usual penalties. Finally, treat the article as having 1/10 of its actual weight for the sole purpose of lifting or moving it with TK.

Any clothing or flexible body armor can be psiberweave at 4× its usual cost.

\section{Telepathic Technology}
Telepathic psychotronics are related to the Telepathy power (\textbf{GURPS Psionic Powers}, pp. 57-67).

\subsection{Empathic Mirror}\label{subsec:empathic_mirror}
This headgear amplifies all physical sensations felt by the wearer and broadcasts them around him. While an empathic mirror has its peacetime uses (primarily in the bedroom; used appropriately, it can grant +2 to Erotic Art), it's intended mainly as a \textit{defensive} weapon: Everyone within a five-yard radius of the user suffers the same shock, stun, and knockdown effects as he does, as well as any irritating or incapacitating conditions that afflict him! People affected by the device make their own recovery rolls, using their scores (most often HT or Will) rather than the wearer's. For example, if the user takes 4 HP of injury from a bullet, everybody within five yards is at -4 due to his pain -- and if he's physically stunned, everyone within that radius is stunned and must make HT rolls to recover.

An empathic mirror affects friend and foe alike. Thus, it's most practical in combat where the wearer faces several nearby opponents alone. Any form of the Mind Shield advantage (e.g., the Psionic Shield ability or equivalent psychotronic device) blocks its effects completely -- as does another empathic mirror. 

Available as a lightweight headband or built into a helmet (add cost and weight to that of the armor): \$20,000, 1 lb., 6B/1 day. LC3.

\subsection{Memory Crystal}\label{subsec:memory_crystal}
This is a cubic crystal within which a psi with the Telesend ability can permanently imprint a single mental image, along with all associated emotional resonances. If the memory is particularly strong and violent, those who touch the crystal must resist the psi's Telesend skill or be mentally stunned. 

A typical memory crystal costs \$2,000 and has negligible weight. It is possible, but uncommon, for larger objects to be built from memory crystal: the cost will vary wildly but are generally \$10,000 per lb.. Regardless of size, there is no power requirement. LC4

\subsection{Mental Translator}\label{subsec:mental_translator}
This device beams telepathic signals directly into another
person's brain. In effect, this is mechanical telepathy. A mental translator requires a psiberface unit to function, and the user can only transmit. No special hardware is needed on the receiving end, however. Any sentient (IQ 1+) living brain, including that of a total cyborg, can receive the transmissions; entities with IQ 0 (like most plants and microbes), and purely digital intelligences, cannot.

The signal is directional, much like that of a laser communicator, but not blocked by material objects. It must be focused on a particular target in line of sight, or at a known location within range. Transmissions can propagate beyond the listed ``effective'' range, but these are more difficult to pick up. To extend range, the operator may roll against Electronics Operation (Communications or Psychotronics), at -1 per +10\% to range, to a maximum extension of +100\%.

Humans and similar races perceive mental-translator signals as ``voices in the head,'' at the volume of a loud whisper. Other species perceive them as analogs to their primary communication sense (sound, smell, or whatever). Regardless, the message is ``universal'' and transcends language -- any IQ 1+ being can understand it, although nonsapient ones (IQ 1-5) are limited to simple concepts.

\textit{Tiny:}\label{itm:tiny_mental_translator} 20-yard range. \$20,000, 0.06 lb., 4A/8 hrs. LC4.

\textit{Small:}\label{itm:small_mental_translator} 200-yard range. \$100,000, 0.6 lb., 4B/1 day. LC4.

\textit{Medium:}\label{itm:medium_mental_translator} 1-mile range. \$400,000, 6 lb., M/6 hrs. or 4¥C/1 day. LC3.

\textit{Large:}\label{itm:large_mental_translator} 10-mile range. \$2,000,000, 60 lb., 4D/1 day (or external power). LC3.

\subsection{Mind-Transfer Machine}\label{subsec:mind-transfer_machine}
This psychotronic device enables two people to switch minds. The new inhabitant of each body has all of his old memories and none of the former occupant's; for guidelines, see \textit{Mind Transfer} (p. B296). The individuals involved need not be members of the same species, but both must have IQ 2+.

The machine's operator must roll against Electronics Operation (Psychotronics) for the transfer. Neither party can resist! Success means the process takes five minutes; this includes time to adjust to the new body and become functional. Critical success permits rapid adjustment, halving this time; failure indicates disorientation, doubling it. Critical failure burns out the machine and causes exotic effects (e.g., both minds in both bodies, resulting in two cases of Split Personality)\ldots or simply brain damage, ranging from Epilepsy or Neurological Disorder to both minds being reduced to IQ 1 vegetables (best inflicted upon NPCs). All effects are permanent, and while the machine can restore a mind to its former body, critical failure results may be irreversible.

A mind-transfer machine is \$100,000,000, 200 lb., external power. LC1.

\subsection{Mindscanner}\label{subsec:mindscanner}
The mindscanner is a passive psychic detector -- typically an early development in settings with telepathic psychotronics. It detects thoughts but isn't sensitive enough to interpret them. Its screen simply reads out the location of all sapient (IQ 6+) beings in range who are currently thinking about something; anyone who stops thinking vanishes from the display. The device cannot identify individuals. However, it works through walls and other solid cover, making it useful despite its limitations.

Roll against Electronics Operation (Psychotronics) locate anyone within range who are currently thinking. It comes with a built~-in screen, but can be connected to any terminal (p. \pageref{subsec:terminals}) to display signals on a map.

The greater the number of thinking people in the area, the harder it is to keep track of their locations. All skill rolls are at -1 for 10-19 people in range, -2 for 20-39, and so on. Each doubling gives another -1.

A mindscanner won't detect sleeping beings unless they're dreaming. It cannot sense nonsapient (animal) thoughts or raw emotions, either. And individuals protected by any form of Mind Shield (e.g., the Psionic Shield ability), or within a null field or an area of Psi Static, are completely invisible to it.

A conscious person who lacks shielding can only hide from a mindscanner if he avoids thinking. He must roll against Mind Block (p. B210), at an extra -2 because Mind Block normally involves conscious efforts to ``jam'' thoughts through such ploys as doing math in your head -- not trying not to think! Moreover, he can't use mental (IQ-, Will-, or Per-based) skills besides Mind Block. He can only perform physical actions or skills that can be done instantly and with planning. In particular, a fighter can attack, defend, and move, as his training will have taught him to do these things almost reflexively, but he can't take Aim, Evaluate, or Feint maneuvers, which always require a certain degree of planning.

\textit{Handheld Mindscanner:}\label{itm:handheld_mindscanner} 30-yard range, \$6,000, 1 lb., 4B/1 day. LC3.

\textit{Large Mindscanner:}\label{itm:large_mindscanner} Usually vehicle~- or tripod~-mounted. 150-yard range. \$300,000, 25 lb., 2C/1 day. LC3.

\subsection{Mindseeker}\label{subsec:mindseeker}
A mindseeker can replace the normal guidance of any homing missile or torpedo, enabling it to lock onto sapient (IQ 6+) minds within 500 yards in a 60° cone in front of it. Unless the weapon has other systems (e.g., inertial guidance) that allow it to follow a preprogrammed route, it will move directly forward until a sapient mind comes into range, at which point the seeker will steer it toward that target. If the sensor detects several such minds before it strikes, it will home in on the nearest. Use the rules under \textit{Homing Weapons} (p. B413). The weapon has a penalty to hit targets with Mind Shield (e.g., the Psionic Shield ability) equal to their level of that trait.

Mindseekers can be species-specific; a mindseeker programmed to hunt one species won't be useful against another. A mindseeker can even be programmed to go after one particular individual. This necessitates transmitting the target's psychic signature to the seeker's memory; a psi who has previously encountered that person's mind can do so using Telesend. A weapon with such guidance will move until it finds its prey -- it won't home in on other targets -- and if it runs out of fuel or crashes first, its warhead won't detonate.

A psi who notices a mindseeker missile or torpedo may try to divert it telepathically -- assuming he has time before it hits! This involves using Telesend to transmit bogus signals to its ``brain.'' Roll against Telesend at -5. Success means the weapon turns aside and crashes harmlessly. Critical success lets the psi give it an alternative target signature, if he wishes.

Mindseeker-equipped weapons cost five times as much as ordinary homing missiles or torpedoes. Other stats are unchanged.

\subsection{Psionic Mind Shield}
See \textit{Psionic Mind Shield}, p. \pageref{subsec:psionic_mind_shield}.

\subsection{Telepathic Switches}\label{subsec:telepathic_switches}
Telepathic switches (or \textit{teleswitches}) are psi-sensitive circuits that respond to mental control via Telepath ability.

\subsubsection{Basic Telswitch}\label{subsubsec:basic_teleswitch}
The simplest teleswitches allow telepaths to turn on but not \textit{control} electronic devices, from TVs to computers. They most often replace manual on/off switches in systems such as lights, vehicle ignitions, and electronic doors. More interesting uses include activating and deactivating detonators and timers for explosives; turning homing beacons on and off; and activating and deactivating security systems. \$200, negligible weight. LC4

\subsubsection{Secure Teleswitch}\label{subsubsec:secure_teleswitch}
A teleswitch can be sensitized to a single set of mental signatures -- only those minds can operate it. Such are switches useful as electronic locks on doors and safes, and for limiting access to computers and the like. \$1,000, negligible weight. LC4.

\subsubsection{Telepathic Control Panel}\label{subsubsec:telepathic_control_panel}
This is an array of exceptionally sensitive, miniaturized telepathic switches built into a single device; e.g., a computer keyboard where each teleswitch corresponds to a single key. The increased sensitivity enables the psi to control several switches per second. A telepathic control panel fitted to a computer, calculator, sensor, gunnery console, etc. lets a psi use his mind to operate the device at a distance, visualizing each key or button and so activating the switch. While doing so, he uses his normal skill for operating the device or the average of that skill and his Telesend skill, whichever is \textit{lower}. One Telesend skill roll per minute is required to maintain mental communication with the controls. Added to a normal control panel: +\$10,000, or +\$50,000 if secure. LC4.

\subsection{Thought Globe}\label{subsec:thought_globe}
A sphere a few inches in diameter, the thought globe is highly sensitive to psychic impressions. Anyone -- psionic or not -- who touches it and concentrates on a specific image will cause the globe to show that thought-image as a picture or a hologram inside it. This is not a mental projection, but a physical display that can be photographed. \$5,000, 0.5 lb, 4A/8 hr. LC4.

\section{Teleportation Technology}\label{sec:teleportation_technology}
These devices are related to the Teleportation power (\textbf{GURPS Psionic Powers}, pp. 66-71).

\subsection{Actuality Shield}\label{subsec:actuality_shield}
An actuality shield is an exotic matter built into an object's surface making it easier to transport with Teleportation. Treat the shielded item as having only 10\% of its actual weight when determining how much weight can be teleported. This applies when calculating encumbrance limits for the Autoteleport and Combat Teleport abilities, and when figuring out whether Exoteleport can affect the thing. 

This shielding has a drawback: objects ``protected'' by actuality shields are \textit{more} vulnerable to attack by Innerportation, as more mass can be teleported away! This ability inflicts \textit{double} (that is, 2d-4 impaling damage per level) on shielded items.

An actuality shield for any object costs \$10,000 per pound of weight. LC3.

\subsection{Jump Beacon}\label{subsec:jump_beacon}
A jump beacon physically stresses space~-time, creating a node that is ``weaker'' than the surrounding area. This makes it easier for a psi to teleport himself or an object to its vicinity. The device has a simple on/off switch. While it is active, teleportation by any means (Autoteleport, Exoteleport, etc.) to a location within its radius is at +4 to skill. 

The side effect of this is that teleportation attempts within 1\% of the radius of an active jump beacon is at -2 to skill if they would teleport the subject \textit{farther away} from the beacon.

\textit{Portable Jump Beacon:}\label{itm:portable_jump_beacon} A suitcase~-sized unit that generates a node that covers a 500-yard radius. \$40,000, 30 lb., 2D/2 days. LC4.

\textit{Local Jump Beacon:}\label{itm:local_jump_beacon} A bulky, cabinet~-sized installation with a node that covers 10,000-yard radius. \$1,000,000, 300 lb., external power. LC4.

\subsection{Jump-Vortex Generator}\label{subsec:jump-vortex_generator}
This variation on jump beacon technology is used as a psionic trap for teleporters. The jump vortex attempts to intercept anyone using psionics to teleport to or from any destination within its radius, drawing him to it instead. It has a similar effect on objects teleported with Exoteleport. People or items successfully diverted by the vortex appear adjacent to the generator.

A jump vortex's area of effect depends on the device's power; two examples appear below. The vortex can ``catch'' people and things teleporting out of or into that area -- any trip with an origin or a destination within the vortex's radius risks being diverted. If two or more vortices are within range, the teleport is drawn to the nearest one.

A psionic teleporter may be able to resist the vortex's influence. If the skill roll for his Teleportation ability succeeds by a sufficiently large margin, the teleport isn't diverted. The psi senses a mysterious ``pull'' attempting to drag him or the object he's teleporting off course. If he resists \textit{and} gets a critical success, he senses the vortex's location.

Jump vortices are typically used as traps to snare intruding teleporters, and often built into secure areas such as prisons. But they can also be helpful! A porter deliberately trying to go to or send something to a vortex receives the same bonus that a jump beacon (above) would give.

\textit{Portable Jump Vortex:}\label{itm:portable_jump_vortex} A suitcase-sized unit with a 200-yard range. It can fit in a backpack and is easily installed in a room (often under the floor or furniture). To resist its pull, a teleporter must succeed by 3+. \$200,000, 40 lb., 2D/4 hr. (or external power). LC3.

\textit{Local Jump Vortex:}\label{itm:local_jump_vortex} A heavy installation with a 2,000-yard range. To resist its pull, a teleporter must succeed by 5+. \$5,000,000, 500 lb., external power. LC3.

\subsection{Teleport Jammer}
A teleport jammer exerts a ``tightening'' effect on the local space-time, making it difficult to teleport into or out of the area it covers. Within its field, skill rolls for all Teleportation abilities other than Portersense are at \textit{-10}. This penalty diminishes by -2 per full 10 yards of distance from the device; e.g., a psi who’s 40 yards from a teleport jammer has only -2 to his Autoteleport, Exoteleport, and Innerportation skills.

When someone with Teleportation abilities first comes into contact with the edge of the field, the GM should make a Per-based roll against the porter’s \textit{best} Teleportation psi skill at -3 (ignore this penalty if he has Portersense). Success gives him a hint that something is ``not right'' in the area; success by 3+ or critical success tells him that he’s near a teleport jammer.

The generator is a semi-portable device that can affect up to a 50-yard radius. \$500,000, 100 lbs., 4C/2 weeks (or external power). LC3.