\section{Personal Items}
%\addcontentsline{toc}{section}{Personal Items}
\label{sec:personal_items}
\subsection{Attaché Case}
A briefcase made of tough, high impact armorplast. It has DR 12. It can be fitted with any standard lock or security system. It can also be coordinated with any outfit, thanks to a varicloth surface with a few dozen different patterns programmed into it. A fingerprint lock system prevents anyone but the owner from changing the pattern. \$80, 2 lbs, LC4. \label{itm:attache_case}

\subsection{Pocket Pack}
Standard issue on ships, containing six invaluable items for technicians and spacers: penlight, multitool (screwdriver, scissors, small knife, file, tweezers, bottle opener, and toothpick, \$10, 1/8 lb.), roll of vacuum-proof sticky tape (\$2, 1/8 lbs, 150 yards × 2 inches), marking pen (\$4 and 1/16 lb., will write on metal or glass, in temperatures from -150° to 400° F, in zero gravity and in vacuum), single meal's worth of food tablets (\$5, 1/4 lb.), candy bar (\$1, 1/8 lb., vacuum-proof wrapper). \$25, 0.75 lb. \label{itm:pocket_pack}

\subsubsection{Grooming and Style}
\textit{Cleaning Gel:} Quick-hardening gel that the user applies, then peels off with any dirt. Bottle with 7 applications worth: \$7, 1.5 lb.\label{itm:cleaning_gel}

\textit{Smart Brush:} Motorized micro-brush and vacuum cleaner used to remove dirt without water. Common in the field, on desert planets or on spacecraft. \$50, 0.5 lb., B/24 hr. \label{itm:smart_brush}

\textit{Depilatory Cream:} Painlessly removes hair, prevents growth (based on strength; for a month, year or permanently, no difference in cost). Comes in bottles good for several (~50) topical or 1 whole-body application. \$10, 0.1 lb. \label{itm:depilatory_cream}

\textit{Digital Shampoo:} Electrostatic films which assembled when exposed with water and bind to hair, turning into a programmable video screen. Hair-care products can break down the hair films or reinforce them, acting as high-tech styling gels and conditioners. They last for at most a month, though to ensure best quality, weekly applications are recommended. \$10/application. \label{itm:digital_shampoo}

\textit{Smart Hairspray:} Hair coating which, when applied, causes hair to automatically shed dirt and maintain flexibility. \$2/application (lasts 1 week). \label{itm:smart_hairspray}

\subsection{Bioplas Contact Lenses}
These correct vision problems and change eye color. They are constructed from bioplas, which allows them to be worn indefinitely. Normal scanners cannot detect them. \$20. \label{itm:bioplas_contact_lenses}

\section{Clothing}
%\addcontentsline{toc}{section}{Clothing}
\label{sec:clothing}
\subsubsection{Imprint Circuits}
Simple microcircuits and microprocessors can be printed onto cloth (or even flesh). For \$10, a solar-powered electronic device such as a chronometer or calculator can be imprinted onto nearly any surface. Artistic designs made out of multicolored LEDs are available. \label{itm:imprint_circuits}

\subsubsection{Computer Clothing}
General-purpose computers can also be clothing. A small computer with the printed option will fit on a single garment such as a shirt or dress. Complexity 5, 10 TB. \$100, 0.5 lb., 2Bf/20 hr. LC4. \label{itm:computer_clothing}

\subsubsection{Varicloth}
Cloth using imprinted circuits to alter its color and/or pattern. A single article of clothing can be bought with a half-dozen different color patterns programmed into it. Running a finger over a concealed sensor in the garment switches the pattern. +2 CF. \label{itm:varicloth}

\subsubsection{Buzz Fabric}
\label{subsec:buzz_fabric}
Contain microscopic circuitry and brushes that eject dit and grime, allowing anything made with Buzz Fabric to clean itself. Someone weaing buzz-fabric can be totally clean moments after falling down in a mud puddle. Dirt is ejected, not destroyed.

Buzz fabric sheds water, and dries five times faster than normal cloth. This makes it very popular for rainwear. Despite its nickname, buzz fabric doesn't make an audible noise. + 1 CF for normal clothing or fabric and versions are available for flexible armor and most types of environmental suits, also +1 CF. For bioplastic, it is only +0.2 CF. \label{itm:buzz_fabric}

\subsubsection{Responsive Fabric ("Memswear")}
Clothing, footwear, and imitation-leather goods can be made with integrated microelectromechanical systems (MEMS). These tighten or loosen to produce a stylish and comfortable fit.

Not quite one-size-fits-all, it offers more tolerance than ordinary clothing. Memswear can also change porosity, adjust to temperature and humidity, and absorb sweat stains. Normally, +2 CF, but when incorporating buzz fabric or varicloth, +3 CF (thus totalling +4 CF). Bioplastic suits already incorporate responsive fabric as standard. \label{itm:memswear}

\subsection{Swimwear}
\label{subsec:swimwear}
This is a full-body ultra-smooth low-drag swimsuit and optional set of swim fins. Fins take four seconds to attach or remove, and add +1 to Basic Move for the purpose of figuring Water Move. When wearing fins on land, Move suffers a -1 penalty.

% \textit{Biomimetic Swimsuit:} +1 to Basic Move for Water Move; with fins, total bonus is +2. Design inspired by fish skin. \$100, 0.2 lb. (\$150, 0.3 lb. with fins). \label{itm:biomimetic_swimsuit}

\textit{Bioplas Swimsuit:} +2 to Basic Move for Water Move. with fins, total bonus is +3. Similar to the biomimetic swimsuit, but incorporates a layer like slickskin. Also heals any rips automatically. The fins are detachable. \$100, 0.1 lb. (\$150, 0.2 lb. with fins). \label{itm:bioplas_swimsuit}

\subsection{Suitspray}
\label{subsec:suitspray}
Spray tube containing a smart polymer that sticks to bare flesh, then solidifies into a skintight fabric with the look and feel of a silk body stocking. It provides as much warmth as light summer clothing, while being porous enough to allow the wearer's skin to breathe. Various colors are available, including skin tone, metallic colors, and translucent models. It has no DR. 

Donning suitspray requires spraying it over the body. This takes about 20 seconds, half that if someone else is helping. It does not wash off in ordinary water, but rinsing with a special soap or sonic shower will remove it within 30 seconds. (So will 10 seconds of stunner fire, or any hit by a screamer.)

\textit{Suitspray:} A can holding enough suitspray to cover an adult human. \$4, 0.25 lb. Flakes off in two days if not removed. LC4. \label{itm:suitspray}

\textit{Video Suitspray:} As above, but incorporates digital ink, transforming the body into a low-res video screen. This is usally controlled by a wearable computer, and is equivalent to programmable camoflage. A can is \$20, 0.25 lb. LC4. \label{itm:video_suitspray}

\textit{Slicksuit Spray:} Suitspray that incorporates a layer similar to slickskin. It has the same effects as slickskin, but wears off after a day. Avoid spraying it on the soles of feet or palms of hands. \$40, 0.25 lb. LC3. \label{itm:slicksuit_spray}

\subsection{Swarmwear}
\label{subsec:swarmwear}
Any cloud of aerostat microbots can be programmed to hover in close formation around their master, forming a body suit, a trailing cloak, a veil and cloak, etc.

Up to 4 square yards of swarms can combine around a SM 0 person. A 1-square yard swarm is wispy; 2-square or larger swarm covering a single person will be opaque. Swarmwear can only act upon the wearer or anyone touching him.

A person using swarmwear can't move any faster than the swarm's top speed (unless they land on them, which prevents them from performing their normal functions).
If the swarmwear is enough to be opaque, it provides DR 1.


\section{Entertainment}
%\addcontentsline{toc}{section}{Entertainment}
\label{sec:entertainment}
\subsection{Cybervox}
\label{subsec:cybervox}
Combination sound mixer, synthesizer, and digital recorder. A cybervox can analyze, record, duplicate, and modify any sound (short of dangerous ultrasonic or sub-sonic frequencies), including music and speech. Can be used as an electronic musical instrument. Often worn on a shoulder strap; some are built into instruments such as guitars. Provides a +1 (quality) bonus to appropriate Electronics Operation (Media) or Musical Instrument tasks. \$200, 2.5 lb., C/10 hr. LC4. \label{itm:cybervox}

\subsection{Electronic Ecstasy}
%\addcontentsline{toc}{subsection}{Electronic Ecstasy}
\label{subsec:electronic_ecstasy}
These devices use neural technology to produce continuous sensory pleasure.

\textit{Euphoria Machine:} Connected to user via direct neural interface, this device electrically stimulates the brain's pleasure centers for as long as it is worn. It is very addictive. If trying to function while using it, the user suffers the Euphoria irritating condition (B428), and must roll vs. Will each week to avoid addiction. It is small enough to be discreetly attached to a belt or headband. \$100, 0.1 lb., A/100 hr. LC3. \label{itm:euphoria_machine}

\textit{Ecstasy Machine:} A more powerful device, usually worn in bed. Works the same way as a euphoria machine and can function at "low power" as one. It can also be set for a level of pleasure instense enough that the user can do nothing else: this is the Ecstasy incapacitating condition (B428). Roll vs. Will-3 each day that the device is used to avoid addiction. \$500, 0.5 lb., 2A/24 hr. LC2. \label{itm:ecstasy_machine}

\textit{Neurostimulator:} Can be handheld or implant. Uses direct neural induction to produce an effect similar to the euphoria machine. It does not require a neural interface, but works only as long as it is in contact with bare flesh, plus a second after. The intensity increases to incapacitating ecstasy if applied to erogenous zones. Takes a few seconds to build to full intensity, making it ineffective as a weapon. It can provide a +2 (quality) bonus to both Erotic Art skill and to Interrogation skill with a cooperative or restrained individual. \$100, 0.2 lb., A/1 hr. LC3. \label{itm:neurostimulator}

\section{Recreational and Personal Robots}
%\addcontentsline{toc}{section}{Recreational and Personal Robots}
\label{sec:rec_and_personal_robots}

% \subsection{7Sign General Purpose Robot Body}

% % \setlength{\parindent}{0pt}
% \begin{hangparas}{1em}{1}
%     \noindent\textbf{Attributes:} HT+1 [10]; ST+3 [30].
    
%     \noindent\textbf{Secondary Characteristics:} HP+7 [14].
    
%     \noindent\textbf{Advantages:} Absolute Direction [5]; Doesn't Breathe [20]; DR 5 [25]; Machine [25]; Payload 1 [1]; Protected Vision [5]; Radio (Burst, +30\%; Secure, +20\%) [15]; Reduced Consumption 2 [4].
    
%     \noindent\textbf{Perk:} Accessories (Personal computer) [1].
    
%     \noindent\textbf{Disadvantages:} Electrical [-20]; Maintenance (one person, bi-weekly) [-3].
%     \$50,000, 100-250 lb., 2D/24 hr. LC4. \label{robot_7sign_general}\\
% \end{hangparas} 
% \subsection{7Sign Hospitality Android}
% \label{subsec:7sign_hospitality}
% 7Sign produces this volitional android line and contracts them out. Generally speaking, the customer pays for a discounted amount of the android's production cost (between 30-60\% of \$50,000) with the caveat that a percent of the Android's wages go to 7Sign.

\subsection{General Android}\label{subsec:general_android}
\hfill{\large \textbf{111 points}}

This general-purpose humanoid robot body comes in
male, female, and androgynous versions. Custom designs,
including those that resemble real people, are also possible.
Higher-TL models are cheaper and more reliable.

\begin{hangparas}{1em}{1}
    \textbf{Attribute Modifiers:} ST+3 [30].
    
    \textbf{Secondary Characteristic Modifiers:} HP+7 [14].
    
    \textbf{Advantages:} Absolute Direction [5]; Doesn't Breathe [20]; DR 5 [25]; Machine [25]; Payload 1 [1]; Protected Vision [5]; Radio (Burst, +30\%; Secure, +20\%) [15].
    
    \textbf{Perk:} Accessories (Personal computer) [1].
    
    \textbf{Disadvantages:} Electrical [-20]; Restricted Diet (Very Common, power cells) [-10].
\end{hangparas}

\subsubsection{Lenses}
Choose a age lense, a machine intelligence lens (p \pageref{sec:machine_intelligence_lenses}), and a biomorphic lens (p. \pageref{sec:biomorphic_lens}) for the robot.
\begin{hangparas}{1em}{1}
    \textit{Old Model} (-5 points): Add Maintenance (one person, weekly) [-5]. \$35,000, 150-250 lbs., 2D/8 hr. LC4.
    
    \textit{Modern Model} (+11 point): Add HT+1 [10]; Maintenance (one person, bi-weekly) [-3], Reduced Consumption 2 [4]. \$50,000, 100-250 lbs., 2D/24 hr. LC4.
\end{hangparas}

\subsubsection{Optional Lenses}
\begin{hangparas}{1em}{1}
    \textit{Child Body} (-30 points): A smaller robot body, the size of a 9- to 12-year-old. Remove the ST bonus. Halve the body weight and number of power cells (e.g., D instead of 2D). -40\% to cost.\\
\end{hangparas}

\subsection{Petbot}\label{subsec:petbot}
\hfill{\large \textbf{71 points}}

This is a small mechanical beast with a head and four legs. It may look cute or fierce, depending on the market. Typical models resemble small dogs, house cats, miniature dinosaurs, and so on, although they usually have modified paws or claws with opposable thumbs that give them some manipulatory ability.

Robots of this type are often used for home security, keeping track of children, or pest control. They can be equipped with a range of sensors and “natural'' weapons. 

\begin{hangparas}{1em}{1}
    \textbf{Attribute Modifiers:} ST-3 [-30].
    
    \textbf{Secondary Characteristic Modifiers:} SM-2; HP+1 [2]; Basic Move+5 [25].
    
    \textbf{Advantages:} Absolute Direction (Requires signal, -20\%) [4]; Doesn't Breathe [20]; Discriminatory Smell [15]; DR 5 (Cannot Wear Armor, -40\%) [15]; Extra Legs (4 legs) [5]; Infravision [10]; Machine [25]; Radio (Secure, +20\%) [12]; Sharp Claws [5]; Sharp Teeth [1]; Ultrahearing [5].
    
    \textbf{Perks:} Accessories (Small computer; fire extinguisher) [2]. Disadvantages: Bad Grip 1 [-5]; Electrical [-20]; Horizontal [-10]; Restricted Diet (Very Common, power cells) [-10].
\end{hangparas}

\subsubsection{Lenses}
Select one of the TL options. Also select a machine intelligence lens (p. \pageref{sec:machine_intelligence_lenses}) and a biomorphic lens (p. \pageref{sec:biomorphic_lens}).

\begin{hangparas}{1em}{1}
    \textit{Vintage Model} (-5 points): Add Maintenance (one person, weekly) [-5]. \$7,500, 20-50 lbs., 2C/8 hr. LC4.
        
    \textit{Modern Model} (+1 point): Add Maintenance (one person, bi-weekly) [-3], Reduced Consumption 2 [4]. \$10,000, 20-50 lbs., 3C/24 hr. LC4.
\end{hangparas}

\subsection{Recreational Swarms}\label{subsec:recreational_swarms}
These are microbot or nanobot types. See Swarmbots (p. \pageref{sec:swarmbots}).

\subsubsection{Massage Swarm}\label{subsubsec:massage_swarm}
These swarmbots are similar to a cleaning swarm (p. \pageref{subsec:cleaning_swarm}), but they are equipped and programmed to deliver relaxing or erotic tactile sensations to their subject. They use Professional Skill (Massage)-10 and Erotic Art-10, (+1 per TL after introduction), or provide a +5 (quality) bonus to someone directing them. \$200/square yard. LC4.

\subsubsection{Play Swarm}\label{subsubsec:play_swarm}
These swarmbots are equipped to play and interact with one another in an amusing fashion. For example, a ``farm in a box'' might contain 'bots that look and act like tiny animals, agricultural robots, human farmers, and so on. \$200/square yard. LC4.