\section{Maintaining Gadgets}\label{sec:maintaining_gadgets}
Simple objects don't require much maintenance. If an object costs less than \$50, it generally is simple enough that it will work indefinitely without need for repairs. 

Some items -- especially those that are complex or regularly placed under stress -- may require periodic ``maintenance checks.'' Most of the time, this can be assumed to have happened during downtime (such as during long space voyages), but if, for whatever reason, it takes place ``on screen'' it requires a  roll against a suitable technical skill, as described for the Maintenance disadvantage (p. B143). M

Missed or failed maintenance checks result in HT loss (if an item does not have a listed HT, assume 10). This HT loss is cumulative, and affects any HT rolls the equipment must make (see \textit{Effects of Injury} p. B483 and \textit{Slime, Sand, and Equipment Failure} p. B482).

As mentioned above, these rules do not apply to simple items, equipment in storage, or anything unused in a sealed case (or equivalent). 

\section{Repairing Gadgets}
If a gadget breaks down, it requires either a minor or a major repair. Performing repairs requires the appropriate repair skill. Use:

\begin{itemize}
    \item Armoury for weapons and defenses.
    \item Computer Operation for software problems.
    \item Electronics Repair for electronic devices
    \item for power transmission systems, power cells, and their interfaces.
    \item Machinist for manufacturing plants and tools.
    \item Mechanic for robots, power plants, and vehicles.
    \item Sewing for fabric (other than body armor).
\end{itemize}

Some complex systems may require more than one skill. Except for software repairs, appropriate tools are needed -- see \textit{Tool Kits} (p. \pageref{subsec:tool_kits}).

\textit{Minr Repairs:} Each attempt to repair damaged equipment that still has positive HP requires half an hour and a successful skill roll. See \textit{Equipment Modifiers} (p. B345) and \textit{Time Spent} (p. B346) for common modifiers. As well, if the device costs \$1,000 or less, roll at +1; if it costs \$10,001~-\$100,000 at -1; \$100,001~-\$1,000,000 at -2; >\$1,000,000 at -3. Success restores 1 HP times the margin of success.

\textit{Major Repairs:} For equipment that has been reduced to zero or negative HP requires spare parts that cost 1d × 10\% of its original price. These spare parts can also be fabricated using the Machinist skill and the proper tools. After obtaining these parts, use the rules above, except at an extra -2. 

\section{Powering Gadgets}
Many gadgets require power. Near universally, these gadgets use the standardized power cells outlined in \textit{Power Cells} (p. \pageref{sec:power_cells}). 