\section{Burglary, Infiltration, and Sabotage}\label{sec:burglary_inf_sabo}
%\addcontentsline{toc}{section}{Burglary, Infiltration, and Sabotage}
These gadgets are useful for cracking security measures, or entering hard~-to~-reach places.



Items listed elsewhere that are helpful for burglars include explosives (p. \pageref{subsec:explosives}), laser torches (p. \pageref{subsec:laser_plasma_torches}), plasma torches (p. \pageref{subsec:laser_plasma_torches}), sonic probes (p. \pageref{subsec:sonic_probe}), and tool kits (p. \pageref{subsec:tool_kits}).

Gadgets mentioned elsewhere that are especially useful for infiltration include diver propulsion (p. TODO), flight packs (p. TODO), and stealth drop capsules (p. TODO). Demolitions (p. \pageref{sec:demolitions}) and gremlins (p. TODO) are useful for sabotage operations. Portable fabricators (p. \pageref{itm:minifac}) are also extremely useful for any black ops team.

\subsection{Electronic Lockpick}\label{subsec:elec_lockpick}
This sensor/decoder gives a +3 to Lockpicking and Electronics Operation (Security) skill on attempts to pick any electronic or combination lock. \$1,500, 0.2 lb., A/2 hr., LC2.

\subsection{Biometric Cracker Tools}\label{subsec:biometric_cracker_tools}
This sensor/decoder gives a +3 to Lockpicking and Electronics Operation (Security) skill on attempts to defeat any biometric scanner. \$4,000, 10 lb., A/2 hr. LC2.

\subsection{Electronic Thumb}\label{subsec:electronic_thumb}
An electronic thumb counter retina and fingerprint scanners. The pocket~-sized gadget has the size and shape of an eyeball, and lights from within to display a retina pattern. The other end has the shape of a lumb and wams to body temperature. Its memory plastic pad can be configured to match any thumbprint in the device's memory. New thumb and retina prints can be downloaded into it by connecting it via cable to an appropriate database. Getting thumb or retina prints for the database may not be easy -- high~-quality photos of the targets' eyes and actual thumb impressions are needed. \$5,000, 0.25 lb., A/100 hr. LC3.

\subsection{Electromagnetic Autograpnel}\label{subsec:electromag_autograpnel}
This uses an electromagnetic coil gun to silently fire a grappling hook up to 30 yards. Make a Climbing or Guns (Grenade Launcher) roll to hit, at -2 if unfamiliar with this gadget (see p. B169). An electromagnetic winch on the gun lifts up to 800 lb. at up to 5 yards per second. The reel constians 30 yards of 1/8"~-diameter rope (p. \pageref{itm:rope_1/8}). \$500, 5 lb., C/15 min. LC4.

\subsection{Gecko Gear}\label{subsec:gecko_gear}
These gloves and footwear let the user cling to walls and ceilings and move at half her Basic Move; no use of Climbing skill is necessary. Gecko gear designed for humanoids can support only 50 lbs. per limb in contact with the surface, including the user’s body weight. An adult human won’t be able to carry much gear with her. If the user’s weight requires three or four limbs in contact, she will be limited to crawling. Each pad is \$500 and 0.1 lbs. weight. They can be built into armor or other suits. LC3.

\subsection{Sonic Screen}\label{subsec:sonic_screen}
Worn strapped onto a belt, this forms a portable privacy field (p. TODO) which moves with the wearer. The field is three yards in diameter. Sounds from outside the field cannot be perceived by someone inside the field (-10 to detection), and vice versa. The field also provides DR 10 against sonic attacks. Assassins and thieves use sonic screens to make the victims’ cries inaudible. \$5,000, 2.5 lbs., C/1 hr. LC3.

\subsection{Variable Lockpick}\label{subsec:variable_lockpick}
A memory~-metal lockpick with a small imaging radar, an ultrasound imager, and its own contact mike. It reconfigures its shape into one of several hundred alternative forms after performing a sensor analysis of the lock. It includes a fiber-optic scope. Gives +4 to Lockpicking skill to open mechanical locks. It fits in a wallet., \$50, neg., A/12 hr. LC2.

\section{Forgery and Counterfeiting}\label{sec:forgery_counterfeit}
%\addcontentsline{toc}{section}{Forgery and Counterfeiting}

\subsection{Document Fabricator}\label{sec:document_fab}
This is a dedicated terahertz scanner, and a specialized 3D printer to copy and manufacture the special dyes, fibers, films, foils, inks, papers, and plastics used in identity documents or currency. With a sample to analyze, they can forge documents from any prior TL.

\textit{Desktop Doc-Fab:}\label{itm:desktop_doc-fab} Table~-sized. Provides a +2 (quality) bonus for Forgery and Counterfeiting skills at the modern TL. For older TL documents, the bonus is +5. Most documents take an hour per attempt to scan plus a minute per copy to print. \$20,000, 50 lb., 4D/10 hr. LC2.

\textit{Suitcase Doc-Fab:}\label{itm:suitcase_doc-fab} Suitcase~-sized. Provides a +1 (quality) bonus for Forgery and Counterfeiting skills at its own TL, increasing to +5 for any lower~-TL documents. Most documents take about two hours per attempt to scan, plus five minutes per copy to print. \$4,000, 10 lb., 4C/10 hr. LC2.

\section{Disguises and Smuggling}\label{sec:disguises_smuggling}
%\addcontentsline{toc}{section}{Disguises and Smuggling}
This section covers gadgets and technology for personal concealment and the smuggling of people or items. Distortion chips (p. TODO) are another useful technology.

\subsection{Disguise Kit}\label{subsec:disguise_kit}
An elaborate set of prosthetic devices, skin~-tinting checmicals, and hormone sprays for disguising one person's appearance. Many components incorporate microelectromechanical systems that can mimic muscle twitches, realistic lims, and other key characteristics.

\textit{Suitcase Disguise Kit:}\label{itm:suitcase_disguise_kit} Provides a +1 (quality) bonus to Disguise skill. \$200, 10 lb., LC3.

\textit{Disguise Fabricator:}\label{itm:disguise_fab} Desgined specifically for intelligence agents. Provides a +2 (quality) bonus for the Disguise skill. \$800, 50 lb., LC2.

\subsection{Shape~-Memory Disguises}
Memory~-plastic and memory~-metal technology can disguise weapons and other suspicious items as innocuous devices of the same general shape and size. Another possibility is to break the contraband down into several parts, each of which appears to be an unrelated piece of equipment.

\textit{Singe~-Function:}\label{itm:shape-mem_single-function} While disguised, the gadget doesn't funciton (except as much as its basic shape allows). It costs five times as much as a normal version of the original gadget. 

\textit{Multi~-Function:}\label{itm:shape-mem_multi-function} Both the disguise and the disguised gadget are fully functional. Cost is 20 times the sum of the cost of \textit{both} the gadgets. Both gadgets must be within 10\% weight.

Shape~-memory devices usually incorporate a power cell (an AA cell for devices up to 0.1 lb. weight, A cell for up to 1 lb., B cell for up to 10 lb., etc.) to provide an electrical impulse that triggers the change. The cell powers 60 changes and is removable if power cells would be suspicious. A simple gadget may also use a piezoelectric material that changes if shaken vigorously for 10 seconds.

A gadget with a shape~-memory disguise has \textit{half} its normal LC (rounded up). 

\subsection{Stealth Luggage and Cargo}\label{subsec:stealth_luggage_cargo}
These items use the latest in electronic countermeasures and stealth materials to spoof scanners and sniffers. A hidden liner compartment provides safety for small packages, while a biometric lock (p. TODO) provides security. The liner compartment holds one~-tenth the luggage's capacity and provides a +2 (quality) bonus to Smuggling skill. It is sealed to defeat chemical sniffers and dogs.

\textit{Attaché Case:}\label{itm:stealh_attache_case} Holds up to 20 lb. (or two cubic feet). \$400, 2 lb. LC3.

\textit{Travel Bag:}\label{itm:stealth_travel_bag} Holds 100 lb. (or five cubic feet). \$1,200, 10 lb. LC3.

\textit{Trunk:}\label{itm:stealth_trunk} Holds 400 lb. \$4,000, 40 lb. LC3.

\textit{Shipping Container:}\label{itm:stealth_shipping_contain} Holds 10,000 lb. Up to four SM 0 people can hide in the liner compartment, but they'll need breathing gear. \$10,000, 1,000 lb. LC3.

These items may have programmable camouflage (p. TODO) surface at +0.5 CF. Distortion chips or fields (p. TODO) can also be added. 

\subsection{Voice Mask}\label{subsec:voice_mask}
This wearable mic obscures the speaker's voice. They can set it to sound human, but different than their normal voice, or to change their apparent age, accent, gender, or species. It will also alter the speaker's voiceprint. \$200, 0.1 lb., B/20 hr. LC3.

\subsection{Active Flesh Mask}\label{subsec:active_flesh_mask}
A full~-face mask of a \textit{specific} person, complete with micromotors that move the face in realistic fashion. This is a custom design, and detailed measurements of both the user and the subject's face (which can be taken by medical examination, or remotely by T-ray scanner, X-rays, or ultra-scan) are needed. It takes 10 seconds to put on, two seconds to remove. 

The mask adds +3 to Disguise skill, cumulative with quality modifiers. When impersonating somebody, this is the perfect disguise, but in order to convince someone who knows the individual being mimicked requires a successful Acting roll. The mask's legality class is a reflection of its legal uses in media productions and as a prosthetic. It includes a voice mask (above). \$10,000, 1 lb., B/24 hr. LC3.

\subsection{Dynamic Holotech}\label{subsec:dynamic_holotech}
This holographic projector casts a preset 3D image. It will not fool sensors that do not use visible light, such as infrared or hyperspectral imaging. Because it projects light, it glows in the dark.

\textit{Holobelt:}\label{itm:holobelt} Casts an image around the wearer, roughly human-sized, for concealment. The image must be bigger than the person concealed. Standard holodisks let the user choose between a native~-looking rock, tree, mailbox, bush, animal, etc., or plug in a disk taken from a 3D camera. All attacks on the user are at -1 to hit, and aimed shots to specific body areas are not possible unless the image closely rembles the user's body. \$2,000, 2.5 lb., C/10 hr. CL3. Prerecorded holodisks are usually about \$50.

\textit{Holofield:}\label{itm:holofield} A larger model of the holobelt, used to disguise buildings, camps, and vehicles. The field will cover a radius of up to 10 yards. New images can be captured via a 3D camera or synthesized with a computer. \%50,000, 25 lb., D/10 hr. LC3.

\section{ECM and Stealth}\label{sec:ecm_stealth}
%\addcontentsline{toc}{section}{ECM and Stealth}
Electronic countermeasures used to jam or deceive surveillance sensors.

\subsection{Chameleon Surface}\label{subsec:chameleon_surface}
A suit can be equipped with sensor~-controlled active camouflage that changes color and pattern to match the local background environment, in both the visual and infrared spectra. This provides a bonus to the user' Stealth skill when attempting to avoid visual and infrared detection. The bonus is halved against hyperspectral or ultraviolet vision.

The system can also be manually controlled, allowing the user to ``paint'' the surface with whatever color scheme or markings are desired (as \textit{Programmable Camouflage}, p. TODO), or to give a mirrored skin equivalent to reflec armor (p. TODO).

\subsubsection{Thermo~-Optic Chameleon Surface}\label{subsubsec:thermo-optic_chameleon_surf}
This may be added to an outfit covering an entire body, or to a vehicle surface. It gives +4 to Stealth skill against ordinary and infrared vision, +2 against hyperspectral or ultraviolet vision, and +1 against extended high~- or low~-band hyperspectral vision. This bonus halved (round down) if moving. \$4,000, 4 lb. (adjust for SM). LC3.

\subsubsection{Multispectral Chameleon Surface}\label{subsubsec:multispec_chameleon_surf}
This versio gives +8 to Stealth skill against ordinary and infrared vision, +4 against hyperspectral or ultraviolet vision, and +2 against extended high~- or low~-band hyperspectral vision. This bonus is halved if moving. \$6,000, 4 lb. (adjust for SM). LC3.

\subsubsection{Chameleon Cloak}\label{subsubsec:chameleon_cloak}
A large cloak that can be wrapped around a person or object to conceal it. It works the same way as a chameleon surface, but the bonus is halved again, cumulative with other modifiers (round down!) when moving! It can also be used just like any other large cloak. It is half the cost and weight of an equivalent chameleon surface. LC3.

\subsubsection{Chameleon Net}\label{subsubsec:chameleon_net}
This camouflage net works much like a large chameleon cloak, and can hide vehicles, heavy equipment, or campsites. It covers 25 square yards, and is 10 times the cost and weight of an equivalent chameleon surface. LC3.

\subsection{Deception ECM}\label{subsec:deception_ecm}
These devices detect and mimic incoming active sensor pulses to give a distorted or false reading of the user. Most models can jam radar and imaging radar \textit{or} sonar. The Raven-tech variant uses a ``distortion field'' derived from the Ravens called no-eyes. 

They can also be set to spoof rather than just jam. If so, there is no penalty to detection, but the sensor operator must succeed by an amount \textit{greater} than half the detection penalty, or he is fooled into detecting something \textit{else.}

\textit{Deceptive Radar Jammer:}\label{itm:deceptive_radar_jammer} This jams all types of radar signals: -6 to radar, -4 to imaging radar. Spoofing is only possible for non-imaging radar; successfully doing so can change the user's apparent size and course by up to $\pm$6 SM or 60\degree. \$2,000, 2.5 lb., C/10 hr. LC2.

\textit{Deceptive Sonar Jammer:}\label{itm:deceptive_sonar_jammer} This emits deceptive sonar signals: it gives a -6 to sonar detection. Successsfully spoofing sonar can change the user's apparent size and course by up to $\pm$6 SM or 60\degree. \$2,000, 2.5 lb., C/10 hr. LC2.

\textit{No~-Eye Distortion Field Belt:}\label{itm:no-eye_distort_field_belt} -6 to \textit{all} active sensors. Successful spoofing can provide a pre~-set, seemingly accurate, but completely false (within the limits of the spoofed sensor) and/or change the apparent size and course by up to $\pm$6 SM or 60\degree. If the belt is significantly damaged, it releases a horrifying shriek, deafeningly audible to anyone looking at the user as well as the user herself, make an HT-5 roll, +1 for every 2 yards from the user, or become deafened for a number of minutes equal to margin of failure. Failure by 5 or more permanently deafens. This renders the belt unusable until the mechanism is replaced. \$10,000, 2.5 lb., C/10 hr. LC2.

\textit{Holo~-Distory Belt:}\label{itm:holo-distort_belt} Combines a distortion belt with a holobelt (p. \pageref{itm:holobelt}). \$12,000, 3 lb., 2C/10 hr. LC3.

\textit{No-Eye Distortion Chip:}\label{itm:no-eye_chip} A small distortion field that protects a one~-foot radius around it. It is usually hidden in clothing or luggage, or attached to a weapon or other device to evade or spoof Search rolls that use active sensors. Provides the same penalty to sensors as the No~-Eye field belt, and has the same effect if significantly damaged, though its affects those who are looking at anything in the radius. \$500, 0.05 lb., A/4 hr. LC2.

Except for the distortion chip, these jammers protect roughly a human-size (SM 0) area. Larger objects like vehicles need bigger jammers: multiply cose, weight, and number of C~-cells by the square of the vehicle's \textit{longest} dimension in yards. (Substitute a D cell for 10 C cells, an E cell for 100 C cells, etc.)

\begin{ravenbox}
    \subsection{No~-Eyes}
    These Ravens lurk in the dark recesses of the universe. They appear as moving fields of distortion, obscure to all forms of surveillance. Looking at one (even remotely through any sensor) triggers its true ability. A ear~- and mind~-shattering noise assaults the senses, this requires an HT roll (at a penalty based on the strength of the no~-eye, generally a minimum of -12). Failure means the victim suffers Blindness and Deafness. Failure by 5 or more means these are permanent. 
    
    Sensors also make this roll if they see one, failure means the sensor is damaged; failure by 5 or more means that the sensor spontaneously explodes. Additionally, reflective materials which reflect its image also trigger this roll for themselves, failure ruins their reflectivity and failure by 5 or more significantly damages the surface. A No~-Eye witnessed through a survivng sensor or reflective surface still triggers the HT roll, but gives a +3 per layer of seperation (so seeing one that has been reflected off of two mirrors, gives a +6)

    No~-Eyes which have died and undergone a decontamination process are visible without danger. They look like a combination of an octopus and whale, ranging in size from a large dog to a semi~-truck.
\end{ravenbox}

\subsection{Infrared Cloaking}\label{subsec:infrared_cloaking}
This system reduces an object's heat signature to defeat infrared and thermal imaging detection. It subtracts -6 from rolls to detect via infrared or similar sensors. \$1,500, 3 lb. (adjust by SM). LC3. 

\subsection{Programmable Camouflage}\label{subsec:program_camouflage}
This electronic~-camouflage system allows the wearer to choose a color scheme from any of eight different patterns -- desert, snow/arctic, jungle, forest, underwater, urban, black, or high~-visibility orange. It takes three seconds to reset the suit. A suitable camouflage pattern gives +2 to Camouflage rolls, but a -1 to Camouflage rolls in non~-matching terrain, and a -2 in high~-contrasting terrain.

Programmable camouflage systems are a significantly cheaper alternative to sensor~-controlled systems, and are commonly used by civilian hunters, survey scouts, or lightly~-equipped military forces. This can be added to any outfit that covers most of the wearer: \$1,000, 2 lb. (adjust for SM). LC4.

\subsection{Radar Stealth}\label{subsec:radar_stealth}
Many suits of personal armor incorporate radar~-absorbent material as part of their structure. This subtracts -6 from detection by radar, imaging radar, or terahertz (T-ray) radar. Integral radar stealth systems are tandard with many armor suits. THey may also be added to any sealed suit: \$1,500, 3 lb. (adjust for SM). LC3.

\subsection{Scent Masking}\label{subsec:scent_masking}
This seal prevents any chemicals from leaving the clothing. It provides a +4 on Tracking when trying to cover your scent trail. Available for any sealed suit. \$200, 1 lb. LC4.

\subsection{Invisibility Surface}\label{subsec:invisibility_surface}
This active optical camouflage system renders the user nearly invisible. Its fabric incorporates thousands of embedded nanocamers and projectors to create a seamless ``projection stealth'' system. Controlled by a fast dedicated computer, this captures images of the user' surroundings, then displays photorealistic imagery that can fool observers from multiple angles and perspectives.

The user is invisible. They get +9 to Stealth rolls in most circumstances. The invisibility is effective against living things and machines, and will fool cameras. The user casts a visible shadow. They also appear as a shadow when silhouetted \textit{directly} against the sun or any other extremely bright light source (such as a searchlight); reduce the Stealth bonus to +3 under these conditions. When they move, there is a faint shimmering that others can spot with a Vision-6 roll, and target in combat at -6 to hit.

The suit can also function as a video display terminal. The user can ``paint'' the suit with any desired color or patter; this reduces the power drain by a factor of 10. This effect is only effective against visual and infrared (or thermal) imaging.

\subsubsection{Invisibility Surface}\label{subsubsec:invisibility_surface}
The cost and weight includes coverage for gloves, boots, and a helmet of hooded mask. \$20,000, 4 lb., 2C/30 min. LC2.

\subsubsection{Invisibility Cloak}\label{subsubsec:invisibility_cloak}
This optical camouflage cloak can be wrapped around a person or object to conceal it. This works like an invisibility surface, but provides only a +3 bonus when moving. \$10,000, 4 lb., C/15 min. LC2.

\subsubsection{Invisibility Net}\label{subsubsec:invisibility_net}
This invisibility cloak is large enough to hide vehicles, heavy equipment, or a base camp. It covers 25 square yards. \$200,000, 50 lb., 2D/8 hr. LC2.

\section{Computer Intrusion}\label{sec:computer_intrusion}
%\addcontentsline{toc}{section}{Computer Intrusion}
These hardware devices retrieve data from computers or their interfaces. For online intrusion, use software tools (p. \pageref{subsec:software_tools}) for Computer Hacking or Computer Programming. For hacking encryption, see \textit{Quantum Computers} (p. \pageref{subsec:quantum_comms}).

\subsection{Computer Monitoring Gear}\label{subsec:computer_monitor_gear}
Computer equipment emits radio signals when in use. This gadget picks these up. It can detect whatever data is being typed or displayed on an interface screen at a distance, allowing someone to eavesdrop on computer activity. It cannot read what is stored inside the computer. It can scan through walls, provided they are not shielded.

Using the device requires an Aim maneuver for the duration of the surveillance; roll against Electronics Operation (Surveillance) to get clear data. High~-security systems will likely be shielded against these emissions, but these tools remain useful when infiltrating less secure systems.

\textit{Mini Scanner:}\label{itm:mini_scanner} 100~-yard range; -1 to skill per 10 yards range. \%500, 0.1 lb., A/10 hr. LC2.

\textit{Long~-Range Scanner:}\label{itm:long-range_scanner} 1,000~-yard range; -1 to skill per 100 yards of range. \$5,000, 5 lb., C/10 hr. LC2.

\subsection{Keyboard Bug}\label{subsec:keyboard_bug}
This pinhead~-sized adhesive bug can be stuck to the bottom of a terminal's keyboard. It uses induction to read the keystrokes, recording everything that gets typed in its memory. It can record a terabyte. The bug can be retrieved manually, or it can be programmed to send out the data as coded burst transmission using its radio microcommunicator (p. \pageref{itm:radio_comm_micro}). It runs for a year. \$200, weight is negligible. LC3.

\subsection{SQUID}\label{subsec:squid}
A superconducting quantum interference device is used to interrogate a computer brain to retrieve data, \textit{even if that system is offline.}

\textit{Contact SQUID:}\label{itm:contact_squid} This SQUID must be physically attached to the target computer, it can then assist in reading the data stored within. \$20,000, 5 lb., 2C/10 hr. LC3.

\textit{Memory Scan:}\label{itm:memory_scan} Any ultra~-scan (p. TODO) active sensor with this modification can scan a computer that it has detected. +2 CF to the sensor. LC2.


\newcommand{\redbookname}{\textit{The Collection of Tools of Anti~-Creation; Blessings of The Entropic Heaven}}
\subsection{Red Key}\label{subsec:red_key}
Also known as an ``Oblivion Chip,'' this bizarre object was originally created from a corrupt blueprint found in the ``Red'' Spectral Codex also known by its title, \redbookname{}. It looks like a small, red data~-drive. When connected to a computer, the drive infects the computer with a bizarre virus which decrypts everything on the computer automatically. The virus then begins destroying all data. The only thing that can stop it is the removal of the key, upon being disconnected all the encryption and security systems return and any spread viruses vanish. LC0.

Also known as an ``Oblivion Chip,'' this bizarre object is based on a design found in the ``Red'' Spectral Codex or \redbookname{}. It looks like a small, red data~-drive. When connected to a computer, it begins devouring data bit~-by~-bit. Depending on the quality of the specific key, it consumes anywhere from 100 GB a second to 1 PB a second. This process can be taken advantage of, as it seems to destroy encryption as part of its devouring process, so if an intruder can risk deleting data, it can easily overcome most encryption. If the computer is connected to a network, the key also begins deleting data on any connected system.

While it may seem like the key is deleting everything it consumes, it actually seems to contain some storage. It is unclear how to access it, perhaps the answer lies in the Red Book?

Any fabricator which attempts to make a Red Key always run unusual and inexplicable errors, such as requesting seemingly random ingredients, creating a completely different objects, etc.

\begin{ravenbox}
    \subsection{Spectral Codicies}
    These are a collection of Ravens which exist as \textit{texts.} Untold number of books, scrolls, and digital documents which have a life of their own. Each offers the reader unique abilities and powers, but at a heavy cost. 

    The Red Book, also known as \redbookname{} is a well~-known example. It is a database of unusual and dangerous blueprints. Objects created from these blueprints are bound to be destructive, and they are near~-universally banned. The original database's location is unknown, as even though it is digital, full copies of it do not exist. Poor and corrupted copies of its blueprints are a valuable commodity on the black market. It's ``red'' name comes from the fact that all objects its designs produce are red.
\end{ravenbox}