This equipment is used to enforce laws, control populations, and compel obedience. It can also easily be used for torture and mind control.

\section{Forensics and Lie Detection}\label{sec:forensics_lie_detection}
%\addcontentsline{toc}{section}{Forensics and Lie Detection}
Forensic equipment is used to analyze clues, such as those at crime scenes. In addition to this specialized gear, investigators use chemsniffers (p. \pageref{subsec:chemsniffer}), portable labs (p. \pageref{subsec:portable_laboratories}), and medscanners (p. TODO). 

Lie detectors help determine whether the subject believes they are telling the truth. It is up to the investigator to decide if that subject is correct or if they have a faulty memory, is delusional, or was brainwashed. Even with modern, high~-tech, the veracity of this technology is often contested.

\subsection{Verifier Software}\label{subsec:verifier_software}
This computer program monitors a person's facial expression, especially facial movements near the eye muscles; different programs are needed for nonhumans. Creating software for other species requires knowledge of the species' biology and psychology. The software uses passive visual sensors (p. \pageref{sec:passive_visual_sensors}), and has Detect Lies-12. Complexity 4. LC3.

If the subject whose lies are being tested has any knowledge of the software being used, they can ``fudge the test'' giving them a +2 to Fast~-Talk or other skill rolls when trying to fool the software. If they know the exact methods of the software, add an additional +1.

\subsection{Neural Veridicator}\label{neural_veridicator}
A \textit{veridicator program} provides highly accurate lie detection by monitoring brain waves transmitted through a braintap neural interface (p. TODO). It gives a human or computer a bonus of +5 to Detect Lies skill.

\textit{Neural veridicator helmets} are \textit{completely} reliable, providing an automatic success on a Detect Lies roll. However, people can forget, delude themselves, be fooled, or have their memories altered by brainwashing technology. A veridicator does not provide absolute truth; it just tells if someone believes they are telling the truth.

\textit{Veridicator Helmet:}\label{itm:veridicator_helmet} This incorporates a dedicated neural interface and veridicator software. The user wears the helmet; it signals if he is lying. \$12,000, 2 lb. B/24 hr. LC3.

\textit{Veridicator Program:}\label{itm:veridicator_program} Complexity 6. LC3.

\subsection{Forensic Swarm}\label{subsec:forensic_swarm}
These swarms can provide detailed information on the room’s occupants and visitors for the past several years by analyzing the buildup of organic and inorganic detritus: skin flakes, blood, clothing fibers, food residue, presence of other nano, etc. When gathering forensic evidence, each square yard of swarm can sweep one square yard per hour. The data collected from people or animals will reveal their sex, race, blood type, genetic pattern and approximate age. It can form the basis of a computer simulation of what they might look like, but will not identify someone unless she is listed in a database available to the investigator. Forensic swarms can also perform pathological analysis without an autopsy.

A forensic swarm gives a +3 (quality) bonus to Forensics skill for gathering evidence. Analyzing the data requires Forensics (or Biology) skill or an appropriate expert-system program. \$4,000/square yard. LC2.


\subsection{Truth Croaker}\label{subsec:truth_croaker}
This raven~-tech device has the subject mostly consumed by a controlled oracle toad and then asked questions. By analyzing the brainwaves of the oracle toad, the operators can tell whether or not the statement is true according to the toad's oracle abilities.

This technology is experimental, not really understood, and considered physically and metaphysically dangerous. Construction requires a giant, captured oracle toad, making it particularly difficult to manufacture. Not generally available for sale, likely in the multi~-millions. 800 lb. LC0.

\begin{ravenbox}
    \subsection{Oracle Toads}\label{subsec:oracle_toads_ravenbox}
    Toad~-like Ravens which are the size of a compact car. They have six eyes in their head and one on the tip of their long tongue. 

    Their name originates with their abilities; they have precognitive, retrocognitive, and more oracle~-like abilities. They are capable of communicating with humans, offering them prophecies in exchange for heavy and often gruesome costs. They seem to universally hate humans and take pleasure in answering their questions in horrifying them with their prophecies and answering questions that people would be better off not knowing.

    Capturing one is no small feat, given they can predict the future and are unlikely to ever be caught off guard.
\end{ravenbox}

\section{Restraint and Riot Control Devices}\label{sec:restrain_riot_control}
%\addcontentsline{toc}{section}{Restraint and Riot Control Devices}
This equipment is used by security forces to restrain individuals, or to control and disperse crowds of demonstrators or rioters. Other useful equipment includes:

\textit{Barricades:} Construction foam (p. \pageref{subsec:construction_foam}), construction swarms (p. \pageref{subsubsec:construction_swarm}), and slipspray (p. \pageref{subsec:slipspray}) allow quick erection of barricades to channel crowds and block streets. Holoprojectors (p. \pageref{subsec:holoprojectors}) may create illusionary barriers to divert an unwary mob.

\textit{Dispersion:} Techniques useful for scattering crowds without leaving a field of stunned, injured, or dead bodies are microwave pain beams (MAD, p. TODO) and sonic nauseators (p. TODO). Launchers and sprays may deliver riot gas (p. TODO), sonic nauseators (p. TODO), or warbler warheads (p. TODO). Shock clubs (p. TODO) and neurolashes (p. TODO) let an officer defend themself, and can be a painful but nonlethal deterrent.

\textit{Shields:} Riot shields (p. TODO) can used not only as defenses, but also to push or slam rioters.

\subsection{Cufftape}\label{subsec:cufftape}
This looks like duct tape, but the sticky side is a memory polymer that tightens if the prisoner struggles. A two~-foot~-long strip has ST 20, and is sufficient to restrain arms or legs. Each failure to escape does one point of damage to the taped area. Cufftape has DR 1; six points of cutting, corrosioon, or burning damage severs it. \$10, 0.5 lb. per 100~-foot spool. LC3.

\subsubsection{Razortape}\label{subsubsec:razortape}
This cufftape has a thin strand of sharp wire embedded in it. On a successful attempt to break free using brute force (a Quick Contest of ST), the wire does thrust cutting damage using the escapee's own ST. \$40, 0.5 lb. per 100~-foot spool. LC2.

\textit{Monowire Razortape:}\label{itm:monowire_razortape} As razortrape, but it costs twice as much and does +1d damage. The damage has an armor divisor of (10).

\subsection{Electronic Cuffs}\label{subsec:electronic_cuffs}
This is a rigid pair of handcuffs or leg irons, padded to avoid abraisons and used for restraining people or animals. It is controlled by an embedded remote~-controlled radio microcommunicator, and incorporates a homing beacon (p. \pageref{subsec:homing_beacon}) for tracking the prisoner.

To break free of the restraints, win a Quick Contest of ST or make an Escape roll at -6 (-8 if both arms and legs are cuffed). The first try takes one second; further attempts require 10 minutes of struggle. Also available with color and 10' leash (same weight) for animals, slaves, etc. It may incorporate neuronic restraints or a neural pacifier (p. TODO).

\textit{Electronic Cuffs:}\label{itm:electroninc_cuffs} This has ST 25 and DR 15. \$40, 0.25 lb., A/1 wk. LC4.

\textit{Heavy~-Duty Electronic Cuffs:}\label{itm:heavy-duty_electronic_cuffs} ST 45 and DR 20. Uncomfortable to wear. \$100, 0.5 lb., A/1 wk. LC3.

\subsection{Explosive Collar}\label{subsec:explosive_collar}
A locked, plastic~-alloy collar that attaches around a prisoner's neck. It contains an inertial compass, secure radio, and a tiny computer (p. \pageref{itm:tiny_com}) -- none of them usable by the wearer -- along with explosives equivalent to a 15mm HE warhead (p. TODO). The radio and computer constantly broadcast the prisoner's exact coordinates.

A coded signal can detonate the explosive liner, decapitating the wearer. The collar can also be broken (it has DR 10 and 2 HP), but any attempt to damage it that fails to immediately remove it results in detonation next to the subject's neck. Disarming the explosives requires appropriate tools and a Traps-4 roll; failure means the collar explodes. \$200, 0.25 lb., B/100 hr. LC2.

\subsection{Power Damper}\label{subsec:power_damper}
A neural~-feedback device that is designed to restrain espers, ravens, and witches; each requires their own devices. It prevents the subject from consciously making use of their powers.

The subject can attempt to overcome the device by deliberately pushing herself: each time she tries to use an ability that would be impeded by the device. she must win a Quick Contest of Will against the device's Will. She may add her relevant Talent (Magery for witches), if any. If she succeeds, she overloads the device, which burns out. If she fails, she cannot try again for \textit{hours} equal to the margin of failure.

A power damper may be combined with neuronic restraints (below), triggering a ``punishment circuit.'' This activates the neurolash after any attempt to overcome the damper.

\textit{Power~-Damper Band:}\label{itm:power-damper_band} A small headband. The damper can also be built into electronic cuffs, a collar, or a sensory restraint. It has an effective Will 20. \$2,000, 0.1 lb., B/100 hr. LC3.

\textit{Power~-Damping Field:}\label{itm:power_damper_field} This covers a 2~-yard radius, it can be built into a cell, giant test tube, small prison, etc. Effective Will 22. \$20,000, 70 lb., E/100 hr. LC3.

Models which dampen witches or ravens are more expensive the the espers. Double the cost for ravens, and triple for witches. 

\subsection{Sensory Control Restraints}\label{subsec:sensory_control_restraints}
A single~-piece device containing a video visor (p. \pageref{itm:conf_goggles_visor}) and ear muffs designed to control the reality perceived by the wearer. It can also see and hear what the prisoner does (and, if desired, record it). The visor can blank out the prisoner's vision or hearing, restore it, or let the controller overlay false sounds and images. It can be controlled by any external interface with the proper security codes. It includes a tiny computer, and is can be equipped with its own AI (sold separately). It has DR 9.

\textit{Smart Blindfold:}\label{itm:smart_blindfold} Locks onto the head, covering eyes and ears. Gives a +1 (quality) bonus to Interrogation skill against the wearer. \$100, 1.5 lb., C/100 hr. LC2.

\textit{Restraint Mask:}\label{itm:restraint_mask} A flexible helmet that covers the entire head and locks into place; it takes six seconds to attach or remove. It blocks the senses of smell and taste, and also includes a removable gag/feeding tube and respirator tube. Gives a +2 (quality) bonus to Interrogation rolls against the wearer. \$500, 2 lb., 2C/100 hr. LC2.

\textit{Sensory Deprivation Tank:}\label{itm:sensory_deprivation_tank} \textit{Completely} removes all sensations except that permitted by the operator by supsending the subject in a sense~-deadening liquid medium (experimental gwhel~-contragravity versions have been made as well). Treat as a restraint mask, but the bonus to Interrogation rolls increases to +3 after the subject has been in the tank for an hour. Long stays require Fright Checks: use the \textit{Size and Speed/Range Table}, reading ``yards'' as ``hours'' and rolling every time an interval passes at the listed penalty. An unrelated benefit of sensory deprivation tanks is that they provide espers bonuses, see \textit{Sensory Deprivation} (p. \pageref{sec:sensory_deprivation}). The tank includes a restrain mask, respirator, and feeding tubes. \$10,000, 200 lb. D/100 hr. LC3.

Advanced set ups can integrate or use neural interfaces (p. \pageref{sec:neural_interfaces}) and either sensie (p. \pageref{sec:sensies}) or total virtual reality (p. \pageref{subsec:total_vr}) technology for sensory control.

\subsection{Neuronic Restraints}\label{subsec:neuronic_restraints}
An add~-on for electronic cuffs or collars, these use a tailored electrical impulse to deliver a neurolash effect (p. TODO) if tampered with, or if triggered by a communicator.

They are available in all standard neurolash settings, although the seizure, pain, paralysis, and ecstasy effects are most common (sometimes pain or ecstasy are purchased for recreational purposes). The effect is identical to a neurolash strike (roll vs. HT-5 to resist). However, since the victim is restrained and the effect can be continued each turn, these restraints are very effective.

This option can also be built into sensory restraints (above). A neurolash delivering pain or pleasure in a sensory deprivation tank is especially effective; add an extra -1 to the roll to resist. \$200, 0.25 lb., B/100 sec. lC2. Tunable versions are +0.5 CF per setting.

\subsection{Neural Pacifier}\label{subsec:neural_pacifier}
Used legally by police, prison guards, and hospitals, this restraint band projects a soothing hypnagogic field into the wearer's brain, keeping them sedated and compliant without using drugs or risking injury.

It has two settings: sleep and control. On ``sleep,'' it places the wearer into a deep slumber. They cannot be awakened until the device is removed or turned off. On ``control,'' the headband projects frequencies that allow the user to retain consciousness while suppressing aggressive tendencies, making the subject easily led. It effectively give sthem the Slave Mentality disadvantage.

The device can be resisted. After it is activated, the wearer gets a roll against the \textit{higher} of HT-3 or Will-3 each second to avoid succumbing to the effects. Once a roll is failed, the effects persist for as long as the device remains on. \$500, 0.25 lb., B/100 hr. LC3. This option can also be built into sensory restraints.

\section{Interrogation, Brainwashing, and Animal Control}\label{sec:interrogation_brainwashing_animal_control}
%\addcontentsline{toc}{section}{Interrogation, Brainwashing, and Animal Control}
Unlike passive lie detection gear, these systems are used to actively retrieve information, as well as to alter, erase, or enslave minds of people or animals. See also \textit{Drugs and Nano}, p. TODO.

\subsection{Biopresence Software}\label{subsec:biopresence_software}
This software allows the user to teleoperate another living entity's body (the host). The host must have a puppet implant (p. TODO), and the user must be in telecommunication with the host, or physically jacked into him. THe user must be using a direct neural interface (p. \pageref{subsec:direct_neural_interface}) connected to the computer running this software, or be a digital mind.

Control can be achieved automatically if the user has the appropriate passwords for full access to the puppet's mind; gianing these may require Computer Hacking skill.

The user remotely teleoperates the host's body, completely suppressing the host's personality. Her own body is in a trance; she may choose to return at any time, and must do so if the communications link is interrupted. Sleep does not break the link, but if it is ever jammed or out of range, the operator loses control.

The user gains the host’s ST, DX, HT, and secondary characteristics calculated from these scores, as well as the host’s physical advantages and disadvantages. The user keeps her own IQ, Perception, Will, and mental traits. Social traits may or may not apply. The user’s IQ-, Perception-, and Will-based skills are unchanged. Other skills remain at the same relative skill level. For instance, if the user has Guns at DX+3, then she would have Guns-12 in a DX 9 body and Guns-14 in a DX 11 body.

The user has no access to the subject’s memories.

If you have biopresence software and appropriate equipment implanted in your body, you must take the Puppet advantage (p. B78) for each Ally or Dependent (or group of them) whose mind you have access codes for.

The software is Complexity 7, double standard cost.

\subsection{Brainwipe Machine}\label{subsec:brainwipe_machine}
This technology uses focused energy fields to alter brain structure and destroy memories.

On some planets, brainwipes are used to punish criminals or dissidents. It is also used some places to erase sensitive information from the mind of those who now too much. A Brainwipe causes classic amnesia erasing all memories of the subject's personal life. It leaves personality and abilities intact. After brainwipe, a victim's skills and mental disadvantages remain unchanged. They can function in society, but cannot remember their name, or anything from their past, even when confronted with evidence. This gives the subject the Amnesia disadvantage.

\textit{Clinical Brainwipe Machine:}\label{itm:clinical_brainwipe_machine} This is a room~-sized device incoproating a specialized diagnostic bed (p. TODO). It gives a +1 (quality) bonus to operator skill. \$100,000, 100 lb., D/10 days. LC2.

\textit{Portable Brainwipe Machine:}\label{itm:portable_brainwipe_machine} A helmet~-sized device, plus an attached briefcase~-sized control unit. \$10,000, 5 lb. C/24 hr. LC2.

\subsection{Message Bomb}\label{subsec:message_bomb}
A smart grenade (p. TODO) may be equipped with a tiny speaker and player. This lets it be programmed to deliver an audio message. This is usually set to play when the grenade is used with a time~-delay fuse. The maximum duration of the message is 20 minutes. Add \$10 per weapon. LC3.

\subsection{Neural Programmer}\label{subsec:neural_programmer}
This uses a neural interface to ``get inside'' a subject's head, then alter his perceptions through subtle and overt applications of total virtual reality (p. \pageref{subsec:total_vr}).

The subject must be fitted with a neural interface (p. \pageref{sec:neural_interfaces}) and connected to a computer system running neural programmer software. He is then put through multiple scenarios, some realistic, some bizarre or even hellish. The operator does not require a neural interface. Neural programming may add or remove a permanent self~-imposed mental disadvantage (p. B121). It may give the subject a set of false memories or beliefs, which take the form of Delusions (p. B130). It can also induce a Phobia (p. B149).

The process is handled as a regular contest of Brainwashing skill vs. the subject's Will; add the equipment bonuses given below, and apply a penalty of -1 to skill for every -5 points or fraction the disadvantage is worth. Base time is one day, but more or less time can be taken -- see \textit{Time Spent} (p. B346).

This process cannot actually \textit{erase} memories (see \textit{Brainwipe Machine}, p. \pageref{subsec:brainwipe_machine}) but it can give the subject the Delusion that a brainwashing, kidnapping, or other traumatic event was actually a dream or false memory.

Neural programmer software is Complexity 7. Good~-quality software (+1 quality bonus) is Complexity 9; fine~-quality software (+2 quality bonus) is Complexity 11. LC1.

\subsection{Mechanical Mind Probe}\label{subsec:mechanical_mind_probe}
This device, also called an extractor, probes a subject's mind and retrieves memories. As the operator questions the subject, the extractor stimulates the brain to recall specific memories. It then uses electrochemical means to read those memories as they are formed.

Use of the device requires a successful Electronics Operation (Medical) skill. Critical success retrieves the exact memory the questioner wishes to evoke. Success retrieves some of the desired memories, mixed with exaggerations, errors, or unrelated associations. Failure retrieves fragmentary memories of no interest to the interrogator, or obviously false memories. Critical failure results in the subject's brain constructing false memories that seem realistic.

All memories are in the form of a raw sensie feed. Its length depends on the duration of the probe. This information must be accessed via neural interface before the user knows whether the attempt succeeded or failed; see \textit{Sensies} (p. \pageref{sec:sensies}).

A mind probe may be used as a fast or slow probe. A slow probe is safe, but takes eight hours per attempt. A fast probe takes only an hour per attempt, but is dangerous to the subject: whether the probe succeed or fails, she must roll bs. the \textit{lower} of his HT or the operator's skill. Failure means brain damage (-1 to IQ); critical failure means she suffers the Coma mortal condition, and cannot be further interrogated until she recovers.

\textit{Clinical Mind Probe:}\label{itm:clinical_mind_probe} This is a room~-sized scanning device incorporating a specialized diagnostic bed (p. TODO). \$200,000, 200 lb., D/10 days. LC2.

\section{Black Ops Robots}\label{sec:black_ops_robots}
Robots are perfect for many security and intelligence missions. 

In addition to the types covered below, combat androids (p. TODO), scoutbots (p. \pageref{subsec:scout_robot}), and warbots (p. TODO) are often used for these jobs. Nursebots (p. TODO) also make effective interrogators.

\subsection{Robobug}\label{subsec:robobug}
\hfill \large{\textbf{-32 points}} %+5
\normalsize

This is single robot the size of a large insect (SM-9). It is bigger than most microbots, but still small enough to easily escape notice. It is designed for surveillance, forensics, scouting, or assassination. It may also patrol power conduits or air ducts, performing security or maintenance tasks. Its weapon mount can hold a weapon up to 0.01 lb. weight, such as a micro~-laser or a drug injector.

\begin{hangparas}{1em}{1}
    \textbf{\textit{Attribute Modifiers:}} ST-9 [-90].
    
    \textbf{\textit{Secondary Characteristic Modifiers:}} SM-9; Basic Move -3 [-15].
    
    \textbf{\textit{Advantages:}} Absolute Direction (Requires signal, -20\%) [4]; Clinging [20]; Discriminatory Smell [15]; Doesn't Breathe [20]; DR 1 (Can’t Wear Armor, -40\%) [3]; Extra Arm (Weapon Mount, -80\%) [2]; Infravision [10]; Machine [25]; Peripheral Vision [15]; Protected Vision [5]; Radio (Burst, +30\%; Reduced Range 1/10, -30\%; Secure, +20\%; Video, +40\%) [16]; Sealed [15]; Sharp Teeth [1].

    \textbf{\textit{Perks:}} Accessories (Flashlight, tiny computer) [2].

    \textbf{\textit{Disadvantages:}} Bad Sight (Nearsighted) [-25]; Disturbing Voice [-10]; Electrical [-20]; Increased Consumption 1 [-10]; Restricted Diet (Vey Common, power cells) [-10].

    \textbf{\textit{Availability:}} \$50, 0.01 lb., A/4 hr. LC4.
\end{hangparas}

Robobugs come in various shapes, not all of them bug~-like.

\begin{hangparas}{1em}{1}
    \textit{Crawler} (+16 points): a spider~-bot that crawls along the ground. Add Extra Legs (6 legs) [10] and Super Climbing 2 [6].

    \textit{Flier} (+41 points): A dragonfly~-like ornithopter. Add Extra Legs (4 legs) [5] and Flight (Small Wings, -10\%) [36]. Double cost.

    \textit{Rodent} (-35 points): A mouse~-sized robot. Add the Quadruped [-35] meta~-trait.

    \textit{Toy Soldier} (-15 points): A humanoid robot, like a miniature figure. Remove Peripheral Vision [15].

    \textit{Worm} (-35 points): A serpentine robot slim enough to squirm through a keyhole~-sized opening, along a drain pipe, or even down a throat to explore someone's stomach. Add the Vermiform [-35] meta~-trait.

    \textit{Vehicle} (-80 points): A tiny robot all~-terrain vehicle, like a toy car. Add Enhanced Move 1 (Ground) [20] and Ground Vehicle [-100], with wheels or tracks. Half cost.
\end{hangparas}

\subsubsection{Optional Upgrades}
\begin{hangparas}{1em}{1}
    \textit{Water Jets} (+10 points): Add Amphibious [10]. +50\% cost.
\end{hangparas}