\section{Domestic Equipment and Appliances}\label{sec:domestic_equip}
%\addcontentsline{toc}{section}{Domestic Equipment and Appliances}
The following household items are available:

\subsection{Housebot}\label{subsec:housebot}
This small domestic robot serves as a waiter, janitor, or homemaker, depending on its configuration. Its internal payload space can accommodate a garbage can, vacuum cleaner, microwave oven, ultrasonic dishwasher, or a reservoir for cleaning agents. It is designed to run quietly, to avoid disturbing people while working. It moves on legs.

\begin{hangparas}{1em}{1}
    \textbf{Atribute Modifiers:} ST-3 [-30]; HT+2 [20].
    
    \textbf{Secondary Characteristic Modifiers:} SM-1; HP+5 [10].

    \textbf{Advantages:} Absolute Direction (Requires signal, -20\%) [4]; Doesn't Breathe [20]; DR 5 (Can't Wear Armor, -40\%) [15]; Extra Legs (four) [5]; Infrared Communication (Reduced Range 5, -20\%) [8]; Machine [25]; Reduced Consumption 3 [6]; Silence 2 [10]; Payload 2 (2 lb. cargo) [2]; Radio (Secure, +20\%) [12].

    \textbf{Perks:} Accessory (Cleaning equipment, tiny computer) [2].

    \textbf{Disadvantages:} Electrical [-20]; Maintenance (one person, monthly) [-2]; Restricted Diet (Very Common, power cells) [-10]; Striking ST -2 [-10].

    \$1,000, 20 lb., C/24 hr. LC4.
\end{hangparas}

\subsection{Responsive Beds}\label{subsec:responsive_beds}
This bed can adjust to the shape of the sleeper, respond to voice commands to become softer, firmer, bouncier as desired. Adds +1 to Erotic Art skill if used inventively, and adds +5 to any Will rolls made to get to sleep.

\textit{Single:} \$500, 100 lb.
\textit{Double:} \$700, 140 lb.

\subsection{Autokitchen}\label{subsec:autokitchen}
This automated kitchen is fitted with a complete set of robotic manipulator arms. It can cook on command using its Cooking~-10 skill. Alternatively, when connected to a network, can be used remotely to duplicate the moves of a live chef and use the chef's Cooking skill. \$20,000, 400 lb.

\subsection{Domestic Nanocleanser}\label{subsec:domestic_nanoclean}
Also known as ``smart soap," this is a solution of microscopic cleaning robots that work to remove stains, grime, dirt, dandruff, and loose skin flakes from surfaces. It can serve as a shampoo, soap, or detergent. A teaspoon of nanocleanser powder poured into water will clean anything immersed in it in 10 to 60 seconds. It also comes in pre~-mixed liquid~-detergent form for when water is unavailable.

While some may find washing in nanocleanser to be unsettling due to its tingling sensation, it is not dangerous and once you get used to the tingling sensation, it can be quite pleasent. The bots themselves are biodegradable, non~-toxic, and smart enough not to scrub too hard. Furthermore, they are programmed to break down harmlessly if exposed to ultra~-violet light or the interior of a living body.

Nanocleanser can disrupt forensic evidence such as bloodstains, skin flakes, and other organic residue. While it doesn't work as well as Mask spray (p. TODO), treating an area with it imposes a -3 penalty on any Forensics rolls made to locate or analyze such evidence. That said, Forensice \textit{can} identify the brand of nanocleanser used!

A bottle of nanocleanser lasts for about of week of routine domestic cleaning or one major cleaning job (such as thoroughly wiping down an apartment to remove evidence).

Nanocleanser adds a quality bonus of +5 to Housekeeping skill rolls to clean. A bottle is 1/2 lb. and costs \$10. A bar is 0.1 lb. and costs \$1

\subsection{Cleaning Swarm}\label{subsec:cleaning_swarm}
A swarm of micro or nanobots which is programmed to move around a preprogrammed path or area, removing dust and grit, and polishing smooth surfaces. Its sensors allow it to clean precisely and without damaging surfaces, making it ideal for cleaning glass or lenses or even people! Each square yard of swarm can thoroughly clean one square yard per minute. The swarm gives a +2 (quality) bonus to Housekeeping skill. \$1,000/square yard. LC4.

\subsection{Domestic Android}\label{subsec:domestic_android}
% 7Sign's hospitality model (p. \pageref{subsec:7sign_hospitality}) are often purchased as humanoid butlers or maids.
General-purpose androids (p. \pageref{subsec:general_android}) are often purchased as humanoid butlers or maids.

\subsection{Sonic Shower Head}\label{subsec:sonic_shower}
Found in many homes and starships, and other places where water is scarce. An ultrasonic spray unit clipped to a wall simultaneously cleans and massages the user. \$400, 10 lb., external power (generally from the building or ship's power). LC4.

\section{Housing and Construction}\label{sec:housing_and_construction}
%\addcontentsline{toc}{section}{Housing and Construction}

\subsection{The Intelligent House}\label{subsec:intelligent_house}
While not ubiquitous, it is common for houses, apartments, hotel rooms, and passenger ship cabins to include a voice~-activated computer system that controls climate, domestic appliances, security, and communications. The system is programmed to respond to the occupants' voiceprints. Cheaper apartments tie into the landlord's main building computer, which provides similar services, but with less security. 

\subsection{Domed Cities}
On many planets which haven't been made hospitable or even livable to human life, it is common for entire towns or cities to be enclosed in a transparent dome. The cheapest version of this terrestrial habitat use wire-reinforced shatterproof glass, mist~-plated with aluminum to cut sun glare while still letting in light. From the outside, they look like giant mirrors, from the inside the glass is almost invisible. A dome about two miles wide and a mile high generally weighs about 4,000 tons.

\subsection{Space Habitats}\label{subsec:space_habitats}
%\addcontentsline{toc}{section}{Space Habitats}
Large, manufactured habitats are usually built using titanium, aluminum, and steel that is mined from nearby moons or asteroids. Inside, gravity is simulated using rotation or, on more recent/advanced habitats the gravity is generated using gwhel-gravity generators.

\subsubsection{O'Neill Cylinders}\label{subsubsec:oneill_cylinders}
These large and expensive space habitats are giant cylinders a few miles wide and several miles long. They rotate to simulate Earth-normal gravity. Inside is a complete environment with park and urban landscapes. Each one can house a few million people. Large populations may be supported by additional agricultural habitats.

\subsubsection{Standford Torus}\label{subsubsec:stanford_torus}
Smaller than O'Neill cylinders, these habitats are still very large. A typical torus is shaped like a bicycle wheel, with gravity and lanscaping on the floor of the outer rim. The spokes are elevators that lead to a central microgravity hub. Typically, they house 10,000 to 100,000 people.

\subsubsection{Asteroid Hives}\label{subsubsec:asteroid_hives}
Instead of manufacturing space habitats as free-floating structures, these are made by completely or partially hollowing out asteroids so that people can live inside. Larger asteroids are capable of supporting billions of inhabitants.

\subsubsection{Macrohabitats}\label{subsubsec:macrohabitats}
These are continent~-sized habitats. As humanity first started colonizing space, inhabitants simply had to tolerate microgravity though recent advances in contragravity generations has allowed for Earth-like gravity even aboard these habitats.

\subsection{The Flexible House}\label{subsec:flexible_house}
An intelligent house can have a \textit{sapient} brain that handles everything from doing the dishes to tutoring children. It is smart enough to anticipate the owner's desires.

Within the house, domestic products can be made of smart, self~-repairing materials. Living carpets may clean themselves. Beds, tables, and chairs may assume different shapes, textures, and colors to fit the occasion, or be absorbed into the walls and floor when not in use. Artifacts and interior partitions may change color with a word to the house computer.

These houses give a +2 (quality) bonus to Housekeeping skill. A typical three~-bedroom home is \$100,000, but this does not account for the cost of the AI.

\subsection{Castles in the Air}\label{subsec:castles_in_the_air}
As contragravity generators advance, they are expanding the possibilities of human construction. Take, for example, the floating cities of Erebos, which use gwhel gravity generators to create floating islands upon which cities can rest while also providing inhabitants Earth-like gravity.

\subsection{Phantom Places}\label{subsec:phantom_places}
Holotech projectors can create illusionary partitions and art images; redecoration is as easy as changing programs. Scented air conditioning and realistic audio effects can complete the illusion.

\subsection{Star Habitats}\label{subsec:star_habitats}
Industry leaders claim that soon humanity will be able completely enclose entire stars and build massive habitats. 

\subsubsection{Dyson Bubble}\label{subsubsec:dyson_bubble}
A loose array of light sails and solar energy collectors which beam energy to other habitats. Andromeda Electric has recently begun plans to start building such structures as it expands to other galaxies besides Andromeda.

\section{Foodstuffs}\label{sec:foodstuffs}
%\addcontentsline{toc}{section}{Foodstuffs}

\subsection{Meal Pack}\label{subsec:meal_pack}
These packaged meals have little weight or volume, yet supple the nutrition and calories needed to keep a person active for extended periods. Although long~-term use could cause some discomfort or weight gain, they are usually tasty and provide enough variation for almost everyone to have a favorite. Stored meal packs have a safe shelf~-life of 20 years. They come in dozens of variations, with randomly selected main courses, side dishes, and dessert. The packages can heat or cool themselves, and are sealed against the outside environment. \$2, 1 lb. per meal.

\subsection{Survival Rations}\label{subsec:survival_rations}
These are designed to put the maximum amount of nutrients into the smallest sealed package; the flavors are limited and generally underwhelming. They have a safe shelf~-life of 30 years, provided the package is not tampered with. Each meal is \$5, 0.5 lb.

\subsection{Food Tablets or Paste}\label{subsec:food_tablets}
These tablets or paste~-filled tubes provide all the vitamins and calories that an active person requires. They also incorporate appetite suppressants. A one~-day supply (usually split into 6 to 12 individual meals) is \$10, 0.75 lb.

\subsection{Food Vats}\label{subsec:food_vats}
These culture growth tanks allow for an endless supply of imitation vegetables, lean meat, fish, or other foodstuff. On most planets, your average person has never eaten non~-vat meat and ``real'' meat has become a luxury.