Humanity has had many millennia to study psionics and has developed a strong understanding of the underlying mechanics and science.

``Psi amps'' boost a psi's Talent level in a particular power, such as Psychokinesis. This boost can increase the psi's Talent beyond the usual limits. The user can always choose (unless noted otherwise) to use less than the maximum boost, which reduces the danger should psychotronic feedback (below) occur. 

 Optionally, a psi amplifier can be set up to boost psionic abilities, instead each +1 bonus adds +1 level to any leveled psionic ability, this requires specialization and +0.5 CF to the psi amp.

A psi amp should be attuned to the user, and can only be attuned to one person at a time. This requires a successful roll against Electronics Operations (Psychotronics) skill. Failure wastes an hour; critical failure damages the device. It is possible to use a psi amp that is not properly attuned, or is attuned to someone else, buy any roll of 15+ when using the device is treated as a critical failure.

The power surge a psi experiences when using an amplifier can be dangerous. If the user ever suffers a critical failure while using an amplified ability, they suffer psychotronic feedback. This burns out the machine, which requires minor repairs. The user must make a HT+3 roll, at a penalty equal to the boost. Failure means they suffer a seizure (p. B429) for seconds equal to margin of failure (along with the usual 1d FP loss afterward); failure by 5+ results in psionic feedback that leaves the user unconscious, suffering the Coma mortal condition (p. B429).

\subsection{Amplifier Throne}\label{subsec:amplifier_throne}
This is a throne~-like chair, with a helmet, biofeedback monitors, and a computer. The user sits in the chair, and power floods through him to be channeled into psionic energy. Unless the user is very powerful, machines amplifying teleportation will move the user, but not the machine. The device adds up to +5 to the user's Talent in a particular power.  \$200,000, 1,000 lb., external power. Machines that can amplify more than one power at a time are available -- add \$100,000, 500 lb. per extra power. LC3.

\subsection{Backpack Psi Amplifier}\label{subsec:backpack_psi_amp}
A psi amplifier that uses a backpack~-sized power pack connected to a helmet, and run off a D cell. Portable amplifiers can increase the user's Talent by up to +3 in a particular power. \$40,000, 20 lb., D/1 week. Add \$20,000 and 10 lb. per extra power it can amplify. LC3.

\subsection{Psi Amplifier Helmet}\label{subsec:psi_amp_helmet}
A low-powered psionic amplifier. It adds a maximmum of +1 levels of Talent to a prticular power. \$25,000, 4 lb., C/1 week. Add \$10,000 and +2 lb. per extra power it can boost. LC3.